### 2022-06-23 Russia Case Study.Rmd
Visualized artis demo

---
title: "Russia Case Study"
author: "Joseph Barnes"
date: '2022-06-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(formatR)
library(RColorBrewer)
library(viridis)
library(janitor)
library(reader)

library(cli)
library(devtools)
library(tidyverse)
library(sf)
library(cowplot)   # for theme_map()
library(lwgeom) # for st_transform_proj
library(ggsn) # for adding north arrows and scale bar
library(rworldmap) # for getMap()
#library(spData) # for world data
library(rnaturalearth)
library(rnaturalearthdata) # supporting data, only install/load if prompted 
library(gtrendsR)
library(knitr)
library(readr)
library(stringr)
library(ggthemes)
library(kableExtra)
library(countrycode)
```

```{r}
artis_russia <- read_csv("C:/Users/User/Documents/American University/Global Seafood Lab/case_study_russia/20220616_josephbarnes_ARTIS_snet.csv", 
     col_types = cols(year = col_number()))

```

```{r}
artis_russia <- clean_names(artis_russia)
artis_russia$hs6 <- str_pad(artis_russia$hs6, 6, pad = "0")

str(artis_russia) # 246,373 x 12
unique(artis_russia$exporter_iso3c)
unique(artis_russia$importer_iso3c)
unique(artis_russia$dom_source) # "foreign export"  "domestic export" "error export"  
unique(artis_russia$source_country_iso3c)
unique(artis_russia$sci_name) # > 999 
unique(artis_russia$environment) # "marine"  "inland"  "unknown"
unique(artis_russia$method) # "capture" "aquaculture" "unknown" 
unique(artis_russia$hs_version) #HS12
unique(artis_russia$year) # 2012, 13, 14, 15, 16

```
  Exporters:
  [1] "ARE" "ARG" "ARM" "AUS" "AUT" "BEL" "BGD" "BGR" "BLR" "BRA" "CAN" "CHE" "CHL" "CHN" "COL" "CYP"
 [17] "CZE" "DEU" "DNK" "ECU" "EGY" "ESP" "EST" "FIN" "FLK" "FRA" "GBR" "GEO" "GRC" "GRL" "HKG" "HRV"
 [33] "HUN" "IDN" "IND" "IRL" "ISL" "ISR" "ITA" "JPN" "KAZ" "KOR" "LBN" "LKA" "LTU" "LVA" "MAR" "MDA"
 [49] "MDV" "MEX" "MRT" "MYS" "NGA" "NIC" "NLD" "NOR" "NZL" "PAK" "PER" "POL" "PRT" "RUS" "SAU" "SGP"
 [65] "SRB" "SVK" "SVN" "SWE" "SYC" "THA" "TUN" "TUR" "TWN" "UGA" "UKR" "URY" "USA" "UZB" "VNM" "YEM"
 [81] "ZAF" "AZE" "FJI" "GHA" "KGZ" "MLT" "PHL" "PRK" "TJK" "BHR" "CMR" "FSM" "IRN" "MMR" "MNG" "OMN"
 [97] "TZA" "BFA" "CIV" "KEN" "NAM" "TGO" "BEN" "MUS" "SEN"

Importers:
Show in New Window
  [1] "CAN" "CIV" "HKG" "MDV" "OMN" "PAK" "QAT" "SDN" "RUS" "CHN" "JPN" "MYS" "SGP" "THA" "TWN" "CHE"
 [17] "DEU" "FRA" "GRC" "HUN" "NLD" "POL" "SVK" "SVN" "AUS" "AUT" "CZE" "DNK" "ESP" "FIN" "GBR" "IRL"
 [33] "ISR" "ITA" "LTU" "MLT" "NGA" "NOR" "PRT" "ROU" "SWE" "ARM" "AZE" "EST" "GEO" "KAZ" "MDA" "NZL"
 [49] "TKM" "UKR" "USA" "ATG" "BRA" "BRB" "CUW" "DMA" "DOM" "GRD" "GTM" "HTI" "IDN" "ISL" "JAM" "KOR"
 [65] "MAC" "MEX" "SUR" "TTO" "VNM" "ZAF" "ARG" "BOL" "PER" "ABW" "AGO" "ALB" "ARE" "BEL" "BGD" "BGR"
 [81] "BHR" "BIH" "BLR" "BRN" "CHL" "CMR" "COD" "COG" "COL" "CRI" "CUB" "CYP" "DZA" "EGY" "FJI" "GHA"
 [97] "GIN" "GNQ" "HND" "HRV" "IND" "IRN" "JOR" "KGZ" "KWT" "LBN" "LBY" "LKA" "LVA" "MAR" "MDG" "MMR"
[113] "MOZ" "MUS" "MYT" "NAM" "NIC" "PAN" "PHL" "PRK" "SAU" "SRB" "TGO" "TUN" "TUR" "URY" "WSM" "ZWE"
[129] "AFG" "MKD" "PYF" "GRL" "CPV" "GIB" "UZB" "DJI" "GAB" "NCL" "SEN" "SPM" "TCD" "ECU" "LCA" "GUM"
[145] "KHM" "SLB" "TJK" "VGB" "BEN" "BLZ" "GNB" "IRQ" "KEN" "LBR" "MNG" "MNP" "PLW" "PRY" "VUT" "MNE"
[161] "STP" "TLS" "VEN" "IOT" "LAO" "YEM" "BHS" "CYM" "SLV" "SXM" "BWA" "LSO" "SWZ" "ZMB" "SYC" "VCT"
[177] "BMU" "COM" "PNG" "SOM" "TON" "TZA" "MLI" "BFA" "SLE" "GMB" "MRT" "NER" "RWA" "UGA" "SYR" "ETH"
[193] "FSM" "GUY" "KIR" "MWI" "NPL" "PSE" "CAF" "BLM" "TCA" "MHL" "WLF" "KNA"

Source Country:
Show in New Window
  [1] "RUS"     "ARG"     "BRA"     "CHL"     "unknown" "ARM"     "ITA"     "ESP"     "GEO"    
 [10] "NOR"     "AUS"     "NZL"     "USA"     "CHN"     "TWN"     "PHL"     "KOR"     "VNM"    
 [19] "NAM"     "MMR"     "IDN"     "ZAF"     "BGD"     "BEL"     "DNK"     "NLD"     "BGR"    
 [28] "FRA"     "GRC"     "MAR"     "TUR"     "LTU"     "BLR"     "POL"     "ISR"     "ISL"    
 [37] "LVA"     "EST"     "GBR"     "CAN"     "URY"     "UKR"     "IND"     "KAZ"     "ECU"    
 [46] "DEU"     "IRL"     "FIN"     "PER"     "THA"     "JPN"     "COL"     "GUY"     "SPM"    
 [55] "PAK"     "PRT"     "SGP"     "HKG"     "HND"     "SUR"     "MEX"     "SWE"     "GHA"    
 [64] "SEN"     "LKA"     "MYS"     "GRL"     "FSM"     "MDV"     "MHL"     "PNG"     "VUT"    
 [73] "FJI"     "COK"     "MUS"     "OMN"     "PRK"     "KEN"     "TZA"     "YEM"     "MOZ"    
 [82] "BRN"     "GTM"     "KHM"     "BEN"     "ARE"     "MDG"     "IRN"     "MRT"     "DOM"    
 [91] "GMB"     "PAN"     "CYP"     "CZE"     "HUN"     "AUT"     "ROU"     "SYC"     "JOR"    
[100] "FLK"     "BLZ"     "CPV"     "CUW"     "CIV"     "MLT"     "MYT"     "SHN"     "HRV"    
[109] "DZA"     "TUN"     "NIC"     "SVK"     "VEN"     "ATF"     "BHS"     "CUB"     "NGA"    
[118] "ALB"     "WSM"     "SLB"     "SAU"     "CRI"     "GIN"     "TUV"     "BHR"     "CHE"    
[127] "KWT"     "UGA"     "EGY"     "IOT"     "ZMB"     "VGB"     "KIR"     "SLV"     "LBY"    
[136] "GNQ"     "IRQ"     "TTO"     "SVN"     "MNG"     "AGO"     "JAM"     "AZE"     "SLE"    
[145] "LBN"     "SRB"     "LAO"     "ASM"     "GRD"     "PYF"     "BRB"     "COG"     "BIH"    
[154] "GNB"     "ATG"     "COM"     "LBR"     "GAB"     "TON"     "UZB"     "MKD"     "VCT"    
[163] "SOM"     "MAC"     "NCL"     "BOL"     "KGZ"

![ISO 3 Codes](https://www.researchgate.net/profile/Chahir-Zaki/publication/23779008/figure/tbl7/AS:669253044801551@1536573768865/List-of-countries-by-code-iso-3.png)

Foreign Export = Selling goods outside a country's borders
Domestic Export = goods originated from exporting country 
Error Export =

```{r}
artis_12_14 <- artis_russia %>%
  filter(year == 2012:2014)
# 2014 ends around row 153,000

artis_14_16 <- artis_russia %>%
  filter(year == 2014:2016)

aquaculture_12_14 <- artis_russia %>% 
  filter(year == 2012:2014) %>%
  filter(method == "aquaculture")

aquaculture_14_16 <- artis_russia %>% 
  filter(year == 2014:2016) %>%
  filter(method == "aquaculture")

capture_12_14 <- artis_russia %>% 
  filter(year == 2012:2014) %>%
  filter(method == "capture")

capture_14_16 <- artis_russia %>% 
  filter(year == 2014:2016) %>%
  filter(method == "capture")

artis_12_14_top_10 <- artis_12_14 %>%
  filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
    mutate(hs_4digit = substr(hs6, 1, 4)) %>%
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

artis_12_14_top_10_with_years <- artis_12_14 %>%
  filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year, method) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>%
    filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "NLD" | importer_iso3c == "JPN" | importer_iso3c == "BLR" | importer_iso3c == "NGA" | importer_iso3c == "USA" | importer_iso3c == "DEU" | importer_iso3c == "THA" | importer_iso3c == "KAZ")

artis_14_16_top_10 <- artis_14_16 %>%
  filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
    mutate(hs_4digit = substr(hs6, 1, 4)) %>%
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

artis_14_16_top_10_with_years <- artis_14_16 %>%
  filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
#    mutate(hs_4digit = substr(hs6, 1, 4)) %>%
  group_by(importer_iso3c, year, method) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>%
    #slice_max(order_by = sum, n=10)
  filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "JPN" | importer_iso3c == "NLD" | importer_iso3c == "BLR" | importer_iso3c == "FRA" | importer_iso3c == "NGA" | importer_iso3c == "NOR" | importer_iso3c == "POL" | importer_iso3c == "USA")

```

Aquaculture subsets
```{r}
aquaculture_12_14_top10 <- aquaculture_12_14 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

aquaculture_12_14_top10_years <- aquaculture_12_14 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "KOR" | importer_iso3c == "JPN" | importer_iso3c == "BLR" | importer_iso3c == "CHN" | importer_iso3c == "KAZ" | importer_iso3c == "HKG" | importer_iso3c == "USA" | importer_iso3c == "UKR" | importer_iso3c == "POL" | importer_iso3c == "DEU")

aquaculture_14_16_top10 <- aquaculture_14_16 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

aquaculture_14_16_top10_years <- aquaculture_14_16 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "BLR" | importer_iso3c == "JPN" | importer_iso3c == "KAZ" | importer_iso3c == "UKR" | importer_iso3c == "VNM" | importer_iso3c == "LTU" | importer_iso3c == "USA" | importer_iso3c == "DEU")
```

Capture Subsets
```{r}
capture_12_14_top10 <- capture_12_14 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

capture_12_14_top10_years <- capture_12_14 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "NLD" | importer_iso3c == "JPN" | importer_iso3c == "BLR" | importer_iso3c == "NGA" | importer_iso3c == "USA" | importer_iso3c == "DEU" | importer_iso3c == "THA" | importer_iso3c == "KAZ")

capture_14_16_top10 <- capture_14_16 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

capture_14_16_top10_years <- capture_14_16 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "JPN" | importer_iso3c == "NLD" | importer_iso3c == "BLR" | importer_iso3c == "FRA" | importer_iso3c == "NGA" | importer_iso3c == "NOR" | importer_iso3c == "POL" | importer_iso3c == "USA")

tmp <- artis_russia %>%
  filter(exporter_iso3c == "RUS") %>%
  group_by(importer_iso3c, exporter_iso3c, year, product_weight_t) %>%
  mutate(change = case_when(
    product_weight > 0 ~ "increased",
    product_weight <= 0 ~ "decreased"
  ))

```

```{r}
colnames(artis_12_14_top_10) <- c("Importer", "2012-2014 Product Weight (t)")
colnames(artis_14_16_top_10) <- c("Importer", "2014-2016 Product Weight (t)")
Top_10_12_16 <- full_join(artis_12_14_top_10, artis_14_16_top_10, by = "Importer") %>%
  arrange(desc("2012-2014 Product Weight (t)", "2014-2016 Product Weight (t)"))

kable(Top_10_12_16, caption = "Top 10 Importers of Russian Goods")
```
Doesn't work yet- can I determine which countries' exports to Russia increased/decreased, which countries' Russian imports increased/decreased, and how the method was affected?

Do that with each 12-14, 14-16 data set, and then join data sets for total?
```{r}
tmp <- aquaculture_12_14 %>%
  group_by(importer_iso3c, exporter_iso3c, year) %>%
  summarise(product_weight = sum(product_weight_t))

artis_percentages <- artis_russia %>%
  group_by(importer_iso3c, exporter_iso3c, method, year) %>%
  summarise(product_weight = sum(product_weight_t)) %>%
  mutate(method_percentage = percent(product_weight/method))
```

```{r}

ggplot()+
  geom_area(artis_12_14_top_10_with_years, mapping = aes(x= year, y= sum, fill= importer_iso3c))+
  geom_area(artis_14_16_top_10_with_years, mapping = aes(x= year, y= sum, fill= importer_iso3c))  +
  facet_wrap(~method)

```
```{r}

```

```{r}
ggplot(artis_14_16_aquaculture %>%
         filter(importer_iso3c == "RUS"))+
  geom_col(aes(x = sci_name, y = product_weight_t, fill = environment))+
  facet_wrap(~year)+
  theme(axis.text.x = element_text(angle = 90))

ggplot(artis_12_14_aquaculture %>%
         filter(importer_iso3c == "RUS"))+
  geom_col(aes(x = sci_name, y = product_weight_t, fill = environment))+
  facet_wrap(~year)+
  theme(axis.text.x = element_text(angle = 90))

ggplot(artis_12_14_exporter_russia)+
  geom_line(aes(x= year, y= product_weight_t, fill= hs_4digit))

ggplot(artis_12_14)+
  geom_point(aes(y= product_weight_t, x = live_weight_t, fill = method))
```

```{r}
russia <- ne_states(c(country = "Russia", "Ukraine"), returnclass = "sf")

Crimea <- data.frame(long = 35.382435, lat = 45.031933)

ggplot() +
  geom_sf(data = russia, color = "black", fill = "darkseagreen", size= 1) +
  coord_sf(xlim = c(20.0, 60.0))+
  geom_point(data = Crimea, color = "orangered", shape = 18, fill= "red", size = 5, aes(x = long, y = lat))+
  theme(panel.grid.major = element_line(color = "lavenderblush4")) +
  labs(title = "Crimean Peninsula")+
  xlab("Longitude")+
  ylab("Latitude")+
  panel_border(color= "black", size = 2)+
  theme(panel.background = element_rect(fill = "royalblue"))+
  north(russia, location = "bottomright", symbol = 4,   scale= .03)+
scalebar(russia, location = "bottomleft", transform = TRUE, dist_unit = "km", dist = 10, st.size = 5)

#xlim = c(-76.5, -77.5), ylim = c(38.7, 39)
#, anchor = c(x= -77.5, y = 38.75

```

Not used:
```{r}
artis_12_13 <- artis_russia %>%
  filter(year == 2012:2013)

artis_14 <- artis_russia %>%
  filter(year == 2014)

artis_15_16 <- artis_russia %>%
  filter(year == 2015:2016)

aquaculture_12_13 <- artis_12_13 %>% 
  filter(year == 2012:2013) %>%
  filter(method == "aquaculture")

aquaculture_12_13_top10 <- aquaculture_12_13 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

aquaculture_12_13_top10_years <- aquaculture_12_13 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "JPN" | importer_iso3c == "KOR" | importer_iso3c == "BLR" | importer_iso3c == "CHN" | importer_iso3c == "DEU" | importer_iso3c == "UKR" | importer_iso3c == "KAZ" | importer_iso3c == "POL" | importer_iso3c == "EST" | importer_iso3c == "USA")

capture_12_13 <- artis_russia %>% 
  filter(year == 2012:2013) %>%
  filter(method == "capture")

capture_12_13_top10 <- capture_12_13 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

capture_12_13_top10_years <- capture_12_13 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "KOR" | importer_iso3c == "CHN" | importer_iso3c == "JPN" | importer_iso3c == "NLD" | importer_iso3c == "NGA" | importer_iso3c == "USA" | importer_iso3c == "BLR" | importer_iso3c == "NOR" | importer_iso3c == "FRA" | importer_iso3c == "DEU")

aquaculture_14 <- artis_russia %>% 
  filter(year == 2014) %>%
  filter(method == "aquaculture")

aquaculture_14_top10 <- aquaculture_14 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

aquaculture_14_top10_years <- aquaculture_14 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "KOR" | importer_iso3c == "CHN" | importer_iso3c == "JPN" | importer_iso3c == "BLR" | importer_iso3c == "KAZ" | importer_iso3c == "HKG" | importer_iso3c == "VNM" | importer_iso3c == "UKR" | importer_iso3c == "DEU" | importer_iso3c == "USA")

capture_14 <- artis_russia %>% 
  filter(year == 2014) %>%
  filter(method == "capture")

capture_14_top10 <- capture_14 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

capture_14_top10_years <- capture_14 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "NLD" | importer_iso3c == "JPN" | importer_iso3c == "BLR" | importer_iso3c == "NGA" | importer_iso3c == "USA" | importer_iso3c == "DEU" | importer_iso3c == "POL" | importer_iso3c == "FRA")

artis_15_16 <- artis_russia %>%
  filter(year == 2015:2016)

aquaculture_15_16 <- artis_russia %>% 
  filter(year == 2015:2016) %>%
  filter(method == "aquaculture")

aquaculture_15_16_top10 <- aquaculture_15_16 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

aquaculture_15_16_top10_years <- aquaculture_15_16 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "JPN" | importer_iso3c == "KOR" | importer_iso3c == "BLR" | importer_iso3c == "CMR" | importer_iso3c == "KAZ" | importer_iso3c == "UKR" | importer_iso3c == "CHN" | importer_iso3c == "LTU" | importer_iso3c == "DEU" | importer_iso3c == "USA")

capture_15_16 <- artis_russia %>% 
  filter(year == 2015:2016) %>%
  filter(method == "capture")

capture_15_16_top10 <- capture_15_16 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
    slice_max(order_by = sum, n=10)

capture_15_16_top10_years <- capture_15_16 %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>% 
  group_by(importer_iso3c, year) %>%
  summarise(sum = sum(product_weight_t)) %>%
      arrange(desc(sum)) %>% 
  filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "NLD" | importer_iso3c == "JPN" | importer_iso3c == "BLR" | importer_iso3c == "NGA" | importer_iso3c == "UKR" | importer_iso3c == "CMR" | importer_iso3c == "KAZ" | importer_iso3c == "VNM")

```

### 2022-06-23 analyze.Rmd
Visualized artis demo

---
title: "ARTIS S-net Overview"
output: html_document
date: '2022-06-21'
author: "Jessica Gephart and Rahul Agrawal Bejarano"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Reset Environment to start with an empty workspace
rm(list=ls())

library(tidyverse)
library(countrycode)
library(kableExtra)

# POINT THESE paths to folders and files in your local computer
# File Path to the folder where your data lives
datadir <- "data"
# File Path to the folder where you want to ouput results
outdir <- "Outputs"

# File name of the data you want to use
artis_snet_filename <- "20220616_josephbarnes_ARTIS_snet.csv"

```

```{r include=FALSE}

artis <- read.csv(file.path(datadir, artis_snet_filename))
```

## Timeseries

### Creating a timeseries line graph

Below is a code sample for creating timeseries by year based on seafood product weights.
```{r }
# Function that creates a timeseries
# INPUT:
#   - df: A data frame with a Year column and Product weight
#   x_var and y_var need to be passed in tidyverse style as variables
#   - x_var: col variable that will be plotted on the x axis (Group by var)
#   - y_var: col variable that will be plotted on the y axis (Summarize var)
# OUTPUTS:
#   - p: Timeseries plot
create_timeseries_line <- function(df, x_var, y_var, plot_title, x_title, y_title) {
  timeseries <- df %>%
  group_by({{ x_var }}) %>%
  summarize(quantity = sum({{ y_var }}))

  p <- ggplot(timeseries) +
    geom_line(aes(x={{ x_var }}, y=quantity)) +
    labs(x=x_title, y=y_title, title=plot_title)

  return(list(p, timeseries))
}

timeseries_results <- artis %>% 
  create_timeseries_line(x_var=year, y_var=product_weight_t,
                              "Timeseries of ARTIS S-net HS12", 
                              "Year", "Quantity (tonnes)")

timeseries_p <- timeseries_results[[1]]
timeseries_df <- timeseries_results[[2]]

rm(timeseries_results)

plot(timeseries_p)

# Use the code below to get a visual representation of the timeseries as a dataframe
# timeseries_df %>%
#   kable() %>%
#   kable_styling(full_width=FALSE)

```

### Creating a stacked line graph based on Species, HS codes, Trade Partners
```{r}
# Creates a stacked graph based on a time variable and stacking variable
# INPUTS
#   - df: dataframe containing data to be visualized
#   - time_var: X axis variables
#   - stack_var: variable to create stacking groups
#   - q_var:Y axis variable
#   - prop_flow_cutoff: Minimum proportion cutoff, 
#       - all groups below this cutoff get grouped into an "Other" group
# OUTPUTS:
#   - p: plot of a stacked timeseries
create_stacked_graph <- function(df, time_var, stack_var, q_var, 
                                 prop_flow_cutoff=0.05, 
                                 plot_title="", x_title="", y_title="") {

  stacked <- df %>%
    group_by({{ time_var }}, {{ stack_var }}) %>%
    summarize(quantity = sum({{ q_var }})) %>%
    ungroup() %>%
    group_by({{ time_var }}) %>%
    mutate(total_by_time = sum(quantity)) %>%
    mutate(prop_flow = quantity / total_by_time) %>%
    mutate(common_name = case_when(
      prop_flow < prop_flow_cutoff ~ "Other",
      TRUE ~ as.character({{ stack_var }})
    )) %>%
    ungroup() %>%
    group_by({{ time_var }}, common_name) %>%
    summarize(quantity = sum(quantity)) %>%
    ungroup()

  year_grid <- expand_grid(common_name=unique(stacked$common_name),
                           year=unique(stacked %>% pull({{ time_var }})))

  stacked <- stacked %>%
    full_join(year_grid) %>%
    mutate(quantity = case_when(
      is.na(quantity) ~ 0,
      TRUE ~ as.numeric(quantity)
    ))

  p <- stacked %>%
    ggplot() +
    geom_area(aes(x={{ time_var }}, y=quantity, fill=common_name)) +
    scale_fill_viridis_d() +
    labs(x=x_title, y=y_title, title=plot_title, fill="Common Name") +
    theme_bw()

  return(list(p, stacked))
}
```

An example using species as the stacking group:
```{r message=FALSE}

species_stacked <- artis %>% 
  create_stacked_graph(year, SciName, product_weight_t, 
                            plot_title="Species breakdown over time", 
                            x_title="Year", y_title="Quantity (tonnes)")

species_p <- species_stacked[[1]]
species_df <- species_stacked[[2]]

rm(species_stacked)

plot(species_p)
```

An example using hs product codes as the stacking group:
```{r message=FALSE}

hs_stacked <- artis %>% 
       create_stacked_graph(year, hs6, product_weight_t, 
                            plot_title="Seafood product (by HS code) over time", 
                            x_title="Year", y_title="Quantity (tonnes)")

hs_p <- hs_stacked[[1]]
hs_df <- hs_stacked[[2]]

rm(hs_stacked)

plot(hs_p)
```

An example using exporter as the stacking group:
```{r message=FALSE}

exporter_stacked <- artis %>% 
       create_stacked_graph(year, exporter_iso3c, product_weight_t, 
                            plot_title="Exporters over time", 
                            x_title="Year", y_title="Quantity (tonnes)")

exporter_p <- exporter_stacked[[1]]
exporter_df <- exporter_stacked[[2]]

rm(exporter_stacked)

plot(exporter_p)
```

### 2022-08-11 Case Study Final Draft.Rmd
Case Study Final Draft is the RMD for the finished writeup. Russia Case Study under the hood includes the complete writeup, plus code for unused charts, tables, and vectors to find unused data, like species of each exporting country

---
title: "Effects of the 2014 Russian Annexation of Crimea on Russian Seafood Trade"
author: "Joseph Barnes"
date: "2022-06-28"
output:
  html_document:
    toc: yes
    df_print: paged
  word_document:
    toc: yes
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)

library(tidyverse)
library(lubridate)
library(formatR)
library(RColorBrewer)
library(viridis)
library(janitor)
library(reader)
library(ggplot2)
library(ggrepel)
library(ggpubr)

library(cli)
library(devtools)
library(tidyverse)
library(sf)
library(cowplot)   # for theme_map()
library(lwgeom) # for st_transform_proj
library(ggsn) # for adding north arrows and scale bar
library(rworldmap) # for getMap()
#library(spData) # for world data
library(rnaturalearth)
# library(rnaturalearthhires)
library(rnaturalearthdata) # supporting data, only install/load if prompted 
library(gtrendsR)
library(knitr)
library(readr)
library(stringr)
library(ggthemes)
library(kableExtra)
library(countrycode)
library(ggridges)
library(dplyr)
library(networkD3)
library(RColorBrewer)
library(forcats)
library(circlize)
```

```{r, include=FALSE}
artis_russia_2009_2019 <- read_csv("C:/Users/User/Documents/American University/Global Seafood Lab/case_study_russia/20220629_josephbarnes_ARTIS_snet.csv", 
     col_types = cols(year = col_number())) %>%
  filter(year %in% c(2009:2019)) %>%
    mutate(sanctions_towards_russia = case_when(
      importer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No"
    )) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No"))

```

```{r, include=FALSE, echo= FALSE}
artis_russia_2009_2019 <- clean_names(artis_russia_2009_2019)
artis_russia_2009_2019$hs6 <- str_pad(artis_russia_2009_2019$hs6, 6, pad = "0")

# str(artis_russia_2009_2019 %>%
# filter(year %in% 2010:2019)) # 487,324 x 14
# sort(unique(artis_russia_2009_2019$exporter_iso3c))
# sort(unique(artis_russia_2009_2019$importer_iso3c))
# unique(artis_russia_2009_2019$dom_source) # "foreign export"  "domestic export" "error export"  
# sort(unique(artis_russia_2009_2019$source_country_iso3c))
# unique(artis_russia_2009_2019$sci_name) # 1520
# unique(artis_russia_2009_2019$environment) # "marine"  "inland"  "unknown"
# unique(artis_russia_2009_2019$method) # "capture" "aquaculture" "unknown" 
# unique(artis_russia_2009_2019$hs_version) #HS 2, 7, 12

```

# Introduction

Russia began an annexation on Ukraine’s Crimean peninsula on March 18, 2014, sparking international tensions that imposed sanctions on Russia (Biersak, 2014). Sanctions included freezing Russian assets and capturing property to restrict Russian access to Western markets, aiming to cripple their banking, energy, and defense sectors; and banning exports to Russia of military technology and dual-use goods, including oil exploration and production equipment. (DeYoung; Christie). In response, Russia provided counter-sanctions as an agricultural embargo in 2014 that banned itself from importing food items, including seafood, from sanctioning nations (Wegren, 2018). With market data available from before and after the 2014 Annexation, this case study seeks to understand the seafood trade flow amid various embargoes and sanctions to better understand whose exports to Russia increased and whose decreased, and how much of that trade entered the market through third-party exporters to complete trades to and from Russia. Data from this case study can help predict market shifts and patterns to the current Ukrainian-Russian war that has seen similar sanctions and alliances rise up again.

```{r, echo=FALSE}
# russia <- ne_states(c(country = "Russia", "Ukraine", "Poland", "Belarus", "Moldova", "Romania"), returnclass = "sf")
# 
# Crimea <- data.frame(long = 35.382435, lat = 45.031933)
# 
# ggplot() +
#   geom_sf(data = russia, color = "black", fill = "darkseagreen")+ #size= 1) +
#   coord_sf(xlim = c(20.0, 60.0), ylim = c(40,60))+
#   geom_point(data = Crimea, color = "orangered", shape = 18, fill= "red", size = 5, aes(x = long, y = lat))+
#   theme(panel.grid.major = element_line(color = "lavenderblush4")) +
#   labs(title = "Crimean Peninsula")+
#   xlab("Longitude")+
#   ylab("Latitude")+
#   panel_border(color= "black", size = 2)+
#   theme(panel.background = element_rect(fill = "royalblue"))+
#   north(russia, location = "bottomright", symbol = 4,   scale= .03)+
# scalebar(russia, location = "bottomleft", transform = TRUE, dist_unit = "km", dist = 10, st.size = 5)

#  ylim = c(40,60)

#xlim = c(-76.5, -77.5), ylim = c(38.7, 39)
#, anchor = c(x= -77.5, y = 38.75

```

# Methods

Trade patterns from 2010 - 2019 were examined using the Aquatic Resource Trade in Species (ARTiS) database, tidied and visualized in R. ARTiS is also composed of Harmonized System (HS) data dating back to 1996, compiling updated seafood trade rosters every five years. HS includes a 4-digit code for a species categorization heading, species scientific names, and from which HS version the data comes from. Additional ARTiS data includes the production method (aquaculture or wild caught), the product and live weights (tons), and the year of the trade. The database was filtered for any seafood connection that was sourced in, exported to, or imported from Russia.

The data was subset into two time periods of fives years before the annexation (2010-2014) and five years after (2015-2019) Since many of the sanctions were implemented or put in force in the summer or later in 2014, 2015 counts as the first full year after the annexation that results could be seen.

Structure (Rows x Columns) | Exporters | Importers | Source Countries | Scientific Names
-------- | -------- | -------- | -------- | -------- 
487,324 x 14 | 115 | 212 | 180 | 1520

Countries are denoted with their 3-digit internationally standardized ISO code.

# Results

## Importers of Russian Seafood

The top 10 importers of Russian goods before (2010-2014) and after (2015-2019) the Crimean Annexation were garnered by subsetting the data by each time frame, and totaling the live weight for each importing country. These countries were manually input into a code to break up the live weight imports from Russia (exporter_iso3c == “RUS”) by year. The only country to drop as a top 10 importer after the 2014 Annexation was the United States, which seemingly stopped importing seafood products from Russia altogether.

```{r, include= FALSE, echo=FALSE}
# Subsetting data into top 10 importers of Russian goods between 2012-2014, and 2014-2016. First, data is vectored into the top 10 importers for each time frame, with live weight totaled between the three years. Using the 10 countries from those datasets, they are then manually imported into a code that groups by year, so that it lists the top 10 importing countries and their totals in each year.
# 
# ** 7/15/2022 Removed source == "RUS" because I just want Russian exports, it doesn't matter where they came from yet.

# tmp <- artis_russia_2009_2019 %>%
#   filter(year %in% 2015:2019) %>%
#  filter( exporter_iso3c == "RUS") %>%
#  group_by(importer_iso3c) %>%
#  summarise(sum = sum(live_weight_t))%>%
#  arrange(desc(sum))

artis_10_14_top_10_with_years <- artis_russia_2009_2019 %>%
  filter(year %in% 2010:2014, exporter_iso3c == "RUS") %>%
  group_by(importer_iso3c, year, method, sanctions_towards_russia) %>%
  summarise(live_weight = sum(live_weight_t)) %>%
     arrange(desc(live_weight)) %>%
    filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "NLD" | importer_iso3c == "JPN" | importer_iso3c == "BLR" | importer_iso3c == "UKR" | importer_iso3c == "DEU" | importer_iso3c == "FRA" | importer_iso3c == "USA" | importer_iso3c == "NGA")
artis_10_14_top_10_with_years$live_weight <-  round(artis_10_14_top_10_with_years$live_weight, digit = 2)

 artis_15_19_top_10_with_years <- artis_russia_2009_2019 %>%
   filter(year %in% 2015:2019, exporter_iso3c == "RUS") %>%
   group_by(importer_iso3c, year, method, sanctions_towards_russia) %>%
   summarise(live_weight = sum(live_weight_t)) %>%
       arrange(desc(live_weight)) %>%
   filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "NLD" | importer_iso3c == "JPN" | importer_iso3c == "BLR" | importer_iso3c == "NGA" | importer_iso3c == "UKR" | importer_iso3c == "FRA" | importer_iso3c == "KAZ" | importer_iso3c == "DEU")
artis_15_19_top_10_with_years$live_weight <-  round(artis_15_19_top_10_with_years$live_weight, digit = 2)
# 
# 
artis_10_19_top_importers <- artis_russia_2009_2019 %>%
  filter(year %in% 2010:2019) %>%
    filter(exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>%
  group_by(importer_iso3c, year, method, sanctions_towards_russia) %>%
  summarise(live_weight = sum(live_weight_t)) %>%
      arrange(desc(live_weight)) %>%
    filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "JPN" | importer_iso3c == "NLD" | importer_iso3c == "BLR" | importer_iso3c == "UKR" | importer_iso3c == "DEU" | importer_iso3c == "FRA" | importer_iso3c == "USA" | importer_iso3c == "KAZ" | importer_iso3c == "NGA" | importer_iso3c == "KAZ"| importer_iso3c == "DEU"| importer_iso3c == "UKR")
```

```{r, include=FALSE, echo=FALSE}
# tmp <- artis_russia_2009_2019 %>%
#     filter(year %in% 2015:2019, exporter_iso3c == "RUS", method == "capture") %>%
#   group_by(importer_iso3c) %>%
#   summarise(live_weight = sum(live_weight_t)) %>%
#       arrange(desc(live_weight))

top_importers_all_years <-
  full_join(
    artis_10_14_top_10_with_years %>% group_by(importer_iso3c) %>% summarise(live_weight = sum(live_weight)),
    artis_15_19_top_10_with_years %>% group_by(importer_iso3c) %>%
      summarise(live_weight = sum(live_weight)),
    by = "importer_iso3c"
  ) %>%
  full_join(
    artis_russia_2009_2019 %>%
      filter(
        year %in% 2010:2014,
        exporter_iso3c == "RUS",
        method == "aquaculture"
      ) %>%
      group_by(importer_iso3c, year) %>%
      summarise(live_weight = sum(live_weight_t)) %>%
      arrange(desc(live_weight))  %>%
      filter(
        importer_iso3c == "KOR" |
          importer_iso3c == "CHN" |
          importer_iso3c == "UKR" |
          importer_iso3c == "JPN" |
          importer_iso3c == "NLD" |
          importer_iso3c == "BLR" |
          importer_iso3c == "DEU" |
          importer_iso3c == "KAZ" |
          importer_iso3c == "GBR" |
          importer_iso3c == "MDA"
      ) %>% group_by(importer_iso3c) %>% summarise(live_weight = sum(live_weight)),
    by = "importer_iso3c"
  ) %>%
  full_join(
    artis_russia_2009_2019 %>%
      filter(
        year %in% 2015:2019,
        exporter_iso3c == "RUS",
        method == "aquaculture"
      ) %>%
      group_by(importer_iso3c, year) %>%
      summarise(live_weight = sum(live_weight_t)) %>%
      arrange(desc(live_weight)) %>%
      filter(
        importer_iso3c == "CHN" |
          importer_iso3c == "KOR" |
          importer_iso3c == "BLR" |
          importer_iso3c == "UKR" |
          importer_iso3c == "JPN" |
          importer_iso3c == "KAZ" |
          importer_iso3c == "FRA" |
          importer_iso3c == "VNM" |
          importer_iso3c == "AZE" |
          importer_iso3c == "MDA"
      ) %>% group_by(importer_iso3c) %>% summarise(live_weight = sum(live_weight)),
    by = "importer_iso3c"
  ) %>%
  full_join(
    artis_russia_2009_2019 %>%
      filter(year %in% 2010:2014, exporter_iso3c == "RUS", method == "capture") %>%
      group_by(importer_iso3c, year) %>%
      summarise(live_weight = sum(live_weight_t)) %>%
      arrange(desc(live_weight)) %>%
      filter(
        importer_iso3c == "CHN" |
          importer_iso3c == "KOR" |
          importer_iso3c == "NLD" |
          importer_iso3c == "JPN" |
          importer_iso3c == "BLR" |
          importer_iso3c == "DEU" |
          importer_iso3c == "UKR" |
          importer_iso3c == "FRA" |
          importer_iso3c == "NGA" |
          importer_iso3c == "USA"
      ) %>% group_by(importer_iso3c) %>% summarise(live_weight = sum(live_weight)),
    by = "importer_iso3c"
  ) %>%
  full_join(
    artis_russia_2009_2019 %>%
      filter(year %in% 2015:2019, exporter_iso3c == "RUS", method == "capture") %>%
      group_by(importer_iso3c, year) %>%
      summarise(live_weight = sum(live_weight_t)) %>%
      arrange(desc(live_weight)) %>%
      filter(
        importer_iso3c == "CHN" |
          importer_iso3c == "KOR" |
          importer_iso3c == "NLD" |
          importer_iso3c == "JPN" |
          importer_iso3c == "BLR" |
          importer_iso3c == "NGA" |
          importer_iso3c == "UKR" |
          importer_iso3c == "FRA" |
          importer_iso3c == "DEU" |
          importer_iso3c == "KAZ"
      ) %>% group_by(importer_iso3c) %>% summarise(live_weight = sum(live_weight)),
    by = "importer_iso3c"
  )
colnames(top_importers_all_years) <-
  c(
    "Importer",
    "Live Weight 2010-2014 (Tons)",
    "Live Weight 2015-2019 (Tons)",
    "Aquaculture Live Weight 2010-2014 (Tons)",
    "Aquaculture Live Weight 2015-2019 (Tons)",
    "Capture Live Weight 2010-2014 (Tons)",
    "Capture Live Weight 2015-2019 (Tons)"
  )

tmp <- top_importers_all_years %>%
  select(-c(`Aquaculture Live Weight 2010-2014 (Tons)`:`Capture Live Weight 2015-2019 (Tons)`)) %>%
  slice(-c(12:15)) %>%
  arrange(desc(`Live Weight 2010-2014 (Tons)`))

  kable(tmp, caption = "Top 10 Importers of Russian Goods")
```

```{r, echo=FALSE}
  kable(tmp, caption = "Top 10 Importers of Russian Goods")
```

Germany, The United States, and South Korea all decreased their imports from Russia after the annexation, although only Germany and the United States had imposed sanctions on Russia and faced the agricultural embargo. Kazakhstan took the place of the USA in the top 10 importers after the annexation, but it was not enough to make up the difference from losses by the USA.

```{r, echo=FALSE, include = FALSE}
kable(top_importers_all_years, caption = "Top 10 Importers of Russian Goods")
```

Due to Russia's agricultural embargo counter-sanction, Russia ramped up domestic good production, primarily in capture fisheries. In most cases, importing countries bought more capture products than aquaculture, with the exceptions being Great Britain, Moldova, Azerbaijan, and Vietnam. Great Britain stopped importing goods from Russia after 2014, and neither Moldova, Azerbaijan, nor Vietman imported capture seafood in either time period. Azerbaijan and Vietnam did not import any aquaculture products prior to 2014, but did after.

```{r, echo=FALSE}
ggplot(artis_10_19_top_importers %>%
         group_by(importer_iso3c, year, sanctions_towards_russia)%>%
         summarise(live_weight = sum(live_weight)), aes(x= year, y= live_weight, fill = importer_iso3c))+
  geom_area()+
  facet_wrap(~sanctions_towards_russia)+
  ggtitle("Russian Seafood Importers", subtitle = "Faceted by Countries that Imposed Sanctions on Russia")+
  xlab("Year")+
  ylab("Live Weight (tons)") +
  geom_vline(xintercept=2014)  +
  guides(fill = guide_legend(title = "Importer of Russian Seafood"))+
  scale_x_continuous(n.breaks = 9)+
  theme(axis.text.x = element_text(angle = 90))+
  scale_y_continuous(breaks = seq(0,4000000,by = 500000))
```

This chart shows the top countries that imported the most seafood from Russia from 2010 to 2019, displaying the changes in top countries and import amounts before and after Annexation. Countries that did not implement sanctions against Russia in or around 2014 saw a sharp decrease in Russian seafood imports in 2014, followed by an immediate increase in the years to follow. South Korea's trade increased but by 2019, fell to around 2010 levels, lowering the total imports overall. Countries that did impose sanctions, on the other hand, increased their Russian imports into 2014. Although trade fell slightly in the years after, it still remained relatively constant to 2013 levels.

```{r, echo = FALSE, fig.width= 8}
full_join(artis_russia_2009_2019 %>%
  filter(year %in% 2010:2014, exporter_iso3c == "RUS") %>%
   group_by(importer_iso3c, sanctions_towards_russia) %>%
   summarise(`Live weight 2010-2014` = sum(live_weight_t)),
  artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019, exporter_iso3c == "RUS") %>%
    group_by(importer_iso3c, sanctions_towards_russia) %>%
    summarise(`Live weight 2015-2019` = sum(live_weight_t)), by = "importer_iso3c") %>%
  pivot_longer(names_to = "time_period", values_to = "live_weight", 
               cols = c(`Live weight 2010-2014`,`Live weight 2015-2019`)) %>%
  arrange(desc(live_weight)) %>%
  filter(importer_iso3c == "CHN" | importer_iso3c == "KOR" | importer_iso3c == "JPN" | importer_iso3c == "NLD" | importer_iso3c == "BLR" | importer_iso3c == "UKR" | importer_iso3c == "DEU" | importer_iso3c == "FRA" | importer_iso3c == "USA" | importer_iso3c == "KAZ" | importer_iso3c == "NGA" | importer_iso3c == "KAZ"| importer_iso3c == "DEU"| importer_iso3c == "UKR") %>%
  ggplot(aes(x= time_period, y = live_weight, color = importer_iso3c, group = importer_iso3c))+
  geom_line() +
  geom_point() +
#  scale_color_discrete(, discrete = TRUE)+
  # scale_colour_brewer()+
  scale_color_brewer(palette = "Paired")+
  xlab("")+
  ylab("Live Weight (Tons)")+ 
  ggtitle("Total Russian Imports Before and After Annexation", subtitle = "Countries Importing Seafood from Russia Faceted by if they Imposed Sanctions on Russia") +
  guides(col = guide_legend(title = "Russian Seafood Importers"))+
  scale_y_continuous(breaks = seq(0, 8000000, by = 1000000))+
  scale_y_continuous(labels = scales::comma)+
#  geom_segment(x = as.numeric(time_period), xend = as.numeric(time_period), y = 0, yend = 1000000)+
  facet_wrap(~sanctions_towards_russia.x)+
  theme(axis.text.x = element_text(angle = 10))
```

Germany, USA, and South Korea all decreased their total imports after the 2014 Annexation, though only Germany and the United States implemented sanctions against Russia following the 2014 Annexation (Fackler). South Korea joined the sanctions in the Russian-Ukraine War in 2022 (North Macedonia).

```{r, echo=FALSE}
top_importers_all_years %>%
  select(-c(`Aquaculture Live Weight 2010-2014 (Tons)`:`Capture Live Weight 2015-2019 (Tons)`))%>%
  slice(-c(11:15)) %>%
  replace(is.na(.), 0) %>%
  mutate(`Percent Change` = (`Live Weight 2015-2019 (Tons)` - `Live Weight 2010-2014 (Tons)`) / abs(`Live Weight 2015-2019 (Tons)`) * 100) %>%
      mutate(sanctions_towards_russia = case_when(
      Importer %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No"
    )) %>%
  ggplot(aes(x = Importer, y = `Percent Change`)) +
  geom_segment(mapping = aes( x = 0, xend = `Percent Change`, y = Importer, yend = Importer, color = sanctions_towards_russia)) +
  geom_point(mapping = aes(x= `Percent Change`, y = Importer, color = sanctions_towards_russia))+
  xlab("Percent Change")+
  ylab("Importers")+
  ggtitle("Percent Change in Imports from Russia After Crimean Annexation") +
  guides(col = guide_legend(title = "Imposed Sanctions Against Russia"))+
      geom_vline(xintercept = 0)

```

Some importing nations had more drastic changes in imports before and after the Annexation than others. The USA and Germany, for example, saw over a 50% decrease in imports from Russia, while other countries like the Netherlands and Nigeria experienced a 50% increase in Russian imports.

## Exporters to Russia
```{r, include=FALSE, echo=FALSE}
# Countries exporting to Russia (importer == RUS)

# tmp <- artis_russia_2009_2019 %>%
#     filter(year %in% 2015:2019, importer_iso3c == "RUS") %>%
#   group_by(exporter_iso3c) %>%
#   summarise(live_weight = sum(live_weight_t)) %>%
#       arrange(desc(live_weight))

top_exporters_all_years <-
  full_join(artis_russia_2009_2019 %>%
    filter(year %in% 2010:2014, importer_iso3c == "RUS") %>%
  group_by(exporter_iso3c) %>%
  summarise(live_weight = sum(live_weight_t)) %>%
  filter(exporter_iso3c == "NOR" |
          exporter_iso3c == "CHN" |
          exporter_iso3c == "ISL" |
          exporter_iso3c == "MAR" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "LVA" |
          exporter_iso3c == "VNM" |
          exporter_iso3c == "UKR" |
          exporter_iso3c == "CHL" |
          exporter_iso3c == "BLR"
      ) %>% group_by(exporter_iso3c) %>% summarise(live_weight = sum(live_weight)),
    artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019, importer_iso3c == "RUS") %>%
  group_by(exporter_iso3c) %>%
  summarise(live_weight = sum(live_weight_t)) %>%
  filter(exporter_iso3c == "CHN" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "MRT" |
          exporter_iso3c == "CHL" |
          exporter_iso3c == "BLR" |
          exporter_iso3c == "VNM" |
          exporter_iso3c == "GRL" |
          exporter_iso3c == "IND" |
          exporter_iso3c == "MAR" |
          exporter_iso3c == "THA"
      ) %>% group_by(exporter_iso3c) %>% summarise(live_weight = sum(live_weight)),
  by = "exporter_iso3c") %>%
  arrange(desc(live_weight.x))

colnames(top_exporters_all_years) <-
  c(
    "Exporter",
    "Live Weight 2010-2014 (Tons)",
    "Live Weight 2015-2019 (Tons)")

artis_10_19_top_exporters <- artis_russia_2009_2019 %>%
  filter(year %in% 2010:2019) %>%
    filter(importer_iso3c == "RUS") %>%
  group_by(exporter_iso3c, year, method, exporter_sanctions_towards_russia) %>%
  summarise(live_weight = sum(live_weight_t)) %>%
      arrange(desc(live_weight)) %>%
    filter(exporter_iso3c == "NOR" |
          exporter_iso3c == "CHN" |
          exporter_iso3c == "ISL" |
          exporter_iso3c == "MAR" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "LVA" |
          exporter_iso3c == "VNM" |
          exporter_iso3c == "UKR" |
          exporter_iso3c == "CHL" |
          exporter_iso3c == "BLR" | 
          exporter_iso3c == "MRT" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "BLR" |
          exporter_iso3c == "IND" |
          exporter_iso3c == "GRL" |
          exporter_iso3c == "THA" )

```

```{r, echo=FALSE}
kable(top_exporters_all_years, caption = "Top 10 Exporters to Russia")
```

Top seafood exporters to Russia include China, Iceland, Latvia, Morocco, Norway, and Ukraine, which all decreased total exports in the five years following the 2014 Annexation. Latvia, Iceland, Norway, and Ukraine stopped exporting to Russia completely due to the embargo. In their place, Greenland, India, Mauritania, and Thailand rose to the top 10 exporters to Russia. These replacements also did not make up the difference from the lost tonnage of Iceland, Latvia, Norway, and Ukraine.

```{r, echo=FALSE, message=FALSE}

ggplot(artis_10_19_top_exporters %>%
         group_by(exporter_iso3c, year, exporter_sanctions_towards_russia)%>%
         summarise(live_weight = sum(live_weight)), aes(x= year, y= live_weight, fill = exporter_iso3c))+
  geom_area()+
  facet_wrap(~exporter_sanctions_towards_russia)+
  ggtitle("Seafood Exporters to Russia", subtitle = "Faceted by if Counter-Sanction Embargo was Imposed")+
  xlab("Year")+
  ylab("Live Weight (Tons)") +
  geom_vline(xintercept=2014)  +
  guides(fill = guide_legend(title = "Exporter to Russia"))+
  scale_x_continuous(n.breaks = 10)+
  theme(axis.text.x = element_text(angle = 90))+
  scale_y_continuous(breaks = seq(0,1000000,by = 200000))+
  scale_y_continuous(labels = scales::comma)

```

China’s total exports decreased, but it seems that its rate of exports increased. Countries that did not impose sanctions initially saw dips in their exports to Russia, but they did pick back up in most cases. Exporters who were counter-sanctioned with the agricultural embargo saw export decreases to 0, except for Denmark, whose exports greatly increased after the Annexation, nearly tripling despite the embargo.

```{r, echo=FALSE, fig.width=6}
full_join(artis_russia_2009_2019 %>%
  filter(year %in% 2010:2014, importer_iso3c == "RUS") %>%
   group_by(exporter_iso3c, exporter_sanctions_towards_russia) %>%
   summarise(`Live weight 2010-2014` = sum(live_weight_t)),
  artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019, importer_iso3c == "RUS") %>%
    group_by(exporter_iso3c, exporter_sanctions_towards_russia) %>%
    summarise(`Live weight 2015-2019` = sum(live_weight_t)), by = "exporter_iso3c") %>%
  pivot_longer(names_to = "time_period", values_to = "live_weight", 
               cols = c(`Live weight 2010-2014`,`Live weight 2015-2019`)) %>%
  arrange(desc(live_weight)) %>%
    filter(exporter_iso3c == "NOR" |
          exporter_iso3c == "CHN" |
          exporter_iso3c == "ISL" |
          exporter_iso3c == "MAR" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "LVA" |
          exporter_iso3c == "VNM" |
          exporter_iso3c == "UKR" |
          exporter_iso3c == "CHL" |
          exporter_iso3c == "BLR" | 
          exporter_iso3c == "MRT" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "BLR" |
          exporter_iso3c == "IND" |
          exporter_iso3c == "GRL" |
          exporter_iso3c == "THA" ) %>%
  ggplot(aes(x= time_period, y = live_weight, color = exporter_iso3c, group = exporter_iso3c))+
  geom_line() +
  geom_point() +
 # scale_color_brewer(palette = "Paired")+
  xlab("")+
  ylab("Live Weight (Tons)")+ 
  ggtitle("Total Exports Before and After Annexation", subtitle = "Countries Exporting Seafood to Russia Faceted by Russian Embargo Counter-Sanction") +
 guides(col = guide_legend(title = "Russian Seafood Exporters"))+
   scale_y_continuous(breaks = seq(0, 2000000, by = 2000000))+
  scale_y_continuous(labels = scales::comma)+  
#  geom_segment(x = as.numeric(time_period), xend = as.numeric(time_period), y = 0, yend = 1000000)+
  facet_wrap(~exporter_sanctions_towards_russia.x)+
    theme(axis.text.x = element_text(angle = 10))

```

Despite the initial dip in exports after the annexation, many countries' exports still increased overall between the two time periods. China and Morocco, in the countries who did not impose sanctions, saw their total exports fall, as did each country affected by the embargo, except for Denmark.
```{r, echo=FALSE}
top_exporters_all_years %>%
  replace(is.na(.), 0) %>%
  mutate(`Percent Change` = (`Live Weight 2015-2019 (Tons)` - `Live Weight 2010-2014 (Tons)`) / abs(`Live Weight 2015-2019 (Tons)`) * 100) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      Exporter %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "yes",
      TRUE ~ "no"
    )) %>%
  ggplot() +
  geom_segment(mapping = aes( x = 0, xend = `Percent Change`, y = Exporter, yend = Exporter, color = exporter_sanctions_towards_russia)) +
  geom_point(mapping = aes(x= `Percent Change`, y = Exporter, color = exporter_sanctions_towards_russia))+
  xlab("Percent Change")+
  ylab("Exporters")+
  ggtitle("Percent Change in Exports to Russia After Crimean Annexation") +
  guides(col = guide_legend(title = "Sanctions Imposed by Russia"))+
      geom_vline(xintercept = 0)
```

China's exports to Russia briefly decreased, but was on an upward trend. All countries with an embargo decreased their exports to 0, except for Denmark. Every other country that did not have the embargo increased their exports to Russia, except for Morocco and China.

```{r, include= FALSE, echo=FALSE, fig.width=10,message=FALSE}

# Here is a further breakdown of trade changes between the top 10 trading countries by seafood production method.

# a <-  ggplot(artis_10_14_top_10_with_years %>%
#            group_by(importer_iso3c, sanctions_towards_russia) %>%
#            summarise(sum = sum(live_weight)),
#          aes(x = sanctions_towards_russia, y = importer_iso3c, fill = sum, label= round(sum))) +
#   geom_tile() + 
#   geom_text()+
#   xlab("")+
#   ylab("Importers")+
#   ggtitle("Seafood Imported from Russia 2010-2014")+
# guides(fill = guide_colorbar(barwidth = 25, barheight = .5), dist_units = "Tons")+
#      scale_fill_gradient(trans = "log", name = "Tons", n.breaks = 5, low = "deepskyblue3", high = "blue3")
# a
# 
# b <-  ggplot(artis_15_19_top_10_with_years %>%
#            group_by(importer_iso3c, sanctions_towards_russia) %>%
#            summarise(sum = sum(live_weight)),
#          aes(x = sanctions_towards_russia, y = importer_iso3c, fill = sum, label= round(sum))) +
#   geom_tile() + 
#   geom_text()+
#   xlab("")+
#   ylab("")+
#   ggtitle("Seafood Imported from Russia 2015-2019")+
#   guides(fill = guide_colorbar(barwidth = 25, barheight = .5), dist_unit = "Tons")+
#   scale_fill_gradient(trans = "log", name = "Tons", n.breaks = 5,  low = "deepskyblue3", high = "blue3")
# #

top_importers_all_years %>%
  select(Importer: `Live Weight 2015-2019 (Tons)`) %>%
  slice(-c(11:15)) %>%
  replace(is.na(.), 0) %>%
  rename(Importer = Importer, weight_2010_2014 = 'Live Weight 2010-2014 (Tons)', weight_2015_2019 = 'Live Weight 2015-2019 (Tons)') %>%
  mutate(Difference = weight_2015_2019 - weight_2010_2014) %>%
  mutate(sanctions_towards_russia = case_when(
      Importer %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "yes",
      TRUE ~ "no"
    )) %>%
  ggplot(aes(x = sanctions_towards_russia, y = Importer, fill = Difference, label = round(Difference)))+
  geom_tile() + 
  geom_text() +
  xlab("Sanctions Towards Russia") +
  ylab("") +
  ggtitle("Change in Russian Seafood Imports Before and After Annexation")+
  guides(fill = guide_colorbar(barheight = 10), dist_unit = "Tons")+
  scale_fill_gradient2(name = "Tons", limits = c(-200000, 2000000), low = "darkred", mid = "white", high = "navy", midpoint = 0) #colors = c("red", "green"))
        #              values = scales::rescale(identity(c(-200000, 0, 
         #                                        1, 2000000))))

# barwidth = 25, 
#Change scale breaks
# Flip scale color gradient
  # , breaks = c(20, 400, 8000, 160000),
# ggarrange(a, b, ncol = 2, common.legend = TRUE)
```

## Species Trade

Trade trends with Russia can be seen when the imports and exports are broken down by the top species, rather than country. Russia stopped importing as many seafood goods due to its agricultural embargo, and instead increased domestic supply to become more agriculturally self-reliant and food secure (Wegner, 2018). It exported much more than it did prior to the Annexation, and exported more than it imported by an order of magnitude. Russia’s primary method was wild capture fisheries.

```{r, echo=FALSE, fig.width= 7}
# tmp <- artis_russia_2009_2019 %>%
#   filter(year %in% 2015:2019, exporter_iso3c == "RUS") %>%
#   mutate(hs_4digit = substr(hs6, 1, 4)) %>%
#   group_by(sci_name) %>%
#   summarise(live_weight = sum(live_weight_t)) %>%
#   arrange(desc(live_weight)) %>%
#   slice_max(order_by = live_weight, n = 10)

ggplot(artis_russia_2009_2019 %>%
         filter(year %in% 2010:2019) %>%
  filter( importer_iso3c == "RUS") %>%
 filter(sci_name == "clupea harengus" | sci_name == "osteichthyes" | sci_name == "salmo salar" | sci_name == "animalia" | sci_name == "scomber scombrus" | sci_name == "sardina pilchardus" | sci_name == "sprattus sprattus" | sci_name == "mallotus villosus" | sci_name == "actinopteri" | sci_name == "oncorhynchus mykiss" | sci_name == "pangasianodon hypophthalmus"| sci_name == "mytilus chilensis"))+
    geom_col(aes(x= year, y= live_weight_t, fill = sci_name))+
              facet_wrap(~method)+
  scale_color_solarized()+
  ggtitle("Top Russian Seafood Imports")+
  xlab("Year")+
  ylab("Live Weight (Tons)")+
  guides(fill = guide_legend(title = "Species"))+
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(breaks = seq(0,800000,by = 100000))+
  scale_y_continuous(labels = scales::comma)+
    scale_x_continuous(n.breaks = 10)+
  geom_vline(xintercept = 2014)

ggplot(artis_russia_2009_2019 %>%
         filter(exporter_iso3c == "RUS") %>%
        filter(sci_name == "gadus chalcogrammus" | sci_name == "gadus morhua" | sci_name == "clupea pallasii" | sci_name == "micromesistius poutassou" | sci_name == "oncorhynchus gorbuscha" | sci_name == "osteichthyes" | sci_name == "melanogrammus aeglefinus" | sci_name == "clupea harengus" | sci_name == "pleuronectiformes" | sci_name == "scomber scombrus" | sci_name == "animalia" | sci_name == "mallotus villosus" | sci_name == "pleuronectiformes")) +
    geom_col(aes(x= year, y= live_weight_t, fill = sci_name)) +
  facet_wrap(~method) +
#  theme_solarized()+
  scale_color_solarized()+
  ggtitle("Top Russian Seafood Exports")+
  xlab("Year")+
  ylab("Live Weight (Tons)")+
  guides(fill = guide_legend(title = "Species"))+
  theme(axis.text.x = element_text(angle = 90))+
    scale_y_continuous(breaks = seq(0,3000000,by = 200000))+
  scale_y_continuous(labels = scales::comma)+
  scale_x_continuous(n.breaks = 10)+
  geom_vline(xintercept = 2014)

```

```{r, include=FALSE}
# Animalia does not show up color-wise as great here because it spans multiple 4digit codes, whereas the ones above were grouped by sci name, not hs 4 digit code

ggplot(artis_russia_2009_2019 %>%
         filter(importer_iso3c == "RUS") %>%
  mutate(hs_4digit = substr(hs6, 1, 4)))+
    geom_col(aes(x= year, y= live_weight_t, fill = hs_4digit))+
                facet_wrap(~method)+
  theme_solarized()+
  scale_color_solarized()+
  ggtitle("Russian Seafood Imports")+
  xlab("Year")+
  ylab("Live Weight (t)")+
  guides(fill = guide_legend(title = "4 Digit HS Code"))+
  theme(axis.text.x = element_text(angle = 90))+
    scale_x_continuous(n.breaks = 10)+
  geom_vline(xintercept = 2014)

ggplot(artis_russia_2009_2019 %>%
         filter(exporter_iso3c == "RUS") %>%
  mutate(hs_4digit = substr(hs6, 1, 4)))+
    geom_col(aes(x= year, y= live_weight_t, fill = hs_4digit))+
                facet_wrap(~method)+
  theme_solarized()+
  scale_color_solarized()+
  ggtitle("Russian Seafood Exports")+
  xlab("Year")+
  ylab("Live Weight (t)")+
  guides(fill = guide_legend(title = "4 Digit HS Code"))+
  theme(axis.text.x = element_text(angle = 90))+
    scale_x_continuous(n.breaks = 10)+
  geom_vline(xintercept = 2014)
```

```{r, include=FALSE}
#Use these codes for expanding on importer/exporter species

top_exporters_species <- artis_russia_2009_2019 %>%
  filter(importer_iso3c == "RUS") %>%
      filter(exporter_iso3c == "CHL" |
          exporter_iso3c == "CHN" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "ISL" |
          exporter_iso3c == "LVA" |
          exporter_iso3c == "MAR" |
          exporter_iso3c == "MRT" |
          exporter_iso3c == "NOR" |
          exporter_iso3c == "UKR" |
          exporter_iso3c == "VNM" |
          exporter_iso3c == "BLR" |
          exporter_iso3c == "IND" )  %>%
  mutate(hs_4digit = substr(hs6, 1, 4)) %>%
  group_by(sci_name, exporter_iso3c) %>%
  summarise(live_weight = sum(live_weight_t)) %>%
  arrange(desc(live_weight)) %>%
  slice_max(order_by = live_weight, n = 10)

# 478 species alone in BLR, cannot graph that. Do top 10 species for each exporter?

top_importers_species <- artis_russia_2009_2019 %>%
  filter(exporter_iso3c == "RUS") %>%
      filter(
        importer_iso3c == "BLR" |
          importer_iso3c == "CHN" |
          importer_iso3c == "DEU" |
          importer_iso3c == "FRA" |
          importer_iso3c == "JPN" |
          importer_iso3c == "KAZ" |
          importer_iso3c == "KOR" |
          importer_iso3c == "NLD" |
          importer_iso3c == "UKR" |
          importer_iso3c == "USA" |
          importer_iso3c == "NGA"
      )  %>%
  mutate(hs_4digit = substr(hs6, 1, 4)) %>%
  group_by(sci_name, importer_iso3c) %>%
  summarise(live_weight = sum(live_weight_t)) 
```

## Trade Changes

Despite a Russian agricultural embargo counter-sanction, it still exported goods to whichever country would buy. This data shows seafood products that originated in Russia and were exported by Russia, compared to seafood that originated in Russia but was not directly exported by Russia.

```{r, include=FALSE}
# Playing around with import change to see if including 2014 made a difference in the data. When subtracted, it would basically zero itself out, which might not be a bad thing, still 5 years before and 5 years after. First graph is a lollipop showing trade changes with and without Russia (importing goods from Russia, Russia exports). The second graph shows the four quadrants of where countries fall in terms of total trade increased, Russian trade increased/ total trade increased, Russian trade increased/ total trade decreased, Russian trade decreased/ etc. 
# 
# Which countries imported more/less goods by weight from Russia?

russian_export_nation_change <- full_join(
  artis_russia_2009_2019 %>%
    filter(year %in% 2010:2014, exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>%
    group_by(importer_iso3c) %>%
    summarise(exports_from_russia_2010_2014 = sum(live_weight_t)),
#     summarise(exports_from_russia_2009_2014 = sum(live_weight_t)/1)  
  artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019, exporter_iso3c == "RUS", source_country_iso3c == "RUS") %>%
    group_by(importer_iso3c) %>%
    summarise(exports_from_russia_2015_2019 = sum(live_weight_t)), by = "importer_iso3c") %>%
  full_join(artis_russia_2009_2019 %>%
    filter(year %in% 2010:2014, exporter_iso3c != "RUS", source_country_iso3c == "RUS") %>%
    group_by(importer_iso3c) %>%
    summarise(nonrussian_exports_2010_2014 = sum(live_weight_t)), by = "importer_iso3c") %>%
  full_join(artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019, exporter_iso3c != "RUS", source_country_iso3c == "RUS") %>%
    group_by(importer_iso3c) %>%
    summarise(nonrussian_exports_2015_2019 = sum(live_weight_t)),
  by = "importer_iso3c"
) %>%
  replace(is.na(.), 0) %>%
  mutate(
    russian_exports = case_when(
      exports_from_russia_2015_2019 > exports_from_russia_2010_2014 ~ "increased",
      exports_from_russia_2015_2019 < exports_from_russia_2010_2014 ~ "decreased",
      exports_from_russia_2015_2019 == exports_from_russia_2010_2014 ~ "no change"
    ), 
    russian_export_trade_change = exports_from_russia_2015_2019-exports_from_russia_2010_2014,
    nonrussian_export = case_when(
      nonrussian_exports_2015_2019 > nonrussian_exports_2010_2014 ~ "increased",
      nonrussian_exports_2015_2019 < nonrussian_exports_2010_2014 ~ "decreased",
      nonrussian_exports_2015_2019 == nonrussian_exports_2010_2014 ~ "no change"
    ), #nonrussian exports are the same thing as those countries' total imports excluding what came from Russia
    nonrussian_export_trade_change = nonrussian_exports_2015_2019-nonrussian_exports_2010_2014
  ) %>%
  mutate(
    russian_export_percentage = (
      exports_from_russia_2015_2019 / exports_from_russia_2010_2014
    ) * 100
  ) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      importer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No"
    ))

#  tmp <- russian_export_nation_change %>%
#    filter(nonrussian_export == "increased", russian_exports == "decreased")
# unique(tmp$importer_iso3c)
# Countries whose total exports increased, but exports to Russia decreased- Chile, Colombia, Cyprus, Egypt Guatemala, Hong Kong, Hungary, Kyrgyzstan, Moldova, Mongolia, Slovenia, Sweden, Syria, Turkmenistan, Trinidad and Tobago, and Turkey

```

There were 16 countries whose total imports increased, but their import trade with Russia decreased- Chile, Colombia, Cyprus, Egypt, Guatemala, Hong Kong, Hungary, Kyrgyzstan, Moldova, Mongolia, Slovenia, Sweden, Syria, Turkmenistan, Trinidad and Tobago, and Turkey- indicating that Russia may have sent their products to a tertiary market before the goods were finally sent to these countries, but the indication probability is unknown. Of these countries, only Sweden, Hungary, and Moldova enacted sanctions against Russia, so their trade with Russia may have truly decreased, or, since their total imports increased, they may have ended up with goods that originated in Russia without dealing with Russia directly.

```{r, fig.height=6, fig.width=7, include=FALSE}

russian_export_nation_change %>%
  rename(`Russian Export Trade Change` = russian_export_trade_change, `Russia-exempt Export Trade Change` = nonrussian_export_trade_change) %>%
  filter(importer_iso3c != "CHN") %>%
  filter(abs(`Russian Export Trade Change`) > 10000 |
           abs(`Russia-exempt Export Trade Change`) > 10000) %>%
  select(importer_iso3c, `Russian Export Trade Change`, `Russia-exempt Export Trade Change`, exporter_sanctions_towards_russia) %>%
 # slice(-"CHN") %>%  
  pivot_longer(`Russian Export Trade Change`:`Russia-exempt Export Trade Change`, names_to = "trade_type", values_to = "trade_change") %>%
  ggplot()+
  geom_segment(mapping = aes( x = 0, xend = trade_change, y = importer_iso3c, yend = importer_iso3c, color = trade_type, group = importer_iso3c)) +
  geom_point(mapping = aes(x= trade_change, y = importer_iso3c, color = trade_type, group = importer_iso3c)) +
    geom_vline(xintercept = 0) +
    theme_bw()+
  xlab("Live Weight (Tons)")+
  ylab("Importers of Russian Goods")+
  ggtitle("Russian Importers Trade Change After Annexation", subtitle = "Faceted by Countries Who Place Sanctions on Russia")+
  guides(col = guide_legend(title = "Trade Type")) +
  facet_wrap(~exporter_sanctions_towards_russia)+
   scale_x_continuous(labels = scales::comma) 
#    theme(axis.text.x = element_text(angle = 10))

```

China was excluded to get a closer look at the countries with smaller import amounts. China's imports with Russia increased by around 1.5 million tons, while its imports from non-Russian countries declined.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

russian_export_nation_change %>% 
  ggplot(aes(x = russian_export_trade_change, y = nonrussian_export_trade_change, label = importer_iso3c, color = exporter_sanctions_towards_russia)) +
  geom_point() +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  geom_text_repel()+
  xlab("Imports Directly from Russia (Tons)")+
  ylab("Non-Russian Seafood Imports (Tons)") +
  ggtitle("Russian Imports Change after Annexation")+
    guides(col = guide_legend(title = "Imposed Sanctions on Russia"))+
  scale_y_continuous(breaks = seq(.250000, 100000, by = 100000))+
  scale_y_continuous(labels = scales::comma)

```

Non-Russian goods imported still originated in Russia, indicating a third-party route to obey sanctions but still do business with Russia. The x-axis displays seafood that originated in Russia and was exported by Russia, while the y-axis displays seafood that originated in Russia but was not exported by Russia.
Looking at the change in imports from Russia (Russian exports), the data can be broken into four categories: (clockwise from top left) direct Russian imports decrease, indirect Russian imports increase; direct Russian imports increase, indirect Russian imports increase; direct Russian imports increase, indirect Russian imports decrease; both direct and indirect imports from Russia decrease.

Although clustered, it appears that most nations who imposed sanctions against Russia saw an increase in imports directly from Russia and an increase in imports that originated from Russia. Japan, on the other hand, saw a noticeable decrease in tertiary Russian imports, but still an increase in direct imports from Russia.

```{r, include= FALSE, echo=FALSE}
# Next, we want to see changes in countries exporting goods to Russia, or change in Russian imports, between the two time periods. Specifically, if a nation’s total exports increased, but their exports to Russia decreased, where was the market shift?
# 
# Seven countries matched these criteria- Belarus, Brazil, Myanmar, Poland, Portugal, and Serbia.

# Which countries did Russia import more/less goods from before and after 2014?

russian_import_change <- full_join(
  artis_russia_2009_2019 %>%
    filter(year %in% 2010:2014, importer_iso3c == "RUS") %>%
    group_by(exporter_iso3c) %>%
    summarise(russian_imports_2010_2014 = sum(live_weight_t)),
  artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019, importer_iso3c == "RUS") %>%
    group_by(exporter_iso3c) %>%
    summarise(russian_imports_2015_2019 = sum(live_weight_t)),
  by = "exporter_iso3c"
) %>%
  full_join(
    artis_russia_2009_2019 %>%
      filter(year %in% 2010:2014) %>%
      group_by(exporter_iso3c) %>%
      summarise(total_imports_2010_2014 = sum(live_weight_t)),
    by = "exporter_iso3c"
  ) %>%
  full_join(
    artis_russia_2009_2019 %>%
      filter(year %in% 2015:2019) %>%
      group_by(exporter_iso3c) %>%
      summarise(total_imports_2015_2019 = sum(live_weight_t)),
    by = "exporter_iso3c"
  ) %>%
  replace(is.na(.), 0) %>%
  mutate(
    russian_import_change = case_when(
      russian_imports_2015_2019 > russian_imports_2010_2014 ~ "increased",
      russian_imports_2015_2019 < russian_imports_2010_2014 ~ "decreased",
      russian_imports_2015_2019 == russian_imports_2010_2014 ~ "no change"
    ),
    russian_import_change_weight = russian_imports_2015_2019 - russian_imports_2010_2014 ,
    total_imports = case_when(
      total_imports_2015_2019 > total_imports_2010_2014 ~ "increased",
      total_imports_2015_2019 < total_imports_2010_2014 ~ "decreased",
      total_imports_2015_2019 == total_imports_2010_2014 ~ "no change"
    ),
    total_trade_change = total_imports_2015_2019 - total_imports_2010_2014
  )  %>%
  mutate(exporter_sanctions_towards_russia = case_when(
    exporter_iso3c %in% c(
      "USA",
      "AUT",
      "BEL",
      "BGR",
      "HRV",
      "CYP",
      "CZE",
      "DNK",
      "EST",
      "FIN",
      "FRA",
      "DEU",
      "GRC",
      "HUN",
      "IRL",
      "ITA",
      "LVA",
      "LTU",
      "LUX",
      "MLT",
      "NLD",
      "POL",
      "PRT",
      "ROM",
      "SVK",
      "SVN",
      "ESP",
      "SWE",
      "GBR",
      "JPN",
      "ALB",
      "ISL",
      "AUS",
      "MNT",
      "UKR",
      "CAN",
      "NOR",
      "CHE",
      "MDA"
    )  ~ "yes",
    TRUE ~ "no"
  ))

tmp <- russian_import_change %>%
  filter(total_imports == "increased", russian_import_change == "decreased")
unique(tmp$exporter_iso3c)

# For countries whose exports decreased, did it go to other markets? Expand filter to all importers

#Exports to Russia decreased, total exports increased:
# "BEL" "BRA" "MMR" "PHL" "POL" "PRT" "SRB"

```

```{r, fig.cap="Filtered by Change greater than 10", fig.height=6, message=FALSE, include=FALSE}
russian_import_change %>%
  rename(`Russian Import Trade Change` = russian_import_change_weight, `Russia-exempt Import Trade Change` = total_trade_change) %>%
  filter(exporter_iso3c != "RUS") %>%
  filter(abs(`Russian Import Trade Change`) > 10000 |
           abs(`Russia-exempt Import Trade Change`) > 10000) %>%
  select(exporter_iso3c, `Russian Import Trade Change`, `Russia-exempt Import Trade Change`, exporter_sanctions_towards_russia) %>%
  pivot_longer(`Russian Import Trade Change`:`Russia-exempt Import Trade Change`, names_to = "trade_type", values_to = "trade_change") %>%
  ggplot()+
  geom_segment(mapping = aes( x = 0, xend = trade_change, y = exporter_iso3c, yend = exporter_iso3c, color = trade_type, group = exporter_iso3c)) +
  geom_point(mapping = aes(x= trade_change, y = exporter_iso3c, color = trade_type, group = exporter_iso3c)) +
    geom_vline(xintercept = 0) +
    theme_bw()+
  xlab("Live Weight (Tons)")+
  ylab("Exporters to Russia")+
  ggtitle("Russian Imports Trade Change after Annexation", subtitle = "Faceted by Embargoed Nations")+
  scale_x_continuous(breaks= seq(-2500000, 3000000, by = 1000000))+
  scale_x_continuous(labels= scales::comma) +
  facet_wrap(~exporter_sanctions_towards_russia)+
      guides(col = guide_legend(title = "Trade Type"))

```

There was little trade change in countries who did not face the embargo, but in countries that did, their total trade decreased, except for, again, Denmark. Russia did not import as many goods from China, even though it's exports to China increased. This was a common theme in Russian trade after the Annexation. In nations that faced the embargo, their total exports decreased as well.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

russian_import_change %>% 
  ggplot(aes(x = russian_import_change_weight, y = total_trade_change, label = exporter_iso3c, color = exporter_sanctions_towards_russia)) +
  geom_point() +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  geom_text_repel()+
  xlab("Russian Imports (Tons)")+
  ylab("Non-Russian Imports (Tons)") +
  ggtitle("Russian Importers Trade Change", subtitle = "Change in Total Russian Imports between 2010-2014, and 2015-2019")+
    scale_x_continuous(breaks= seq(-2500000, 1000000, by = 1000000))+
  scale_x_continuous(labels= scales::comma)+
      guides(col = guide_legend(title = "Imposed Sanctions on Russia")) +
    scale_y_continuous(labels = scales::comma)

```

Here, too, there were four possibilities of trade change, listed clockwise from the top left quadrant- Russian imports decrease, total exports increased; Russian imports increase, total exports increased; Russian imports increase, total exports decreased; and all exports from that country decrease. All countries that placed sanctions on Russia, and therefore had the food embargo placed upon them, saw a decrease in Russian imports of their goods and a decrease in their total exports, except for Denmark, which saw an increase in both Russian and total trade.

# Discussion

Countries that imposed sanctions on Russia, for the most part, still continued or increased their Russian seafood imports. The exceptions were Germany, and the USA. South Korea's imports also decreased, but it wouldn't adopt Western sanctions against Russia until the Russian-Ukrainian War in 2022. Still, with variable degrees of import changes indeterminate of sanction status, there is no clear trend to predict import changes.

Due to the embargo, many countries who imposed sanctions on Russia stopped exporting seafood products there. New countries rose up to fill their ranks, but their exports did not make up the difference of what Russia lost. This did not seem to impact Russia, however, as it ramped up domestic supply, mostly of capture fisheries. There is an inverse relationship between the trends of how much Russia imported and exported after the Annexation. Russia's domestic production allowed for an increase in Russian exports, presumably also supplying increased domestic food security and enriching the fishing economy.

The species did not change, either. The species trade was broken down to see if certain embargoed products were being reworked into a non-agricultural good, but the top HS codes did not change, and included HS 03, 05, 16, and 23, corresponding to fresh, chilled, or frozen fish and invertebrates; animal products; prepared seafood; and fish meal, respectively. No change in HS code trade shows that there was no tertiary market for alternate seafood goods trying to bypass the embargo.

This is shown, too, in total trade changes between Russia and the global seafood trade network. Most nations that enacted sanctions towards Russia saw an increase in imports directly from Russia and an increase in total imports originating in Russia. Their total exports, however, decreased, when they were banned from exporting to Russia. This may be a constraint of the data set, however, as every piece of data was connected to Russia in some way. The opposite happened in Denmark, which experienced an increase in both Russia and total trade. Future work may include expanding trade view around Denmark to include nations using Danish waters and docking in Denmark, or if embargoed nations traded more with Denmark.

The total trade decreases and unchanging HS codes show that there likely was no tertiary market that embargoed nations were using to get their seafood products to Russia. Overall, they were buying more goods, but selling less.

### 2022-08-11 Russia Case Study under the hood.Rmd
Case Study Final Draft is the RMD for the finished writeup. Russia Case Study under the hood includes the complete writeup, plus code for unused charts, tables, and vectors to find unused data, like species of each exporting country

--- 2022-08-11 Case Study Final Draft.Rmd
@@
 
-Russia began an annexation on Ukraine’s Crimean peninsula on March 18, 2014, sparking international tensions that imposed sanctions on Russia (Biersak, 2014).
+Russia began an annexation on Crimea in Ukraine on March 18, 2014, sparking international tensions and sanctions enacted against Russia (Biersak, 2014).
 Sanctions included freezing Russian assets and capturing property to restrict Russian access to Western markets, aiming to cripple their banking, energy, and defense sectors; and banning exports to Russia of military technology and dual-use goods, including oil exploration and production equipment.
 (DeYoung; Christie).
-In response, Russia provided counter-sanctions as an agricultural embargo in 2014 that banned itself from importing food items, including seafood, from sanctioning nations (Wegren, 2018).
+In response, Russia provided counter-sanctions, most notably as an agricultural import ban set in August 2014 that banned itself from importing food items, including seafood, from sanctioning nations (Wegren, 2018).
 With market data available from before and after the 2014 Annexation, this case study seeks to understand the seafood trade flow amid various embargoes and sanctions to better understand whose exports to Russia increased and whose decreased, and how much of that trade entered the market through third-party exporters to complete trades to and from Russia.
@@
 Countries are denoted with their 3-digit internationally standardized ISO code.
+
+![ISO 3 Codes](https://www.researchgate.net/profile/Chahir-Zaki/publication/23779008/figure/tbl7/AS:669253044801551@1536573768865/List-of-countries-by-code-iso-3.png)
 
@@
 
-```{r, echo=FALSE}
+```{r}
   kable(tmp, caption = "Top 10 Importers of Russian Goods")
@@
 Germany, The United States, and South Korea all decreased their imports from Russia after the annexation, although only Germany and the United States had imposed sanctions on Russia and faced the agricultural embargo.
-Kazakhstan took the place of the USA in the top 10 importers after the annexation, but it was not enough to make up the difference from losses by the USA.
+Kazakstan took the place of the USA in the top 10 importers after the annexation, but it was not enough to make up the difference from losses by the U.S.A.
 
@@
 
-Due to Russia's agricultural embargo counter-sanction, Russia ramped up domestic good production, primarily in capture fisheries.
+Due to Russia's agricultural embargo counter-sanction, which banned itself from importing agricultural goods from countries who imposed sanctions against Russia, Russia ramped up domestic good production, primarily in capture fisheries.
 In most cases, importing countries bought more capture products than aquaculture, with the exceptions being Great Britain, Moldova, Azerbaijan, and Vietnam.
@@
 
-```{r, echo=FALSE}
+```{r}
 top_importers_all_years %>%
@@
 
-Some importing nations had more drastic changes in imports before and after the Annexation than others.
+Some importing nations had more drastic changes in imports before and after the Annexation thatn other.
 The USA and Germany, for example, saw over a 50% decrease in imports from Russia, while other countries like the Netherlands and Nigeria experienced a 50% increase in Russian imports.
@@
 
-```{r, echo=FALSE}
+```{r}
 kable(top_exporters_all_years, caption = "Top 10 Exporters to Russia")
@@
 Top seafood exporters to Russia include China, Iceland, Latvia, Morocco, Norway, and Ukraine, which all decreased total exports in the five years following the 2014 Annexation.
-Latvia, Iceland, Norway, and Ukraine stopped exporting to Russia completely due to the embargo.
+Latvia, Iceland, Norway, and Ukraine stopped exporting to Russia completely.
+These four countries enacted sanctions against Russia in response to the Annexation, which meant that the Russian food embargo was placed on them in turn.
 In their place, Greenland, India, Mauritania, and Thailand rose to the top 10 exporters to Russia.
@@
 
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, fig.cap= "Faceted by countries who imposed sanctions on Russia", message=FALSE}
 
@@
 
-```{r, echo=FALSE, fig.width=6}
+```{r, fig.width= 8}
 full_join(artis_russia_2009_2019 %>%
@@
 China and Morocco, in the countries who did not impose sanctions, saw their total exports fall, as did each country affected by the embargo, except for Denmark.
-```{r, echo=FALSE}
+```{r}
 top_exporters_all_years %>%
@@
 Trade trends with Russia can be seen when the imports and exports are broken down by the top species, rather than country.
-Russia stopped importing as many seafood goods due to its agricultural embargo, and instead increased domestic supply to become more agriculturally self-reliant and food secure (Wegner, 2018).
-It exported much more than it did prior to the Annexation, and exported more than it imported by an order of magnitude.
-Russia’s primary method was wild capture fisheries.
+It is evident that Russia stopped importing as many seafood goods due to its agricultural embargo.
+Instead, Russia increased domestic supply to become more agriculturally self-reliant and food secure, and exported much more than it did prior to the Annexation.
+Its primary method was capture fisheries.
+Russia exported more seafood than it imported by an order of magnitude.
 
@@
               facet_wrap(~method)+
+#  theme_solarized()+
   scale_color_solarized()+
@@
 
-```{r, include=FALSE}
+```{r include=FALSE}
 # Animalia does not show up color-wise as great here because it spans multiple 4digit codes, whereas the ones above were grouped by sci name, not hs 4 digit code
@@
 
-```{r, fig.height=6, fig.width=7, include=FALSE}
+```{r, echo=FALSE, fig.height=6, fig.width=7}
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+```{r, echo=FALSE, message= FALSE}
 
@@
 
-```{r, fig.cap="Filtered by Change greater than 10", fig.height=6, message=FALSE, include=FALSE}
+```{r, echo = FALSE, message=FALSE, fig.height= 6, fig.cap = "Filtered by Change greater than 10,000 tons to show highest Exporting Countries to Russia"}
 russian_import_change %>%
@@
 This was a common theme in Russian trade after the Annexation.
-In nations that faced the embargo, their total exports decreased as well.
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+In nations that faced the embargo, their total exports decreased as well, so Russia may have been a significant source of exports for them.
+
+```{r}
 
@@
 The exceptions were Germany, and the USA.
-South Korea's imports also decreased, but it wouldn't adopt Western sanctions against Russia until the Russian-Ukrainian War in 2022.
+South Korea's imports also decreased, but it would go on to adopt Western sanctions against Russia in the Russian-Ukrainian War in 2022.
 Still, with variable degrees of import changes indeterminate of sanction status, there is no clear trend to predict import changes.
@@
 The species trade was broken down to see if certain embargoed products were being reworked into a non-agricultural good, but the top HS codes did not change, and included HS 03, 05, 16, and 23, corresponding to fresh, chilled, or frozen fish and invertebrates; animal products; prepared seafood; and fish meal, respectively.
-No change in HS code trade shows that there was no tertiary market for alternate seafood goods trying to bypass the embargo.
+No change in HS code trade shows that there was no tertiary market for alternate seafood goods.
 
@@
 Their total exports, however, decreased, when they were banned from exporting to Russia.
-This may be a constraint of the data set, however, as every piece of data was connected to Russia in some way.
+This may be a constraint of the dataset, however, as every piece of data was connected to Russia in some way.
 The opposite happened in Denmark, which experienced an increase in both Russia and total trade.
@@
 
-The total trade decreases and unchanging HS codes show that there likely was no tertiary market that embargoed nations were using to get their seafood products to Russia.
+The total trade decreases and unchanging HS codes show that there likely was no teritary market that embargoed nations were using to get their seafood products to Russia.
 Overall, they were buying more goods, but selling less.
+
+```{r}
+# Example 3
+# Showing all trade flows from producers to exporters to importers, 2010-2014
+
+threshold <- 0.01
+
+# Getting all producers limit by threshold
+producers <- artis_russia_2009_2019 %>%
+  filter(year %in% 2010:2014) %>%
+  group_by(source_country_iso3c, exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(source_country_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ source_country_iso3c))
+
+# Getting all exporters limit by threshold
+exporters <- artis_russia_2009_2019 %>%
+    filter(year %in% 2010:2014) %>%
+  group_by(exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(exporter_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ exporter_iso3c))
+
+# Getting all importers limit by threshold
+importers <- artis_russia_2009_2019 %>%
+    filter(year %in% 2010:2014) %>%
+  group_by(importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(importer_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ importer_iso3c))
+
+# Change all producers, exporters, and importers names based on limit threshold
+artis_thresholded <- artis_russia_2009_2019 %>%
+    filter(year %in% 2010:2014) %>%
+  mutate(
+    exporter_iso3c = case_when(
+      exporter_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ exporter_iso3c,
+      TRUE ~ "Other"
+    ),
+    importer_iso3c = case_when(
+      importer_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ importer_iso3c,
+      TRUE ~ "Other"
+    ),
+    source_country_iso3c = case_when(
+      source_country_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ source_country_iso3c,
+      TRUE ~ "Other"
+    )
+  ) %>%
+  group_by(source_country_iso3c, exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t))
+
+# Summarize trade flows from producers to exporters
+source_exporter <- artis_thresholded %>%
+
+  group_by(source_country_iso3c, exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(source_country_iso3c = paste(source_country_iso3c, "_source", sep=""),
+         exporter_iso3c = paste(exporter_iso3c, "_exp", sep="")) %>%
+  rename(source = source_country_iso3c,
+         target = exporter_iso3c)
+
+# Summarize trade flows from exporters to importers
+exporter_importer <- artis_thresholded %>%
+
+  group_by(exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(exporter_iso3c = paste(exporter_iso3c, "_exp", sep=""),
+         importer_iso3c = paste(importer_iso3c, "_imp", sep="")) %>%
+  rename(source = exporter_iso3c,
+         target = importer_iso3c)
+
+# Overall trade flow dataframes from producers -> exporters -> importers
+tmp <- source_exporter %>%
+  bind_rows(exporter_importer)
+
+# Creating node dataframe from country names to node id
+nodes <- data.frame(
+  # Unique list of trading entity names
+  name = unique(c(tmp$source, tmp$target))
+  ) %>%
+  # labels for sankey diagram only include country iso3 code
+  mutate(label = gsub("_.{3,6}", "", name))
+
+# Map source and target names to row in the nodes dataframe, 0-indexed
+tmp <- tmp %>%
+  mutate(source_id = match(source, nodes$name) - 1,
+         target_id = match(target, nodes$name) - 1)
+
+# Create Sankey Diagram
+sankeyNetwork(Links=tmp, Nodes = nodes, Source="source_id", Target="target_id",
+              Value="live_weight_t", NodeID="label")
+
+# Showing all trade flows from producers to exporters to importers, 2015-2019
+
+threshold <- 0.01
+
+# Getting all producers limit by threshold
+producers <- artis_russia_2009_2019 %>%
+  filter(year %in% 2015:2019) %>%
+  group_by(source_country_iso3c, exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(source_country_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ source_country_iso3c))
+
+# Getting all exporters limit by threshold
+exporters <- artis_russia_2009_2019 %>%
+    filter(year %in% 2015:2019) %>%
+  group_by(exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(exporter_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ exporter_iso3c))
+
+# Getting all importers limit by threshold
+importers <- artis_russia_2009_2019 %>%
+    filter(year %in% 2015:2019) %>%
+  group_by(importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(importer_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ importer_iso3c))
+
+# Change all producers, exporters, and importers names based on limit threshold
+artis_thresholded <- artis_russia_2009_2019 %>%
+    filter(year %in% 2015:2019) %>%
+  mutate(
+    exporter_iso3c = case_when(
+      exporter_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ exporter_iso3c,
+      TRUE ~ "Other"
+    ),
+    importer_iso3c = case_when(
+      importer_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ importer_iso3c,
+      TRUE ~ "Other"
+    ),
+    source_country_iso3c = case_when(
+      source_country_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ source_country_iso3c,
+      TRUE ~ "Other"
+    )
+  ) %>%
+  group_by(source_country_iso3c, exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t))
+
+# Summarize trade flows from producers to exporters
+source_exporter <- artis_thresholded %>%
+
+  group_by(source_country_iso3c, exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(source_country_iso3c = paste(source_country_iso3c, "_source", sep=""),
+         exporter_iso3c = paste(exporter_iso3c, "_exp", sep="")) %>%
+  rename(source = source_country_iso3c,
+         target = exporter_iso3c)
+
+# Summarize trade flows from exporters to importers
+exporter_importer <- artis_thresholded %>%
+
+  group_by(exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(exporter_iso3c = paste(exporter_iso3c, "_exp", sep=""),
+         importer_iso3c = paste(importer_iso3c, "_imp", sep="")) %>%
+  rename(source = exporter_iso3c,
+         target = importer_iso3c)
+
+# Overall trade flow dataframes from producers -> exporters -> importers
+tmp <- source_exporter %>%
+  bind_rows(exporter_importer)
+
+# Creating node dataframe from country names to node id
+nodes <- data.frame(
+  # Unique list of trading entity names
+  name = unique(c(tmp$source, tmp$target))
+  ) %>%
+  # labels for sankey diagram only include country iso3 code
+  mutate(label = gsub("_.{3,6}", "", name))
+
+# Map source and target names to row in the nodes dataframe, 0-indexed
+tmp <- tmp %>%
+  mutate(source_id = match(source, nodes$name) - 1,
+         target_id = match(target, nodes$name) - 1)
+
+# Create Sankey Diagram
+sankeyNetwork(Links=tmp, Nodes = nodes, Source="source_id", Target="target_id",
+              Value="live_weight_t", NodeID="label")
+
+```
+
+```{r}
+###############
+# Denmark 2010-2014
+threshold <- 0.01
+
+# Getting all producers limit by threshold
+producers <- artis_russia_2009_2019 %>%
+  filter(year %in% 2010:2014) %>%
+  group_by(source_country_iso3c, exporter_iso3c == "DNK") %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(source_country_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ source_country_iso3c))
+
+# Getting all exporters limit by threshold
+exporters <- artis_russia_2009_2019 %>%
+    filter(year %in% 2010:2014) %>%
+  filter(exporter_iso3c == "DNK") %>%
+  group_by(exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(exporter_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ exporter_iso3c))
+
+# Getting all importers limit by threshold
+importers <- artis_russia_2009_2019 %>%
+    filter(year %in% 2010:2014, exporter_iso3c == "DNK") %>%
+  group_by(importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(importer_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ importer_iso3c))
+
+# Change all producers, exporters, and importers names based on limit threshold
+artis_thresholded <- artis_russia_2009_2019 %>%
+    filter(year %in% 2010:2014, exporter_iso3c == "DNK") %>%
+  mutate(
+    exporter_iso3c = case_when(
+      exporter_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ exporter_iso3c,
+      TRUE ~ "Other"
+    ),
+    importer_iso3c = case_when(
+      importer_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ importer_iso3c,
+      TRUE ~ "Other"
+    ),
+    source_country_iso3c = case_when(
+      source_country_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ source_country_iso3c,
+      TRUE ~ "Other"
+    )
+  ) %>%
+  group_by(source_country_iso3c, exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t))
+
+# Summarize trade flows from producers to exporters
+source_exporter <- artis_thresholded %>%
+
+  group_by(source_country_iso3c, exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(source_country_iso3c = paste(source_country_iso3c, "_source", sep=""),
+         exporter_iso3c = paste(exporter_iso3c, "_exp", sep="")) %>%
+  rename(source = source_country_iso3c,
+         target = exporter_iso3c)
+
+# Summarize trade flows from exporters to importers
+exporter_importer <- artis_thresholded %>%
+
+  group_by(exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(exporter_iso3c = paste(exporter_iso3c, "_exp", sep=""),
+         importer_iso3c = paste(importer_iso3c, "_imp", sep="")) %>%
+  rename(source = exporter_iso3c,
+         target = importer_iso3c)
+
+# Overall trade flow dataframes from producers -> exporters -> importers
+tmp <- source_exporter %>%
+  bind_rows(exporter_importer)
+
+# Creating node dataframe from country names to node id
+nodes <- data.frame(
+  # Unique list of trading entity names
+  name = unique(c(tmp$source, tmp$target))
+  ) %>%
+  # labels for sankey diagram only include country iso3 code
+  mutate(label = gsub("_.{3,6}", "", name))
+
+# Map source and target names to row in the nodes dataframe, 0-indexed
+tmp <- tmp %>%
+  mutate(source_id = match(source, nodes$name) - 1,
+         target_id = match(target, nodes$name) - 1)
+
+# Create Sankey Diagram
+sankeyNetwork(Links=tmp, Nodes = nodes, Source="source_id", Target="target_id",
+              Value="live_weight_t", NodeID="label")
+
+###############
+# Denmark 2015-2019
+threshold <- 0.01
+
+# Getting all producers limit by threshold
+producers <- artis_russia_2009_2019 %>%
+  filter(year %in% 2015:2019) %>%
+  group_by(source_country_iso3c, exporter_iso3c == "DNK") %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(source_country_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ source_country_iso3c))
+
+# Getting all exporters limit by threshold
+exporters <- artis_russia_2009_2019 %>%
+    filter(year %in% 2015:2019) %>%
+  filter(exporter_iso3c == "DNK") %>%
+  group_by(exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(exporter_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ exporter_iso3c))
+
+# Getting all importers limit by threshold
+importers <- artis_russia_2009_2019 %>%
+    filter(year %in% 2015:2019, exporter_iso3c == "DNK") %>%
+  group_by(importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(importer_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ importer_iso3c))
+
+# Change all producers, exporters, and importers names based on limit threshold
+artis_thresholded <- artis_russia_2009_2019 %>%
+    filter(year %in% 2015:2019, exporter_iso3c == "DNK") %>%
+  mutate(
+    exporter_iso3c = case_when(
+      exporter_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ exporter_iso3c,
+      TRUE ~ "Other"
+    ),
+    importer_iso3c = case_when(
+      importer_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ importer_iso3c,
+      TRUE ~ "Other"
+    ),
+    source_country_iso3c = case_when(
+      source_country_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ source_country_iso3c,
+      TRUE ~ "Other"
+    )
+  ) %>%
+  group_by(source_country_iso3c, exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t))
+
+# Summarize trade flows from producers to exporters
+source_exporter <- artis_thresholded %>%
+
+  group_by(source_country_iso3c, exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(source_country_iso3c = paste(source_country_iso3c, "_source", sep=""),
+         exporter_iso3c = paste(exporter_iso3c, "_exp", sep="")) %>%
+  rename(source = source_country_iso3c,
+         target = exporter_iso3c)
+
+# Summarize trade flows from exporters to importers
+exporter_importer <- artis_thresholded %>%
+
+  group_by(exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(exporter_iso3c = paste(exporter_iso3c, "_exp", sep=""),
+         importer_iso3c = paste(importer_iso3c, "_imp", sep="")) %>%
+  rename(source = exporter_iso3c,
+         target = importer_iso3c)
+
+# Overall trade flow dataframes from producers -> exporters -> importers
+tmp <- source_exporter %>%
+  bind_rows(exporter_importer)
+
+# Creating node dataframe from country names to node id
+nodes <- data.frame(
+  # Unique list of trading entity names
+  name = unique(c(tmp$source, tmp$target))
+  ) %>%
+  # labels for sankey diagram only include country iso3 code
+  mutate(label = gsub("_.{3,6}", "", name))
+
+# Map source and target names to row in the nodes dataframe, 0-indexed
+tmp <- tmp %>%
+  mutate(source_id = match(source, nodes$name) - 1,
+         target_id = match(target, nodes$name) - 1)
+
+# Create Sankey Diagram
+sankeyNetwork(Links=tmp, Nodes = nodes, Source="source_id", Target="target_id",
+              Value="live_weight_t", NodeID="label")
+
+```
+
+A closer look at the trade through Denmark shows the changes in source countries and importers from 2010-2014 and 2015-2019.
+After the Annexation, source countries Canada, Iceland, Mauritania, and Norway were replaced with Greenland, India, and Morocco.
+Mauritania was the only source before the Annexation that did not impose sanctions on Russia.
+Denmark continued receiving seafood from Chile, China, Russia, Vietnam, and in its own waters in both time periods.
+Denmark's continued trade with Russia may be a contributing factor as to why it stopped receiving seafood from Canada, Iceland, and Norway- countries that had imposed sanctions of Russia, but it may also be due to the .01% threshold placed on the calculations, putting those countries' decreased trade into the nearly quadrupled "Other" category.
+The real mystery is why Denmark's exports to Russia nearly tripled (373,212 tons -> 977,581 tons), when Russia's agricultural embargo also should have applied to Denmark.
+A total of 381,436 tons of seafood products flowed through Denmark before the Annexation, and 985,261 tons flowed after, so its trade with Russia remained proportional, even though it should have been 0.
+
+```{r, include=FALSE}
+
+library(tidyverse)
+library(networkD3)
+
+#rm(list=ls())
+
+# Directory Structure
+# datadir <- "data"
+# filename <- "artis_russia_case.csv" # ARTIS Russia Case Study
+# 
+# artis <- read.csv(file.path(datadir, filename))
+
+################################################################################
+# Example 1
+# Showing trade relationships where Russia is the main producer or intermediate exporter
+
+# Threshold for creating an Other importer group
+threshold <- 0.01
+
+# Create a links dataframe
+russia_prod_exp <- artis_russia_2009_2019 %>%
+  # Filtering for all trade relationships where Russia is producer OR exporter
+  filter(source_country_iso3c == "RUS" |
+           exporter_iso3c == "RUS") %>%
+  group_by(importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  # Getting proportion of total trade for each direct and indirect importer from Russia 
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = (live_weight_t / total)) %>%
+  # Using proportion to create an Other importer group
+  mutate(importer_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ importer_iso3c)) %>%
+  # Re-summarizing trade flows using Other group
+  group_by(importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t))
+
+# Creating a Node dataframe
+nodes <- data.frame(
+  country = c("RUS", unique(russia_prod_exp$importer_iso3c))
+)
+
+nodes <- nodes %>%
+  mutate(node_id = seq(from=0, to=nrow(russia_prod_exp)))
+
+# Adding exporter column and node ids
+russia_prod_exp <- russia_prod_exp %>%
+  left_join(nodes, by=c("importer_iso3c"="country")) %>%
+  mutate(exporter_nodes = 0) %>%
+  rename(importer_nodes = node_id) %>%
+  select(exporter_nodes, importer_nodes, live_weight_t)
+
+# Creating Sankey Diagram
+sankeyNetwork(
+  Links=russia_prod_exp, Nodes=nodes %>% select(country), Source="exporter_nodes", Target="importer_nodes",
+  Value="live_weight_t", NodeID="country"
+)
+
+################################################################################
+# Example 2
+# Trade relationships where Russia is the importer
+
+# Threshold for creating an Other exporter group
+threshold <- 0.01
+
+russia_imp <- artis_russia_2009_2019 %>%
+  # Filter trade relationships where the importer is Russia
+  filter(importer_iso3c == "RUS") %>%
+  group_by(exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  # Create trade flow proportions and filter to create Other importer group
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(exporter_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ exporter_iso3c)) %>%
+  # Re-summarize with Other exporter group
+  group_by(exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t))
+
+# Create node dataframe relating country names to node ID's
+nodes <- data.frame(
+  country = c("RUS", unique(russia_imp$exporter_iso3c))
+)
+
+nodes <- nodes %>%
+  mutate(node_id = seq(from=0, to=nrow(russia_imp)))
+
+russia_imp <- russia_imp %>%
+  left_join(nodes, by=c("exporter_iso3c"="country")) %>%
+  mutate(importer_nodes = 0) %>%
+  rename(exporter_nodes = node_id) %>%
+  select(exporter_nodes, importer_nodes, live_weight_t)
+
+sankeyNetwork(
+  Links=russia_imp, Nodes=nodes %>% select(country), Source="exporter_nodes", Target="importer_nodes",
+  Value="live_weight_t", NodeID="country"
+)
+################################################################################
+# Example 3
+# Showing all trade flows from producers to exporters to importers
+
+threshold <- 0.01
+
+# Getting all producers limit by threshold
+producers <- artis_russia_2009_2019 %>%
+
+  group_by(source_country_iso3c, exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(source_country_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ source_country_iso3c))
+
+# Getting all exporters limit by threshold
+exporters <- artis_russia_2009_2019 %>%
+  group_by(exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(exporter_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ exporter_iso3c))
+
+# Getting all importers limit by threshold
+importers <- artis_russia_2009_2019 %>%
+  group_by(importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  ungroup() %>%
+  mutate(total = sum(live_weight_t)) %>%
+  mutate(prop = live_weight_t / total) %>%
+  mutate(importer_iso3c = case_when(
+    prop < threshold ~ "Other",
+    TRUE ~ importer_iso3c))
+
+# Change all producers, exporters, and importers names based on limit threshold
+artis_thresholded <- artis_russia_2009_2019 %>%
+  mutate(
+    exporter_iso3c = case_when(
+      exporter_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ exporter_iso3c,
+      TRUE ~ "Other"
+    ),
+    importer_iso3c = case_when(
+      importer_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ importer_iso3c,
+      TRUE ~ "Other"
+    ),
+    source_country_iso3c = case_when(
+      source_country_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ source_country_iso3c,
+      TRUE ~ "Other"
+    )
+  ) %>%
+  group_by(source_country_iso3c, exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t))
+
+# Summarize trade flows from producers to exporters
+source_exporter <- artis_thresholded %>%
+  group_by(source_country_iso3c, exporter_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(source_country_iso3c = paste(source_country_iso3c, "_source", sep=""),
+         exporter_iso3c = paste(exporter_iso3c, "_exp", sep="")) %>%
+  rename(source = source_country_iso3c,
+         target = exporter_iso3c)
+
+# Summarize trade flows from exporters to importers
+exporter_importer <- artis_thresholded %>%
+  group_by(exporter_iso3c, importer_iso3c) %>%
+  summarize(live_weight_t = sum(live_weight_t)) %>%
+  mutate(exporter_iso3c = paste(exporter_iso3c, "_exp", sep=""),
+         importer_iso3c = paste(importer_iso3c, "_imp", sep="")) %>%
+  rename(source = exporter_iso3c,
+         target = importer_iso3c)
+
+# Overall trade flow dataframes from producers -> exporters -> importers
+tmp <- source_exporter %>%
+  bind_rows(exporter_importer)
+
+# Creating node dataframe from country names to node id
+nodes <- data.frame(
+  # Unique list of trading entity names
+  name = unique(c(tmp$source, tmp$target))
+  ) %>%
+  # labels for sankey diagram only include country iso3 code
+  mutate(label = gsub("_.{3,6}", "", name))
+
+# Map source and target names to row in the nodes dataframe, 0-indexed
+tmp <- tmp %>%
+  mutate(source_id = match(source, nodes$name) - 1,
+         target_id = match(target, nodes$name) - 1)
+
+# Create Sankey Diagram
+sankeyNetwork(Links=tmp, Nodes = nodes, Source="source_id", Target="target_id",
+              Value="live_weight_t", NodeID="label")
+
+```
+
+```{r, include= FALSE}
+# https://github.com/Seafood-Globalization-Lab/exploreARTIS
+
+# library(devtools)
+# # devtools::install_github("Seafood-Globalization-Lab/exploreARTIS")
+# 
+# library(exploreARTIS)
+# 
+# plot_sankey(artis_russia_2009_2019, producers = "RUS")
+# plot_species_line(artis_russia_2009_2019 %>%
+#                     rename(sciname= sci_name), producers = "RUS")
+# plot_species_stacked(artis_russia_2009_2019%>%
+#                     rename(sciname= sci_name), producers = "RUS")
+# plot_partner_line(artis_russia_2009_2019 %>%
+#                     rename(sciname = sci_name)
+#                     , producers = "RUS", 
+#                   trade_flow = "import")
+# plot_partner_stacked(artis_russia_2009_2019 %>%
+#                     rename(sciname = sci_name)
+#                     , producers = "RUS", 
+#                   trade_flow = "import")
+# plot_chord(artis_russia_2009_2019 %>%
+#                     rename(sciname = sci_name), 
+#            focal_country = "RUS",
+#            species = "salmo salar",
+#            years = 2009,
+#            prod_method = "aquaculture")
+```

### 2024-02-21 ms-russia-figures.Rmd
update figures with new consumption data anad stats for MS

---
title: "Russian sanctions figures"
output: html_document
date: "2024-02-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(countrycode)
library(exploreARTIS)
library(DBI)
library(janitor)
library(broom)
library(dbscan)
library(GGally)
library(ggrepel)
library(ggpubr)
```

```{r}
habitat_source_colors <- c("#1B708F", # blue = marine capture
                          "#86ADA7", # light blue = freshwater capture
                          "#F37542", # medium orange = marine aquaculture
                          "#F7AF75", # light orange = inland aquaculture
                          "grey50" # unknown
                          )

region_colors <- c(
  "#741A32", # maroon
  "#B34232", # burnt orange
  "#D38F35", #  orange
  "#D4B95f", # khaki
  "#4FA2A2", # teal
  "#114F59" # dark teal
)
```

```{r}
# Initial database pulls

# Database connection
con <- dbConnect(RPostgres::Postgres(),
                 dbname=Sys.getenv("DB_NAME"),
                 host="localhost",
                 port="5432",
                 user=Sys.getenv("DB_USERNAME"),
                 password=Sys.getenv("DB_PASSWORD"))

# Check that connection is established by checking which tables are present
dbListTables(con)

# ARTIS dataframe
artis <- dbGetQuery(con, "SELECT * FROM all_estimates_snet") %>%
  select(-record_id)

# consumption dataframe
consumption <- dbGetQuery(con, "SELECT * FROM complete_consumption") %>%
  select(-record_id)

# Production dataframe
prod <- dbGetQuery(con, "SELECT * FROM production") %>%
  select(-record_id)

# Species metadata
sciname_metadata <- dbGetQuery(con, "SELECT * FROM sciname") %>%
  select(-record_id)

# Improved taxa resolution metadata
sciname_hs_modified <- dbGetQuery(con, "SELECT * FROM code_max_resolved_taxa") %>%
  select(-record_id)

# Close database connection
dbDisconnect(con)
rm(list = c("con"))

artis <- artis %>%
  # Add details on sanctions following annexation of Crimea
    mutate(sanctions_towards_russia = case_when(
      importer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No"
    )) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No")) %>% 
  left_join(sciname_metadata %>% 
              select(sciname, common_name), 
            by = "sciname") %>% 
  mutate(source_sanctions_towards_russia = case_when(
      source_country_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No")) %>% 
  left_join(sciname_metadata %>% 
              select(sciname, common_name), 
            by = "sciname")

consumption <- consumption %>%
  filter(source_country_iso3c == "RUS"|exporter_iso3c == "RUS"|consumer_iso3c == "RUS") %>%
  # Add details on sanctions following annexation of Crimea
    mutate(sanctions_towards_russia = case_when(
      consumer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", 
                            "NLD", # FIXIT: Need to find out what is happening with the Netherlands and others directly importing
                            "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
      TRUE ~ "Did not impose sanctions"
    )) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
      TRUE ~ "Did not impose sanctions")) %>%
    mutate(source_sanctions_towards_russia = case_when(
      source_country_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
      TRUE ~ "Did not impose sanctions")) %>% 
    left_join(sciname_metadata %>% 
              select(sciname, common_name), 
            by = "sciname") %>%
  left_join(sciname_metadata %>% 
              select(sciname, "common_name_hs_modified" = "common_name"), 
            by = c("sciname_hs_modified" = "sciname"))

```

```{r}
consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t)) +
  geom_line()

consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", fill = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal()

consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
  geom_line() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_color_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", color = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal()

# Change in consumption stats
# Change in total consumption of Russian products - imposed sanctions
consumption_change <- consumption %>%
  filter(sanctions_towards_russia == "Imposed sanctions", 
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

100*(q_post - q_pre)/q_pre

# Change in consumption of Russian products via direct import - imposed sanctions
consumption_change <- consumption %>%
  filter(sanctions_towards_russia == "Imposed sanctions", 
         exporter_iso3c == "RUS",
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

100*(q_post - q_pre)/q_pre

# Change in consumption of Russian products via indirect import - imposed sanctions
consumption_change <- consumption %>%
  filter(sanctions_towards_russia == "Imposed sanctions", 
         exporter_iso3c != "RUS",
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

100*(q_post - q_pre)/q_pre

# Change in total consumption of Russian products  - didn't impose sanctions
consumption_change <- consumption %>%
  filter(sanctions_towards_russia == "Did not impose sanctions", 
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

100*(q_post - q_pre)/q_pre

```

```{r}
consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t)) +
  geom_line()

consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  mutate(path = case_when(
    source_country_iso3c == exporter_iso3c ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, source_sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", fill = "") +
  facet_wrap(~source_sanctions_towards_russia) +
  theme_minimal()

consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  mutate(path = case_when(
    source_country_iso3c == exporter_iso3c ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, source_sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
  geom_line() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_color_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", color = "") +
  facet_wrap(~source_sanctions_towards_russia) +
  theme_minimal()

# Change in Russia's consumption from countries imposing sanctions
consumption_change <- consumption %>%
  filter(source_sanctions_towards_russia == "Imposed sanctions", 
         consumer_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

100*(q_post - q_pre)/q_pre

# Change in Russia's consumption from countries imposing sanctions - direct imports
consumption_change <- consumption %>%
  filter(source_sanctions_towards_russia == "Imposed sanctions", 
         source_country_iso3c == exporter_iso3c,
         consumer_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

100*(q_post - q_pre)/q_pre

```

```{r}
consumption %>%
  filter(sanctions_towards_russia == "Imposed sanctions", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", fill = "") +
  theme_minimal()

consumption %>%
  filter(sanctions_towards_russia == "Imposed sanctions", 
         source_country_iso3c == "RUS", 
         year > 2014) %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, consumer_iso3c, path) %>%
  summarise(consumption_live_t = sum(consumption_live_t))

```

```{r}
rus_us_sankey <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  rename("importer_iso3c" = "consumer_iso3c",
         "live_weight_t" = "consumption_live_t") %>%
  plot_sankey(prop_flow_cutoff = 0.01)

ggexport(rus_us_sankey, filename = "rus_us_sankey.png", width = 800, height = 400)

species_rank <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  rename("importer_iso3c" = "consumer_iso3c",
         "live_weight_t" = "consumption_live_t") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path")

ggexport(species_rank, filename = "US_species_rank.png")

# Stats for paper
# Percent by exporter
consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
  group_by(exporter_iso3c) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
  arrange(desc(percent))

# Percent by species
consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
  group_by(common_name_hs_modified) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
  arrange(desc(percent))

```

```{r}
rus_to_chn <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "RUS", importer_iso3c == "CHN") %>%
  group_by(year, sciname) %>%
  summarise(russia_live_t = sum(live_weight_t, na.rm = TRUE))

notrus_to_chn <- artis %>%
  filter(source_country_iso3c != "RUS", exporter_iso3c != "RUS", importer_iso3c == "CHN") %>%
  group_by(year, sciname) %>%
  summarise(notrussia_live_t = sum(live_weight_t, na.rm = TRUE))

chn_to_usa <- artis %>%
  filter(exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
  left_join(rus_to_chn, by = c("year", "sciname")) %>%
  left_join(notrus_to_chn, by = c("year", "sciname")) %>%
  replace_na(list(russia_live_t = 0, notrussia_live_t = 0)) %>% 
  mutate(min_russia = case_when(
    (notrussia_live_t >= live_weight_t) ~ 0,
    (live_weight_t - notrussia_live_t) >= russia_live_t ~ russia_live_t,
    TRUE ~ (live_weight_t - notrussia_live_t)
  )) %>% 
  mutate(max_russia = case_when(
    russia_live_t >= live_weight_t ~ live_weight_t, 
    russia_live_t < live_weight_t ~ russia_live_t
  ))

p1 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "gadus chalcogrammus") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Alaska pollock via China") +
  theme_bw()

p2 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "oncorhynchus gorbuscha") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian pink salmon via China") +
  theme_bw()

p3 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
         year > 1996) %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "gadus morhua") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Atlantic cod via China") +
  theme_bw()

p_joined <- ggarrange(p1, p2, p3, ncol = 1)

ggexport(p_joined, filename = "US_species_import_range.png")

# Stats
chn_to_usa %>% 
  filter(year == 2020, 
         sciname %in% c("gadus chalcogrammus", "gadus morhua", "oncorhynchus gorbuscha"))

```

### 2024-02-29 ms-russia-figures.Rmd
add two new species min/max plots

@@
 
-p_joined <- ggarrange(p1, p2, p3, ncol = 1)
+p4 <- artis %>%
+  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
+         year > 1996) %>%
+  group_by(year, sciname) %>%
+  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
+  filter(sciname == "melanogrammus aeglefinus") %>%
+  left_join(chn_to_usa %>%
+              select(year, sciname, min_russia, max_russia)) %>% 
+  ggplot(aes(x = year)) +
+  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
+  geom_line(aes(y = live_weight_t)) +
+  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian haddock via China") +
+  theme_bw()
+
+p5 <- artis %>%
+  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
+         year > 1996) %>%
+  group_by(year, sciname) %>%
+  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
+  filter(sciname == "gadus macrocephalus") %>%
+  left_join(chn_to_usa %>%
+              select(year, sciname, min_russia, max_russia)) %>% 
+  ggplot(aes(x = year)) +
+  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
+  geom_line(aes(y = live_weight_t)) +
+  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Pacific cod via China") +
+  theme_bw()
+
+p_joined <- ggarrange(p1, p2, p3, p4, ncol = 1)
 
@@
   filter(year == 2020, 
-         sciname %in% c("gadus chalcogrammus", "gadus morhua", "oncorhynchus gorbuscha"))
+         sciname %in% c("gadus chalcogrammus", "gadus morhua", "oncorhynchus gorbuscha", "gadus macrocephalus"))
+
+consumption %>%
+  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
+  group_by(sciname_hs_modified) %>% 
+  summarise(consumption_live_t = sum(consumption_live_t)) %>% 
+  arrange(desc(consumption_live_t)) %>%
+  ungroup() %>%
+  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
+  mutate(cum_percent = cumsum(percent))
 

### 2024-02-29 ms-russia-figures.Rmd
Add comments throughout

@@
 artis <- artis %>%
-  # Add details on sanctions following annexation of Crimea
+  # Add variables for whether source/importer/exporter imposed sanctions following annexation of Crimea
     mutate(sanctions_towards_russia = case_when(
@@
       TRUE ~ "No")) %>% 
+  # Join on common names
   left_join(sciname_metadata %>% 
@@
 consumption <- consumption %>%
+  # Filter consumption to when Russia is involved
   filter(source_country_iso3c == "RUS"|exporter_iso3c == "RUS"|consumer_iso3c == "RUS") %>%
-  # Add details on sanctions following annexation of Crimea
+  # Add variables for whether source/importer/exporter imposed sanctions following annexation of Crimea
     mutate(sanctions_towards_russia = case_when(
@@
       TRUE ~ "Did not impose sanctions")) %>% 
+  # Add common names (for both sciname and sciname_hs_modified)
     left_join(sciname_metadata %>% 
@@
 ```{r}
-consumption %>%
-  filter(consumer_iso3c != "RUS", 
-         source_country_iso3c == "RUS") %>%
-  group_by(year) %>%
-  summarise(consumption_live_t = sum(consumption_live_t)) %>%
-  ggplot(aes(x = year, y = consumption_live_t)) +
-  geom_line()
-
+# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
+# Fill version
 consumption %>%
@@
   )) + 
-  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", fill = "") +
+  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", fill = "") +
   facet_wrap(~sanctions_towards_russia) +
-  theme_minimal()
+  theme_minimal() +
+  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap
 
+# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
+# Line version
 consumption %>%
@@
   )) + 
-  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", color = "") +
+  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", color = "") +
   facet_wrap(~sanctions_towards_russia) +
-  theme_minimal()
+  theme_minimal() +
+  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap
 
@@
 
+paste("Change in consumption of Russian products via indirect import - imposed sanctions")
 100*(q_post - q_pre)/q_pre
@@
 
+paste("Change in total consumption of Russian products  - didn't impose sanctions")
 100*(q_post - q_pre)/q_pre
@@
 ```{r}
-consumption %>%
-  filter(consumer_iso3c == "RUS", 
-         source_country_iso3c != "RUS") %>%
-  group_by(year) %>%
-  summarise(consumption_live_t = sum(consumption_live_t)) %>%
-  ggplot(aes(x = year, y = consumption_live_t)) +
-  geom_line()
-
+# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
+# Fill version
 consumption %>%
@@
   )) + 
-  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", fill = "") +
+  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", fill = "") +
   facet_wrap(~source_sanctions_towards_russia) +
-  theme_minimal()
+  theme_minimal() +
+  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap
 
+# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
+# Line version
 consumption %>%
@@
   )) + 
-  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", color = "") +
+  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", color = "") +
   facet_wrap(~source_sanctions_towards_russia) +
-  theme_minimal()
+  theme_minimal() +
+  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap
 
@@
 
+paste("Change in Russia's consumption from countries imposing sanctions")
 100*(q_post - q_pre)/q_pre
@@
 
+paste("Change in Russia's consumption from countries imposing sanctions - direct imports")
 100*(q_post - q_pre)/q_pre
@@
 ```{r}
-consumption %>%
-  filter(sanctions_towards_russia == "Imposed sanctions", 
-         source_country_iso3c == "RUS") %>%
-  mutate(path = case_when(
-    exporter_iso3c == "RUS" ~ "Direct import", 
-    TRUE ~ "Import from intermediate partner"
-  )) %>% 
-  group_by(year, path) %>%
-  summarise(consumption_live_t = sum(consumption_live_t)) %>%
-  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
-  geom_area() +
-  geom_vline(aes(xintercept = 2014), linetype = 2) +
-  scale_fill_manual(values = c("#D4B95f", # khaki
-                               "#4FA2A2" # teal
-  )) + 
-  labs(x = "", y = "Consumption of Russian seafood (mil t, live weight)", fill = "") +
-  theme_minimal()
-
-consumption %>%
-  filter(sanctions_towards_russia == "Imposed sanctions", 
-         source_country_iso3c == "RUS", 
-         year > 2014) %>%
-  mutate(path = case_when(
-    exporter_iso3c == "RUS" ~ "Direct import", 
-    TRUE ~ "Import from intermediate partner"
-  )) %>% 
-  group_by(year, consumer_iso3c, path) %>%
-  summarise(consumption_live_t = sum(consumption_live_t))
-
-```
-
-```{r}
+# Sankey diagram of flows of Russian products into the US
 rus_us_sankey <- consumption %>%
@@
 
+# Top species US consumes sourced from Russia
 species_rank <- consumption %>%
@@
          "live_weight_t" = "consumption_live_t") %>%
-  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path")
+  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path") + 
+  theme(legend.position = "bottom")
 
@@
 
+# FIXIT:Pull out stats from these data frames to print the one for the paper
+
 ```
@@
   replace_na(list(russia_live_t = 0, notrussia_live_t = 0)) %>% 
+  # Calculate the minimum by year and species that had to come from Russia
   mutate(min_russia = case_when(
+    # If non-Russian product exceeds the volume sent to the US, 
+    # then min that had to be Russian is 0
     (notrussia_live_t >= live_weight_t) ~ 0,
+    # If non-Russian product cannot explain all, then fill up remaining with Russian product
     (live_weight_t - notrussia_live_t) >= russia_live_t ~ russia_live_t,
+    # Otherwise fill up remaining with Russian product
     TRUE ~ (live_weight_t - notrussia_live_t)
   )) %>% 
+  # Calculate the max that could have come from Russia
   mutate(max_russia = case_when(
+    # If Russian product can explain full amount, max is total trade flow
     russia_live_t >= live_weight_t ~ live_weight_t, 
+    # If Russian product cannont explain all, fill up with Russian product to get max
     russia_live_t < live_weight_t ~ russia_live_t
@@
 
+# FIXIT: This can be streamlined to not repeat code
 p1 <- artis %>%

### 2024-03-13 ms-russia-figures.Rmd
Add exploratory figures to identify source of consumption spike

@@
 ```
+
+To do: 
+-
 
@@
 prod <- dbGetQuery(con, "SELECT * FROM production") %>%
+  select(-record_id)
+
+# Product metadata dataframe
+product <- dbGetQuery(con, "SELECT * FROM products") %>%
   select(-record_id)
@@
 ```
+
+```{r}
+# Explore spike in China's apparent consumption of Russian products
+tmp <- consumption %>% 
+  filter(source_country_iso3c == "RUS", consumer_iso3c != "RUS") %>%
+  group_by(year, consumer_iso3c) %>% 
+  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
+
+consumption %>% 
+  filter(source_country_iso3c == "RUS", consumer_iso3c == "CHN") %>%
+  group_by(year) %>% 
+  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
+  ggplot(aes(x = year, y = consumption_live_t)) +
+  geom_line() + 
+  theme_bw()
+
+tmp <- consumption %>% 
+  filter(source_country_iso3c == "RUS", consumer_iso3c == "CHN") %>%
+  group_by(year, sciname_hs_modified) %>% 
+  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
+
+prod %>% 
+  filter(iso3c == "RUS", sciname == "gadus chalcogrammus") %>%
+  group_by(year) %>%
+  summarise(live_weight_t = sum(live_weight_t)) %>%
+  ggplot(aes(x = year, y = live_weight_t)) +
+  geom_line() +
+  theme_bw()
+
+artis %>% 
+  filter(exporter_iso3c == "RUS", importer_iso3c == "CHN") %>%
+  plot_ts(artis_var = "hs6", plot.type = "filled", prop_flow_cutoff = 0.07)
+
+artis %>% 
+  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN") %>%
+  group_by(year) %>%
+  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
+  ggplot(aes(year, live_weight_t)) +
+  geom_line() +
+  theme_bw()
+
+artis %>% 
+  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN") %>%
+  plot_ts(artis_var = "importer_iso3c", plot.type = "filled")
+
+artis %>% 
+  filter(hs6 %in% c(30379, 30380, 303429, 30499, 30510, 30520, 
+                    30530, 30549, 30569, 51191, 1400410, 140420,
+                    160419, 160430), exporter_iso3c == "CHN") %>%
+  plot_ts(artis_var = "hs6", plot.type = "filled")
+
+```

### 2024-03-14 ms-russia-figures.Rmd
change panel labels

@@
     mutate(sanctions_towards_russia = case_when(
-      consumer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", 
-                            "NLD", # FIXIT: Need to find out what is happening with the Netherlands and others directly importing
-                            "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
-      TRUE ~ "Did not impose sanctions"
+      consumer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", 
+                            "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Russia unfriendly countries",
+      TRUE ~ "Russia friendly countries"
     )) %>%
       mutate(exporter_sanctions_towards_russia = case_when(
-      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
-      TRUE ~ "Did not impose sanctions")) %>%
+      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Russia unfriendly countries",
+      TRUE ~ "Russia friendly countries")) %>%
     mutate(source_sanctions_towards_russia = case_when(
-      source_country_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
-      TRUE ~ "Did not impose sanctions")) %>% 
+      source_country_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Russia unfriendly countries",
+      TRUE ~ "Russia friendly countries")) %>% 
   # Add common names (for both sciname and sciname_hs_modified)
@@
 # Fill version
-consumption %>%
+consumption_russian_ts_fill <- consumption %>%
   filter(consumer_iso3c != "RUS", 
@@
 
+consumption_russian_ts_fill
+
 # Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
 # Line version
-consumption %>%
+consumption_russian_ts_line <- consumption %>%
   filter(consumer_iso3c != "RUS", 
@@
 
+consumption_russian_ts_line
+
 # Change in consumption stats
@@
 consumption_change <- consumption %>%
-  filter(sanctions_towards_russia == "Imposed sanctions", 
+  filter(sanctions_towards_russia == "Russia unfriendly countries", 
          source_country_iso3c == "RUS") %>%
@@
 consumption_change <- consumption %>%
-  filter(sanctions_towards_russia == "Imposed sanctions", 
+  filter(sanctions_towards_russia == "Russia unfriendly countries", 
          exporter_iso3c == "RUS",
@@
 consumption_change <- consumption %>%
-  filter(sanctions_towards_russia == "Imposed sanctions", 
+  filter(sanctions_towards_russia == "Russia unfriendly countries", 
          exporter_iso3c != "RUS",
@@
 consumption_change <- consumption %>%
-  filter(sanctions_towards_russia == "Did not impose sanctions", 
+  filter(sanctions_towards_russia == "Russia friendly countries", 
          source_country_iso3c == "RUS") %>%
@@
 # Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
+
 # Fill version
-consumption %>%
+consumption_by_russia_ts_fill <- consumption %>%
   filter(consumer_iso3c == "RUS", 
@@
   theme_minimal() +
-  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap
+  theme(legend.position = "bottom")
+
+consumption_by_russia_ts_fill
 
@@
 # Line version
-consumption %>%
+consumption_by_russia_ts_line <- consumption %>%
   filter(consumer_iso3c == "RUS", 
@@
 
+consumption_by_russia_ts_line
+
 # Change in Russia's consumption from countries imposing sanctions
 consumption_change <- consumption %>%
-  filter(source_sanctions_towards_russia == "Imposed sanctions", 
+  filter(source_sanctions_towards_russia == "Russia unfriendly countries", 
          consumer_iso3c == "RUS") %>%
@@
 consumption_change <- consumption %>%
-  filter(source_sanctions_towards_russia == "Imposed sanctions", 
+  filter(source_sanctions_towards_russia == "Russia unfriendly countries", 
          source_country_iso3c == exporter_iso3c,
@@
 
+```
+```{r, fig.height=6}
+# Join plots
+ggarrange(consumption_russian_ts_fill, consumption_by_russia_ts_fill, 
+          common.legend = TRUE, ncol = 1)
+
+ggarrange(consumption_russian_ts_line, consumption_by_russia_ts_line, 
+          common.legend = TRUE, ncol = 1)
 ```

### 2024-03-14 ms-russia-figures.Rmd
figure edits

--- 2024-03-13 ms-russia-figures.Rmd
@@
 # ARTIS dataframe
-artis <- dbGetQuery(con, "SELECT * FROM all_estimates_snet") %>%
+artis <- dbGetQuery(con, "SELECT * FROM snet") %>%
   select(-record_id)
@@
 # Fill version
-consumption %>%
+consumption_of_rus_p <- consumption %>%
   filter(consumer_iso3c != "RUS", 
@@
   theme_minimal() +
-  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap
+  theme(
+    axis.title.y = element_text(size = 9),
+    legend.position = "top",
+    panel.spacing = unit(5, "mm")
+  )
+
+consumption_of_rus_p
 
@@
   theme_minimal() +
-  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap
+  theme(
+    legend.position = "bottom",
+    panel.spacing = unit(5, "mm")
+  )
 
@@
 # Fill version
-consumption %>%
+rus_foreign_consumption_p <- consumption %>%
   filter(consumer_iso3c == "RUS", 
@@
   theme_minimal() +
-  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap
+  theme(
+    axis.title.y = element_text(size = 9),
+    legend.position = "top",
+    panel.spacing = unit(5, "mm")
+  )
+
+rus_foreign_consumption_p
 
@@
 
+```{r fig.height = 6, width = 8}
+# Format figure 1 together
+ggarrange(
+  consumption_of_rus_p,
+  rus_foreign_consumption_p,
+  nrow = 2,
+  common.legend = TRUE
+)
+
+ggsave("fig1.png", device = "png", height = 5, width = 6.5, units = "in")
+```
+
 ```{r}
@@
     exporter_iso3c == "RUS" ~ "Direct import", 
-    TRUE ~ "Import from intermediate partner"
+    TRUE ~ "Import from\nintermediate partner"
   )) %>% 
@@
          "live_weight_t" = "consumption_live_t") %>%
-  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path") + 
-  theme(legend.position = "bottom")
+  mutate(common_name_hs_modified = case_when(
+    common_name_hs_modified == "alaska pollock(=walleye poll.)" ~ "Alaska Pollock",
+    common_name_hs_modified == "atlantic cod" ~ "Atlantic Cod",
+    common_name_hs_modified == "pink(=humpback) salmon" ~ "Pink Salmon",
+    common_name_hs_modified == "haddock" ~ "Haddock",
+    common_name_hs_modified == "pacific cod" ~ "Pacific Cod",
+    TRUE ~ common_name_hs_modified
+  )) %>%
+  mutate(common_name_hs_modified = gsub(" ", "\n", common_name_hs_modified)) %>%
+  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
+  theme(
+    legend.position = "bottom",
+    axis.text.y = element_text(angle = 90),
+
+  ) +
+  labs(y = "", x = "Consumption (live weight tonnes)", fill = "")
 
@@
 rus_to_chn <- artis %>%
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "RUS", importer_iso3c == "CHN") %>%
+  # Isolating Chinese imports that were originally caught in Russia
+  filter(source_country_iso3c == "RUS", importer_iso3c == "CHN") %>%
   group_by(year, sciname) %>%
@@
 notrus_to_chn <- artis %>%
-  filter(source_country_iso3c != "RUS", exporter_iso3c != "RUS", importer_iso3c == "CHN") %>%
+  # Isolating Chinese imports that were NOT originally caught in Russia
+  filter(source_country_iso3c != "RUS", importer_iso3c == "CHN") %>%
   group_by(year, sciname) %>%
@@
 
-# FIXIT: This can be streamlined to not repeat code
-p1 <- artis %>%
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
-  group_by(year, sciname) %>%
-  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
-  filter(sciname == "gadus chalcogrammus") %>%
-  left_join(chn_to_usa %>%
-              select(year, sciname, min_russia, max_russia)) %>% 
-  ggplot(aes(x = year)) +
-  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
-  geom_line(aes(y = live_weight_t)) +
-  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Alaska pollock via China") +
-  theme_bw()
-
-p2 <- artis %>%
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
-  group_by(year, sciname) %>%
-  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
-  filter(sciname == "oncorhynchus gorbuscha") %>%
-  left_join(chn_to_usa %>%
-              select(year, sciname, min_russia, max_russia)) %>% 
-  ggplot(aes(x = year)) +
-  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
-  geom_line(aes(y = live_weight_t)) +
-  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian pink salmon via China") +
-  theme_bw()
-
-p3 <- artis %>%
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
-         year > 1996) %>%
-  group_by(year, sciname) %>%
-  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
-  filter(sciname == "gadus morhua") %>%
-  left_join(chn_to_usa %>%
-              select(year, sciname, min_russia, max_russia)) %>% 
-  ggplot(aes(x = year)) +
-  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
-  geom_line(aes(y = live_weight_t)) +
-  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Atlantic cod via China") +
-  theme_bw()
-
-p4 <- artis %>%
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
-         year > 1996) %>%
-  group_by(year, sciname) %>%
-  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
-  filter(sciname == "melanogrammus aeglefinus") %>%
-  left_join(chn_to_usa %>%
-              select(year, sciname, min_russia, max_russia)) %>% 
-  ggplot(aes(x = year)) +
-  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
-  geom_line(aes(y = live_weight_t)) +
-  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian haddock via China") +
-  theme_bw()
-
-p5 <- artis %>%
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
-         year > 1996) %>%
-  group_by(year, sciname) %>%
-  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
-  filter(sciname == "gadus macrocephalus") %>%
-  left_join(chn_to_usa %>%
-              select(year, sciname, min_russia, max_russia)) %>% 
-  ggplot(aes(x = year)) +
-  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
-  geom_line(aes(y = live_weight_t)) +
-  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Pacific cod via China") +
-  theme_bw()
-
-p_joined <- ggarrange(p1, p2, p3, p4, ncol = 1)
-
-ggexport(p_joined, filename = "US_species_import_range.png")
-
 # Stats
@@
 
+```
+
+```{r}
+rus_chn_usa <- artis %>%
+  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
+  group_by(year, sciname) %>%
+  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
+  ungroup() %>%
+  left_join(chn_to_usa %>%
+            select(year, sciname, min_russia, max_russia)) %>%
+  mutate(live_weight_t = live_weight_t / 1e3,
+         min_russia = min_russia / 1e3,
+         max_russia = max_russia / 1e3)
+
+p1 <- rus_chn_usa %>% 
+  filter(sciname == "gadus chalcogrammus",
+         year > 1996) %>%
+  ggplot(aes(x = year)) +
+  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
+  geom_line(aes(y = live_weight_t)) +
+  xlim(1997, 2020) +
+  scale_y_continuous(position = "right") +
+  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Alaska pollock via China") +
+  theme_bw() +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.x = element_blank(),
+    plot.margin = margin(l = 2, b = -2, unit = "mm")
+  )
+
+p2 <- rus_chn_usa %>%
+  filter(year > 1996,
+         sciname == "gadus morhua") %>%
+  left_join(chn_to_usa %>%
+              select(year, sciname, min_russia, max_russia)) %>% 
+  ggplot(aes(x = year)) +
+  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
+  geom_line(aes(y = live_weight_t)) +
+  scale_y_continuous(position = "right") +
+  xlim(1997, 2020) +
+  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Atlantic cod via China") +
+  theme_bw() +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.x = element_blank(),
+    plot.margin = margin(r = 2, l = 2, b = -2, unit = "mm")
+  )
+
+p3 <- rus_chn_usa %>%
+  filter(sciname == "oncorhynchus gorbuscha",
+         year > 1996) %>%
+  ggplot(aes(x = year)) +
+  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
+  geom_line(aes(y = live_weight_t)) +
+  scale_y_continuous(position = "right") +
+  xlim(1997, 2020) +
+  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian pink salmon via China") +
+  theme_bw() +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.x = element_blank(),
+    plot.margin = margin(r = 2, l = 2, b = -2, unit = "mm")
+  )
+
+p4 <- rus_chn_usa %>%
+  filter(sciname == "melanogrammus aeglefinus",
+         year > 1996) %>%
+  ggplot(aes(x = year)) +
+  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
+  geom_line(aes(y = live_weight_t)) +
+  scale_y_continuous(position = "right") +
+  xlim(1997, 2020) +
+  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian haddock via China") +
+  theme_bw() +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.x = element_blank(),
+    plot.margin = margin(l = 2, b = -2, r = 1.5, unit = "mm")
+  )
+
+p5 <- rus_chn_usa %>%
+  filter(sciname == "gadus macrocephalus",
+         year > 1996) %>%
+  ggplot(aes(x = year)) +
+  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
+  geom_line(aes(y = live_weight_t)) +
+  scale_y_continuous(position = "right") +
+  xlim(1997, 2020) +
+  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Pacific cod via China") +
+  theme_bw() +
+  theme(
+    axis.title.y = element_blank(),
+    plot.margin = margin(t = -1, r = 2, l = 2, b = -2, unit = "mm")
+  )
+
+p_joined <- ggarrange(p1, p2, p3, p4, p5, ncol = 1)
+
+ggexport(p_joined, filename = "US_species_import_range.png")
+
+# Top species US consumes sourced from Russia
+
+species_rank_df <- consumption %>%
+  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
+  mutate(path = case_when(
+    exporter_iso3c == "RUS" ~ "Direct\nimport", 
+    TRUE ~ "Import from\nintermediate partner"
+  )) %>% 
+  rename("importer_iso3c" = "consumer_iso3c",
+         "live_weight_t" = "consumption_live_t") %>%
+  mutate(common_name_hs_modified = case_when(
+    common_name_hs_modified == "alaska pollock(=walleye poll.)" ~ "Alaska Pollock",
+    common_name_hs_modified == "atlantic cod" ~ "Atlantic Cod",
+    common_name_hs_modified == "pink(=humpback) salmon" ~ "Pink Salmon",
+    common_name_hs_modified == "haddock" ~ "Haddock",
+    common_name_hs_modified == "pacific cod" ~ "Pacific Cod",
+    TRUE ~ common_name_hs_modified
+  )) %>%
+  mutate(common_name_hs_modified = gsub(" ", "\n", common_name_hs_modified)) %>%
+  mutate(live_weight_t = live_weight_t / length(2015:2019)) %>%
+  mutate(live_weight_t = live_weight_t / 1e3)
+
+species_rank_1 <- species_rank_df %>%
+  filter(common_name_hs_modified == "Alaska\nPollock") %>%
+  mutate(dom_source == "") %>%
+  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) +
+  xlim(0, 90) +
+  theme(
+    legend.position = "none",
+    axis.text.x = element_blank(),
+    axis.text.y = element_text(angle = 90, hjust = 0.5),
+    plot.margin = margin(b = -2, unit = "mm")
+  ) +
+  labs(y = "", x = "", fill = "")
+
+species_rank_2 <- species_rank_df %>%
+  filter(common_name_hs_modified == "Atlantic\nCod") %>%
+  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
+  xlim(0, 90) +
+  theme(
+    legend.position = "none",
+    axis.text.x = element_blank(),
+    axis.text.y = element_text(angle = 90, hjust = 0.5),
+    plot.margin = margin(b = -2, unit = "mm")
+  ) +
+  labs(y = "", x = "", fill = "")
+
+species_rank_3 <- species_rank_df %>%
+  filter(common_name_hs_modified == "Pink\nSalmon") %>%
+  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
+  xlim(0, 90) +
+  theme(
+    legend.position = "none",
+    axis.text.x = element_blank(),
+    axis.text.y = element_text(angle = 90, hjust = 0.5),
+    plot.margin = margin(b = -2, unit = "mm")
+  ) +
+  labs(y = "", x = "", fill = "")
+
+species_rank_4 <- species_rank_df %>%
+  filter(common_name_hs_modified == "Haddock") %>%
+  mutate(common_name_hs_modified = paste("\n", common_name_hs_modified, sep = "")) %>%
+  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
+  xlim(0, 90) +
+  theme(
+    legend.position = "none",
+    axis.text.x = element_blank(),
+    axis.text.y = element_text(angle = 90, hjust = 0.5),
+    plot.margin = margin(b = -2, unit = "mm")
+  ) +
+  labs(y = "", x = "", fill = "")
+
+species_rank_5 <- species_rank_df %>%
+  filter(common_name_hs_modified == "Pacific\nCod") %>%
+  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
+  xlim(0, 90) +
+  theme(
+    legend.position = "bottom",
+    axis.text.y = element_text(angle = 90, hjust = 0.5),
+    axis.title.x = element_text(size = 7),
+    legend.key.size = unit(1, units = "line"),
+    plot.margin = margin(t = -2, b = -1, unit = "mm")
+  ) +
+  labs(y = "", x = "Avg. Consumption (1000 t) (2015-2019)", fill = "")
+
+# Format Figure 2 together
+fig2 <- ggarrange(
+  species_rank_1, p1,
+  species_rank_2, p2,
+  species_rank_3, p3,
+  species_rank_4, p4,
+  species_rank_5, p5,
+  ncol = 2, nrow = 5,
+  widths = c(1, 2),
+  heights = c(1, 1, 1, 1, 1),
+  common.legend = TRUE,
+  legend = "bottom"
+  )
+
+fig2
+
+fig2 <- annotate_figure(
+  fig2,
+  right = text_grob("US Imports of Russian Species (1000 t, live weight)", rot = 270)
+  )
+
+fig2 <- ggarrange(
+  rus_us_sankey,
+  fig2,
+  nrow = 2,
+  heights = c(1, 2)
+)
+
+fig2
+
+ggsave("fig2.png", device = "png", width = 6.5, height = 6)
 ```

### 2024-03-14 ms-russia-figures.Rmd

@@
 # Fill version
-consumption_of_rus_p <- consumption %>%
+
+consumption_russian_ts_fill <- consumption %>%
   filter(consumer_iso3c != "RUS", 
@@
     TRUE ~ "Import from intermediate partner"
+  )) %>%
+  mutate(sanctions_towards_russia = case_when(
+    sanctions_towards_russia == "Did not impose sanctions" ~ "Friendly countries' consumption\nof seafood from Russia",
+    TRUE ~ "Unfriendly countries' consumption\nof seafood from Russia"
   )) %>% 
@@
   )) + 
-  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", fill = "") +
+  labs(x = "", y = "Consumption (mil t, live weight)", fill = "") +
   facet_wrap(~sanctions_towards_russia) +
@@
 
-consumption_of_rus_p
+consumption_russian_ts_fill
 
@@
 # Line version
-consumption %>%
+consumption_russian_ts_line <- consumption %>%
   filter(consumer_iso3c != "RUS", 
@@
 # Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
+
 # Fill version
-rus_foreign_consumption_p <- consumption %>%
+consumption_by_russia_ts_fill <- consumption %>%
   filter(consumer_iso3c == "RUS", 
@@
     TRUE ~ "Import from intermediate partner"
+  )) %>% 
+  mutate(source_sanctions_towards_russia = case_when(
+    source_sanctions_towards_russia == "Did not impose sanctions" ~ "Russian consumption of seafood\nfrom friendly countries",
+    TRUE ~ "Russian consumption of seafood\nfrom unfriendly countries"
   )) %>%
@@
   )) + 
-  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", fill = "") +
+  labs(x = "", y = "Consumption (mil t, live weight)", fill = "") +
   facet_wrap(~source_sanctions_towards_russia) +
@@
 
-rus_foreign_consumption_p
+consumption_by_russia_ts_fill
 
@@
 
+consumption_by_russia_ts_line
+
 # Change in Russia's consumption from countries imposing sanctions
 consumption_change <- consumption %>%
-  filter(source_sanctions_towards_russia == "Imposed sanctions", 
+  filter(source_sanctions_towards_russia == "Russia unfriendly countries", # FIXIT
          consumer_iso3c == "RUS") %>%
@@
 
+```
+```{r, fig.height=6}
+# Join plots
+ggarrange(consumption_russian_ts_fill, consumption_by_russia_ts_fill, 
+          common.legend = TRUE, ncol = 1, legend = "bottom")
+
+ggsave("fig1.png", device = "png", width = 6.5, height = 5, unit = "in")
+
+ggarrange(consumption_russian_ts_line, consumption_by_russia_ts_line, 
+          common.legend = TRUE, ncol = 1)
 ```

### 2024-04-17 ms-russia-figures.Rmd
new structure for figures and preparing data

--- 2024-03-14 ms-russia-figures.Rmd
@@
 ---
-title: "Russian sanctions figures"
+title: "ms-russia-figs-analysis"
 output: html_document
-date: "2024-02-07"
+date: "2024-04-17"
 ---
@@
 ```
-
-To do: 
--
 
@@
 )
+
+datadir <- "data"
+figdir <- "figures"
 ```
@@
 ```{r}
-# Initial database pulls
-
-# Database connection
-con <- dbConnect(RPostgres::Postgres(),
-                 dbname=Sys.getenv("DB_NAME"),
-                 host="localhost",
-                 port="5432",
-                 user=Sys.getenv("DB_USERNAME"),
-                 password=Sys.getenv("DB_PASSWORD"))
-
-# Check that connection is established by checking which tables are present
-dbListTables(con)
-
-# ARTIS dataframe
-artis <- dbGetQuery(con, "SELECT * FROM snet") %>%
-  select(-record_id)
-
-# consumption dataframe
-consumption <- dbGetQuery(con, "SELECT * FROM complete_consumption") %>%
-  select(-record_id)
-
-# Production dataframe
-prod <- dbGetQuery(con, "SELECT * FROM production") %>%
-  select(-record_id)
-
-# Product metadata dataframe
-product <- dbGetQuery(con, "SELECT * FROM products") %>%
-  select(-record_id)
-
-# Species metadata
-sciname_metadata <- dbGetQuery(con, "SELECT * FROM sciname") %>%
-  select(-record_id)
-
-# Improved taxa resolution metadata
-sciname_hs_modified <- dbGetQuery(con, "SELECT * FROM code_max_resolved_taxa") %>%
-  select(-record_id)
-
-# Close database connection
-dbDisconnect(con)
-rm(list = c("con"))
-
-artis <- artis %>%
-  # Add variables for whether source/importer/exporter imposed sanctions following annexation of Crimea
-    mutate(sanctions_towards_russia = case_when(
-      importer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
-      TRUE ~ "No"
-    )) %>%
-      mutate(exporter_sanctions_towards_russia = case_when(
-      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
-      TRUE ~ "No")) %>% 
-  left_join(sciname_metadata %>% 
-              select(sciname, common_name), 
-            by = "sciname") %>% 
-  mutate(source_sanctions_towards_russia = case_when(
-      source_country_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
-      TRUE ~ "No")) %>% 
-  # Join on common names
-  left_join(sciname_metadata %>% 
-              select(sciname, common_name), 
-            by = "sciname")
-
-consumption <- consumption %>%
-  # Filter consumption to when Russia is involved
-  filter(source_country_iso3c == "RUS"|exporter_iso3c == "RUS"|consumer_iso3c == "RUS") %>%
-  # Add variables for whether source/importer/exporter imposed sanctions following annexation of Crimea
-    mutate(sanctions_towards_russia = case_when(
-      consumer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", 
-                            "NLD", # FIXIT: Need to find out what is happening with the Netherlands and others directly importing
-                            "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
-      TRUE ~ "Did not impose sanctions"
-    )) %>%
-      mutate(exporter_sanctions_towards_russia = case_when(
-      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
-      TRUE ~ "Did not impose sanctions")) %>%
-    mutate(source_sanctions_towards_russia = case_when(
-      source_country_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Imposed sanctions",
-      TRUE ~ "Did not impose sanctions")) %>% 
-  # Add common names (for both sciname and sciname_hs_modified)
-    left_join(sciname_metadata %>% 
-              select(sciname, common_name), 
-            by = "sciname") %>%
-  left_join(sciname_metadata %>% 
-              select(sciname, "common_name_hs_modified" = "common_name"), 
-            by = c("sciname_hs_modified" = "sciname"))
-
+consumption <- read.csv(file.path(datadir, "case_study_consumption.csv"))
 ```
 
-```{r}
-# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
-# Fill version
-consumption_of_rus_p <- consumption %>%
-  filter(consumer_iso3c != "RUS", 
-         source_country_iso3c == "RUS") %>%
-  mutate(path = case_when(
-    exporter_iso3c == "RUS" ~ "Direct import", 
-    TRUE ~ "Import from intermediate partner"
-  )) %>% 
-  group_by(year, path, sanctions_towards_russia) %>%
-  summarise(consumption_live_t = sum(consumption_live_t)) %>%
+```{r fig1_consumption_from_russia}
+consumption_russian_ts <- read.csv(file.path(datadir, "fig1_consumption_from_russia.csv"))
+
+consumption_russian_ts_fill <- consumption_russian_ts %>%
   ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
@@
 
-consumption_of_rus_p
-
-# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
-# Line version
-consumption %>%
-  filter(consumer_iso3c != "RUS", 
-         source_country_iso3c == "RUS") %>%
-  mutate(path = case_when(
-    exporter_iso3c == "RUS" ~ "Direct import", 
-    TRUE ~ "Import from intermediate partner"
-  )) %>% 
-  group_by(year, path, sanctions_towards_russia) %>%
-  summarise(consumption_live_t = sum(consumption_live_t)) %>%
-  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
-  geom_line() +
-  geom_vline(aes(xintercept = 2014), linetype = 2) +
-  scale_color_manual(values = c("#D4B95f", # khaki
-                               "#4FA2A2" # teal
-  )) + 
-  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", color = "") +
-  facet_wrap(~sanctions_towards_russia) +
-  theme_minimal() +
-  theme(
-    legend.position = "bottom",
-    panel.spacing = unit(5, "mm")
-  )
-
-# Change in consumption stats
-# Change in total consumption of Russian products - imposed sanctions
-consumption_change <- consumption %>%
-  filter(sanctions_towards_russia == "Imposed sanctions", 
-         source_country_iso3c == "RUS") %>%
-  group_by(year) %>%
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
-
-q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-
-100*(q_post - q_pre)/q_pre
-
-# Change in consumption of Russian products via direct import - imposed sanctions
-consumption_change <- consumption %>%
-  filter(sanctions_towards_russia == "Imposed sanctions", 
-         exporter_iso3c == "RUS",
-         source_country_iso3c == "RUS") %>%
-  group_by(year) %>%
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
-
-q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-
-100*(q_post - q_pre)/q_pre
-
-# Change in consumption of Russian products via indirect import - imposed sanctions
-consumption_change <- consumption %>%
-  filter(sanctions_towards_russia == "Imposed sanctions", 
-         exporter_iso3c != "RUS",
-         source_country_iso3c == "RUS") %>%
-  group_by(year) %>%
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
-
-q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-
-paste("Change in consumption of Russian products via indirect import - imposed sanctions")
-100*(q_post - q_pre)/q_pre
-
-# Change in total consumption of Russian products  - didn't impose sanctions
-consumption_change <- consumption %>%
-  filter(sanctions_towards_russia == "Did not impose sanctions", 
-         source_country_iso3c == "RUS") %>%
-  group_by(year) %>%
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
-
-q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-
-paste("Change in total consumption of Russian products  - didn't impose sanctions")
-100*(q_post - q_pre)/q_pre
-
+consumption_russian_ts_fill
 ```
 
-```{r}
-# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
-# Fill version
-rus_foreign_consumption_p <- consumption %>%
-  filter(consumer_iso3c == "RUS", 
-         source_country_iso3c != "RUS") %>%
-  mutate(path = case_when(
-    source_country_iso3c == exporter_iso3c ~ "Direct import", 
-    TRUE ~ "Import from intermediate partner"
-  )) %>% 
-  group_by(year, path, source_sanctions_towards_russia) %>%
-  summarise(consumption_live_t = sum(consumption_live_t)) %>%
+```{r fig1_consumption_by_russia}
+consumption_by_russia_ts <- read.csv(file.path(datadir, "fig1_consumption_by_russia.csv"))
+
+consumption_by_russia_ts_fill <- consumption_by_russia_ts %>%
   ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
@@
 
-rus_foreign_consumption_p
-
-# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
-# Line version
-consumption %>%
-  filter(consumer_iso3c == "RUS", 
-         source_country_iso3c != "RUS") %>%
-  mutate(path = case_when(
-    source_country_iso3c == exporter_iso3c ~ "Direct import", 
-    TRUE ~ "Import from intermediate partner"
-  )) %>% 
-  group_by(year, path, source_sanctions_towards_russia) %>%
-  summarise(consumption_live_t = sum(consumption_live_t)) %>%
-  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
-  geom_line() +
-  geom_vline(aes(xintercept = 2014), linetype = 2) +
-  scale_color_manual(values = c("#D4B95f", # khaki
-                               "#4FA2A2" # teal
-  )) + 
-  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", color = "") +
-  facet_wrap(~source_sanctions_towards_russia) +
-  theme_minimal() +
-  theme(
-    legend.position = "bottom",
-    panel.spacing = unit(5, "mm")
-  )
-
-# Change in Russia's consumption from countries imposing sanctions
-consumption_change <- consumption %>%
-  filter(source_sanctions_towards_russia == "Imposed sanctions", 
-         consumer_iso3c == "RUS") %>%
-  group_by(year) %>%
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
-
-q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-
-paste("Change in Russia's consumption from countries imposing sanctions")
-100*(q_post - q_pre)/q_pre
-
-# Change in Russia's consumption from countries imposing sanctions - direct imports
-consumption_change <- consumption %>%
-  filter(source_sanctions_towards_russia == "Imposed sanctions", 
-         source_country_iso3c == exporter_iso3c,
-         consumer_iso3c == "RUS") %>%
-  group_by(year) %>%
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
-
-q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
-
-paste("Change in Russia's consumption from countries imposing sanctions - direct imports")
-100*(q_post - q_pre)/q_pre
-
+consumption_by_russia_ts_fill
 ```
 
-```{r fig.height = 6, width = 8}
-# Format figure 1 together
-ggarrange(
-  consumption_of_rus_p,
-  rus_foreign_consumption_p,
-  nrow = 2,
-  common.legend = TRUE
-)
+```{r fig1, fig.height=6}
+# Join plots
+ggarrange(consumption_russian_ts_fill, consumption_by_russia_ts_fill, 
+          common.legend = TRUE, ncol = 1, legend = "bottom")
 
-ggsave("fig1.png", device = "png", height = 5, width = 6.5, units = "in")
+ggsave(file.path(figdir, "fig1.png"), device = "png", width = 6.5, height = 5, unit = "in")
 ```
 
-```{r}
+```{r fig2_rus_us_sankey}
 # Sankey diagram of flows of Russian products into the US
@@
 
-ggexport(rus_us_sankey, filename = "rus_us_sankey.png", width = 800, height = 400)
+rus_us_sankey
 
-# Top species US consumes sourced from Russia
-species_rank <- consumption %>%
-  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
-  mutate(path = case_when(
-    exporter_iso3c == "RUS" ~ "Direct import", 
-    TRUE ~ "Import from\nintermediate partner"
-  )) %>% 
-  rename("importer_iso3c" = "consumer_iso3c",
-         "live_weight_t" = "consumption_live_t") %>%
-  mutate(common_name_hs_modified = case_when(
-    common_name_hs_modified == "alaska pollock(=walleye poll.)" ~ "Alaska Pollock",
-    common_name_hs_modified == "atlantic cod" ~ "Atlantic Cod",
-    common_name_hs_modified == "pink(=humpback) salmon" ~ "Pink Salmon",
-    common_name_hs_modified == "haddock" ~ "Haddock",
-    common_name_hs_modified == "pacific cod" ~ "Pacific Cod",
-    TRUE ~ common_name_hs_modified
-  )) %>%
-  mutate(common_name_hs_modified = gsub(" ", "\n", common_name_hs_modified)) %>%
-  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
-  theme(
-    legend.position = "bottom",
-    axis.text.y = element_text(angle = 90),
-
-  ) +
-  labs(y = "", x = "Consumption (live weight tonnes)", fill = "")
-
-ggexport(species_rank, filename = "US_species_rank.png")
-
-# Stats for paper
-# Percent by exporter
-consumption %>%
-  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
-  group_by(exporter_iso3c) %>% 
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
-  arrange(desc(percent))
-
-# Percent by species
-consumption %>%
-  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
-  group_by(common_name_hs_modified) %>% 
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
-  arrange(desc(percent))
-
-# FIXIT:Pull out stats from these data frames to print the one for the paper
-
+ggexport(rus_us_sankey, filename = file.path(figdir, "rus_us_sankey.png"), width = 800, height = 400)
 ```
@@
 ```{r}
-rus_to_chn <- artis %>%
-  # Isolating Chinese imports that were originally caught in Russia
-  filter(source_country_iso3c == "RUS", importer_iso3c == "CHN") %>%
-  group_by(year, sciname) %>%
-  summarise(russia_live_t = sum(live_weight_t, na.rm = TRUE))
-
-notrus_to_chn <- artis %>%
-  # Isolating Chinese imports that were NOT originally caught in Russia
-  filter(source_country_iso3c != "RUS", importer_iso3c == "CHN") %>%
-  group_by(year, sciname) %>%
-  summarise(notrussia_live_t = sum(live_weight_t, na.rm = TRUE))
-
-chn_to_usa <- artis %>%
-  filter(exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
-  group_by(year, sciname) %>%
-  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
-  left_join(rus_to_chn, by = c("year", "sciname")) %>%
-  left_join(notrus_to_chn, by = c("year", "sciname")) %>%
-  replace_na(list(russia_live_t = 0, notrussia_live_t = 0)) %>% 
-  # Calculate the minimum by year and species that had to come from Russia
-  mutate(min_russia = case_when(
-    # If non-Russian product exceeds the volume sent to the US, 
-    # then min that had to be Russian is 0
-    (notrussia_live_t >= live_weight_t) ~ 0,
-    # If non-Russian product cannot explain all, then fill up remaining with Russian product
-    (live_weight_t - notrussia_live_t) >= russia_live_t ~ russia_live_t,
-    # Otherwise fill up remaining with Russian product
-    TRUE ~ (live_weight_t - notrussia_live_t)
-  )) %>% 
-  # Calculate the max that could have come from Russia
-  mutate(max_russia = case_when(
-    # If Russian product can explain full amount, max is total trade flow
-    russia_live_t >= live_weight_t ~ live_weight_t, 
-    # If Russian product cannont explain all, fill up with Russian product to get max
-    russia_live_t < live_weight_t ~ russia_live_t
-  ))
-
-# Stats
-chn_to_usa %>% 
-  filter(year == 2020, 
-         sciname %in% c("gadus chalcogrammus", "gadus morhua", "oncorhynchus gorbuscha", "gadus macrocephalus"))
-
-consumption %>%
-  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
-  group_by(sciname_hs_modified) %>% 
-  summarise(consumption_live_t = sum(consumption_live_t)) %>% 
-  arrange(desc(consumption_live_t)) %>%
-  ungroup() %>%
-  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
-  mutate(cum_percent = cumsum(percent))
-
-```
-
-```{r}
-rus_chn_usa <- artis %>%
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
-  group_by(year, sciname) %>%
-  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
-  ungroup() %>%
-  left_join(chn_to_usa %>%
-            select(year, sciname, min_russia, max_russia)) %>%
-  mutate(live_weight_t = live_weight_t / 1e3,
-         min_russia = min_russia / 1e3,
-         max_russia = max_russia / 1e3)
+rus_chn_usa <- read.csv(file.path(datadir, "rus_chn_usa.csv"))
 
@@
     axis.title.y = element_blank(),
+    axis.text.x = element_text(size = 7),
     plot.margin = margin(t = -1, r = 2, l = 2, b = -2, unit = "mm")
   )
+```
 
-p_joined <- ggarrange(p1, p2, p3, p4, p5, ncol = 1)
-
-ggexport(p_joined, filename = "US_species_import_range.png")
-
-# Top species US consumes sourced from Russia
-
-species_rank_df <- consumption %>%
-  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
-  mutate(path = case_when(
-    exporter_iso3c == "RUS" ~ "Direct\nimport", 
-    TRUE ~ "Import from\nintermediate partner"
-  )) %>% 
-  rename("importer_iso3c" = "consumer_iso3c",
-         "live_weight_t" = "consumption_live_t") %>%
-  mutate(common_name_hs_modified = case_when(
-    common_name_hs_modified == "alaska pollock(=walleye poll.)" ~ "Alaska Pollock",
-    common_name_hs_modified == "atlantic cod" ~ "Atlantic Cod",
-    common_name_hs_modified == "pink(=humpback) salmon" ~ "Pink Salmon",
-    common_name_hs_modified == "haddock" ~ "Haddock",
-    common_name_hs_modified == "pacific cod" ~ "Pacific Cod",
-    TRUE ~ common_name_hs_modified
-  )) %>%
-  mutate(common_name_hs_modified = gsub(" ", "\n", common_name_hs_modified)) %>%
-  mutate(live_weight_t = live_weight_t / length(2015:2019)) %>%
-  mutate(live_weight_t = live_weight_t / 1e3)
+```{r fig2_species_bars}
+species_rank_df <- read.csv(file.path(datadir, "species_ranking.csv"))
 
@@
     axis.text.y = element_text(angle = 90, hjust = 0.5),
-    axis.title.x = element_text(size = 7),
-    legend.key.size = unit(1, units = "line"),
+    axis.text.x = element_text(size = 7),
+    axis.title.x = element_text(size = 7, hjust = 1),
+    legend.key.height = unit(3, "mm"),
+    legend.key.width = unit(3, "mm"),
     plot.margin = margin(t = -2, b = -1, unit = "mm")
   ) +
-  labs(y = "", x = "Avg. Consumption (1000 t) (2015-2019)", fill = "")
+  labs(y = "", x = "Avg. Consumption (1000 t) 2015-2019", fill = "")
 
+species_legend <- get_legend(species_rank_5)
+```
+
+```{r fig2}
 # Format Figure 2 together
@@
   heights = c(1, 1, 1, 1, 1),
-  common.legend = TRUE,
+  legend.grob = species_legend,
+  # common.legend = TRUE,
   legend = "bottom"
@@
 
-ggsave("fig2.png", device = "png", width = 6.5, height = 6)
+ggsave(file.path(figdir, "fig2.png"), device = "png", width = 6.6, height = 6)
 ```
-
-```{r}
-# Explore spike in China's apparent consumption of Russian products
-tmp <- consumption %>% 
-  filter(source_country_iso3c == "RUS", consumer_iso3c != "RUS") %>%
-  group_by(year, consumer_iso3c) %>% 
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
-
-consumption %>% 
-  filter(source_country_iso3c == "RUS", consumer_iso3c == "CHN") %>%
-  group_by(year) %>% 
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
-  ggplot(aes(x = year, y = consumption_live_t)) +
-  geom_line() + 
-  theme_bw()
-
-tmp <- consumption %>% 
-  filter(source_country_iso3c == "RUS", consumer_iso3c == "CHN") %>%
-  group_by(year, sciname_hs_modified) %>% 
-  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))
-
-prod %>% 
-  filter(iso3c == "RUS", sciname == "gadus chalcogrammus") %>%
-  group_by(year) %>%
-  summarise(live_weight_t = sum(live_weight_t)) %>%
-  ggplot(aes(x = year, y = live_weight_t)) +
-  geom_line() +
-  theme_bw()
-
-artis %>% 
-  filter(exporter_iso3c == "RUS", importer_iso3c == "CHN") %>%
-  plot_ts(artis_var = "hs6", plot.type = "filled", prop_flow_cutoff = 0.07)
-
-artis %>% 
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN") %>%
-  group_by(year) %>%
-  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
-  ggplot(aes(year, live_weight_t)) +
-  geom_line() +
-  theme_bw()
-
-artis %>% 
-  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN") %>%
-  plot_ts(artis_var = "importer_iso3c", plot.type = "filled")
-
-artis %>% 
-  filter(hs6 %in% c(30379, 30380, 303429, 30499, 30510, 30520, 
-                    30530, 30549, 30569, 51191, 1400410, 140420,
-                    160419, 160430), exporter_iso3c == "CHN") %>%
-  plot_ts(artis_var = "hs6", plot.type = "filled")
-
-```

### 2024-04-17 prep_data.R

@@ -1,0 +1,225 @@
+
+# libraries
+library(tidyverse)
+library(countrycode)
+library(exploreARTIS)
+library(DBI)
+library(janitor)
+library(broom)
+library(dbscan)
+library(GGally)
+library(ggrepel)
+library(ggpubr)
+
+# Setup-------------------------------------------------------------------------
+outdir <- "data"
+
+# Initial database pulls--------------------------------------------------------
+# Database connection
+con <- dbConnect(RPostgres::Postgres(),
+                 dbname=Sys.getenv("DB_NAME"),
+                 host="localhost",
+                 port="5432",
+                 user=Sys.getenv("DB_USERNAME"),
+                 password=Sys.getenv("DB_PASSWORD"))
+
+# Check that connection is established by checking which tables are present
+dbListTables(con)
+
+# ARTIS dataframe
+custom_artis_query <- "SELECT * FROM snet WHERE 
+((hs_version = 'HS96' AND year >= 1996 AND year <= 2003) OR
+(hs_version = 'HS02' AND year >= 2004 AND year <= 2012) OR
+(hs_version = 'HS12' AND year >= 2013 AND year <= 2020))"
+
+artis <- dbGetQuery(con, custom_artis_query) %>%
+  select(-record_id)
+
+custom_consumption_query <- "SELECT * FROM complete_consumption WHERE 
+((hs_version = 'HS96' AND year >= 1996 AND year <= 2003) OR
+(hs_version = 'HS02' AND year >= 2004 AND year <= 2012) OR
+(hs_version = 'HS12' AND year >= 2013 AND year <= 2020))"
+
+# consumption dataframe
+consumption <- dbGetQuery(con, custom_consumption_query) %>%
+  select(-record_id) 
+
+# Production dataframe
+prod <- dbGetQuery(con, "SELECT * FROM production") %>%
+  select(-record_id) 
+
+# Product metadata dataframe
+product <- dbGetQuery(con, "SELECT * FROM products") %>%
+  select(-record_id) 
+
+# Species metadata
+sciname_metadata <- dbGetQuery(con, "SELECT * FROM sciname") %>%
+  select(-record_id)
+
+# Improved taxa resolution metadata
[…]

### 2024-04-18 Archive/ms-russia-figures_OLD.Rmd
manuscript results now autopopulate in an Rmarkdown

---
title: "Russian sanctions figures"
output: html_document
date: "2024-02-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To do: 
-

```{r}
library(tidyverse)
library(countrycode)
library(exploreARTIS)
library(DBI)
library(janitor)
library(broom)
library(dbscan)
library(GGally)
library(ggrepel)
library(ggpubr)
```

```{r}
habitat_source_colors <- c("#1B708F", # blue = marine capture
                          "#86ADA7", # light blue = freshwater capture
                          "#F37542", # medium orange = marine aquaculture
                          "#F7AF75", # light orange = inland aquaculture
                          "grey50" # unknown
                          )

region_colors <- c(
  "#741A32", # maroon
  "#B34232", # burnt orange
  "#D38F35", #  orange
  "#D4B95f", # khaki
  "#4FA2A2", # teal
  "#114F59" # dark teal
)
```

```{r}
# Initial database pulls

# Database connection
con <- dbConnect(RPostgres::Postgres(),
                 dbname=Sys.getenv("DB_NAME"),
                 host="localhost",
                 port="5432",
                 user=Sys.getenv("DB_USERNAME"),
                 password=Sys.getenv("DB_PASSWORD"))

# Check that connection is established by checking which tables are present
dbListTables(con)

# ARTIS dataframe
custom_artis_query <- "SELECT * FROM snet WHERE 
((hs_version = 'HS96' AND year >= 1996 AND year <= 2003) OR
(hs_version = 'HS02' AND year >= 2004 AND year <= 2012) OR
(hs_version = 'HS12' AND year >= 2013 AND year <= 2020))"

artis <- dbGetQuery(con, custom_artis_query) %>%
  select(-record_id)

custom_consumption_query <- "SELECT * FROM complete_consumption WHERE 
((hs_version = 'HS96' AND year >= 1996 AND year <= 2003) OR
(hs_version = 'HS02' AND year >= 2004 AND year <= 2012) OR
(hs_version = 'HS12' AND year >= 2013 AND year <= 2020))"

# consumption dataframe
consumption <- dbGetQuery(con, custom_consumption_query) %>%
  select(-record_id)

# Production dataframe
prod <- dbGetQuery(con, "SELECT * FROM production") %>%
  select(-record_id)

# Product metadata dataframe
product <- dbGetQuery(con, "SELECT * FROM products") %>%
  select(-record_id)

# Species metadata
sciname_metadata <- dbGetQuery(con, "SELECT * FROM sciname") %>%
  select(-record_id)

# Improved taxa resolution metadata
sciname_hs_modified <- dbGetQuery(con, "SELECT * FROM code_max_resolved_taxa") %>%
  select(-record_id)

# Close database connection
dbDisconnect(con)
rm(list = c("con"))

artis <- artis %>%
  # Add variables for whether source/importer/exporter imposed sanctions following annexation of Crimea
    mutate(sanctions_towards_russia = case_when(
      importer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No"
    )) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No")) %>% 
  left_join(sciname_metadata %>% 
              select(sciname, common_name), 
            by = "sciname") %>% 
  mutate(source_sanctions_towards_russia = case_when(
      source_country_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No")) %>% 
  # Join on common names
  left_join(sciname_metadata %>% 
              select(sciname, common_name), 
            by = "sciname")

consumption <- consumption %>%
  # Filter consumption to when Russia is involved
  filter(source_country_iso3c == "RUS"|exporter_iso3c == "RUS"|consumer_iso3c == "RUS") %>%
  # Add variables for whether source/importer/exporter imposed sanctions following annexation of Crimea
    mutate(sanctions_towards_russia = case_when(
      consumer_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", 
                            "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Russia unfriendly countries",
      TRUE ~ "Russia friendly countries"
    )) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      exporter_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Russia unfriendly countries",
      TRUE ~ "Russia friendly countries")) %>%
    mutate(source_sanctions_towards_russia = case_when(
      source_country_iso3c %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Russia unfriendly countries",
      TRUE ~ "Russia friendly countries")) %>% 
  # Add common names (for both sciname and sciname_hs_modified)
    left_join(sciname_metadata %>% 
              select(sciname, common_name), 
            by = "sciname") %>%
  left_join(sciname_metadata %>% 
              select(sciname, "common_name_hs_modified" = "common_name"), 
            by = c("sciname_hs_modified" = "sciname"))

```

```{r}
# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Fill version

consumption_russian_ts <- consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>%
  mutate(sanctions_towards_russia = case_when(
    sanctions_towards_russia == "Russia friendly countries" ~ "Friendly countries' consumption\nof seafood from Russia",
    TRUE ~ "Unfriendly countries' consumption\nof seafood from Russia"
  )) %>% 
  group_by(year, path, sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ungroup()

consumption_russian_ts_fill <- consumption_russian_ts %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption (mil t, live weight)", fill = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 9),
    legend.position = "top",
    panel.spacing = unit(5, "mm")
  )

consumption_russian_ts_fill

# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Line version
consumption_russian_ts_line <- consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
  geom_line() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_color_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", color = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.spacing = unit(5, "mm")
  )

consumption_russian_ts_line

# Change in consumption stats
# Change in total consumption of Russian products - imposed sanctions
consumption_change <- consumption %>%
  filter(sanctions_towards_russia == "Russia unfriendly countries", 
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

100*(q_post - q_pre)/q_pre

# Change in consumption of Russian products via direct import - imposed sanctions
consumption_change <- consumption %>%
  filter(sanctions_towards_russia == "Russia unfriendly countries", 
         exporter_iso3c == "RUS",
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

100*(q_post - q_pre)/q_pre

# Change in consumption of Russian products via indirect import - imposed sanctions
consumption_change <- consumption %>%
  filter(sanctions_towards_russia == "Russia unfriendly countries", 
         exporter_iso3c != "RUS",
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

paste("Change in consumption of Russian products via indirect import - imposed sanctions")
100*(q_post - q_pre)/q_pre

# Change in total consumption of Russian products  - didn't impose sanctions
consumption_change <- consumption %>%
  filter(sanctions_towards_russia == "Russia friendly countries", 
         source_country_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

paste("Change in total consumption of Russian products  - didn't impose sanctions")
100*(q_post - q_pre)/q_pre

```

```{r}
# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)

# Fill version
consumption_by_russia_ts <- consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  mutate(path = case_when(
    source_country_iso3c == exporter_iso3c ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  mutate(source_sanctions_towards_russia = case_when(
    source_sanctions_towards_russia == "Russia friendly countries" ~ "Russian consumption of seafood\nfrom friendly countries",
    TRUE ~ "Russian consumption of seafood\nfrom unfriendly countries"
  )) %>%
  group_by(year, path, source_sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ungroup()

consumption_by_russia_ts_fill <- consumption_by_russia_ts %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption (mil t, live weight)", fill = "") +
  facet_wrap(~source_sanctions_towards_russia) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 9),
    legend.position = "top",
    panel.spacing = unit(5, "mm")
  )

consumption_by_russia_ts_fill

# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Line version
consumption_by_russia_ts_line <- consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  mutate(path = case_when(
    source_country_iso3c == exporter_iso3c ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, source_sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
  geom_line() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_color_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", color = "") +
  facet_wrap(~source_sanctions_towards_russia) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.spacing = unit(5, "mm")
  )

consumption_by_russia_ts_line

# Change in Russia's consumption from countries imposing sanctions
consumption_change <- consumption %>%
  filter(source_sanctions_towards_russia == "Russia unfriendly countries", # FIXIT
         consumer_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

paste("Change in Russia's consumption from countries imposing sanctions")
100*(q_post - q_pre)/q_pre

# Change in Russia's consumption from countries imposing sanctions - direct imports
consumption_change <- consumption %>%
  filter(source_sanctions_towards_russia == "Russia unfriendly countries", 
         source_country_iso3c == exporter_iso3c,
         consumer_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

q_pre <- consumption_change %>% filter(year %in% 2013:2014) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)
q_post <- consumption_change %>% filter(year %in% 2015:2016) %>% summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% pull(consumption_live_t)

paste("Change in Russia's consumption from countries imposing sanctions - direct imports")
100*(q_post - q_pre)/q_pre

```
```{r, fig.height=6}
# Join plots
ggarrange(consumption_russian_ts_fill, consumption_by_russia_ts_fill, 
          common.legend = TRUE, ncol = 1, legend = "bottom")

ggsave("fig1.png", device = "png", width = 6.5, height = 5, unit = "in")

ggarrange(consumption_russian_ts_line, consumption_by_russia_ts_line, 
          common.legend = TRUE, ncol = 1)
```

```{r}
# Sankey diagram of flows of Russian products into the US
rus_us_sankey <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  rename("importer_iso3c" = "consumer_iso3c",
         "live_weight_t" = "consumption_live_t") %>%
  plot_sankey(prop_flow_cutoff = 0.01)

ggexport(rus_us_sankey, filename = "rus_us_sankey.png", width = 800, height = 400)

# Top species US consumes sourced from Russia
species_rank <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from\nintermediate partner"
  )) %>% 
  rename("importer_iso3c" = "consumer_iso3c",
         "live_weight_t" = "consumption_live_t") %>%
  mutate(common_name_hs_modified = case_when(
    common_name_hs_modified == "alaska pollock(=walleye poll.)" ~ "Alaska Pollock",
    common_name_hs_modified == "atlantic cod" ~ "Atlantic Cod",
    common_name_hs_modified == "pink(=humpback) salmon" ~ "Pink Salmon",
    common_name_hs_modified == "haddock" ~ "Haddock",
    common_name_hs_modified == "pacific cod" ~ "Pacific Cod",
    TRUE ~ common_name_hs_modified
  )) %>%
  mutate(common_name_hs_modified = gsub(" ", "\n", common_name_hs_modified)) %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(angle = 90),

  ) +
  labs(y = "", x = "Consumption (live weight tonnes)", fill = "")

ggexport(species_rank, filename = "US_species_rank.png")

# Stats for paper
# Percent by exporter
consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
  group_by(exporter_iso3c) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
  arrange(desc(percent))

# Percent by species
consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
  group_by(common_name_hs_modified) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
  arrange(desc(percent))

# FIXIT:Pull out stats from these data frames to print the one for the paper

```

```{r}
rus_to_chn <- artis %>%
  # Isolating Chinese imports that were originally caught in Russia
  filter(source_country_iso3c == "RUS", importer_iso3c == "CHN") %>%
  group_by(year, sciname) %>%
  summarise(russia_live_t = sum(live_weight_t, na.rm = TRUE))

notrus_to_chn <- artis %>%
  # Isolating Chinese imports that were NOT originally caught in Russia
  filter(source_country_iso3c != "RUS", importer_iso3c == "CHN") %>%
  group_by(year, sciname) %>%
  summarise(notrussia_live_t = sum(live_weight_t, na.rm = TRUE))

chn_to_usa <- artis %>%
  filter(exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
  left_join(rus_to_chn, by = c("year", "sciname")) %>%
  left_join(notrus_to_chn, by = c("year", "sciname")) %>%
  replace_na(list(russia_live_t = 0, notrussia_live_t = 0)) %>% 
  # Calculate the minimum by year and species that had to come from Russia
  mutate(min_russia = case_when(
    # If non-Russian product exceeds the volume sent to the US, 
    # then min that had to be Russian is 0
    (notrussia_live_t >= live_weight_t) ~ 0,
    # If non-Russian product cannot explain all, then fill up remaining with Russian product
    (live_weight_t - notrussia_live_t) >= russia_live_t ~ russia_live_t,
    # Otherwise fill up remaining with Russian product
    TRUE ~ (live_weight_t - notrussia_live_t)
  )) %>% 
  # Calculate the max that could have come from Russia
  mutate(max_russia = case_when(
    # If Russian product can explain full amount, max is total trade flow
    russia_live_t >= live_weight_t ~ live_weight_t, 
    # If Russian product cannont explain all, fill up with Russian product to get max
    russia_live_t < live_weight_t ~ russia_live_t
  ))

# Stats
chn_to_usa %>% 
  filter(year == 2020, 
         sciname %in% c("gadus chalcogrammus", "gadus morhua", "oncorhynchus gorbuscha", "gadus macrocephalus"))

consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  group_by(sciname_hs_modified) %>% 
  summarise(consumption_live_t = sum(consumption_live_t)) %>% 
  arrange(desc(consumption_live_t)) %>%
  ungroup() %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
  mutate(cum_percent = cumsum(percent))

```

```{r}
rus_chn_usa <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
  ungroup() %>%
  left_join(chn_to_usa %>%
            select(year, sciname, min_russia, max_russia)) %>%
  mutate(live_weight_t = live_weight_t / 1e3,
         min_russia = min_russia / 1e3,
         max_russia = max_russia / 1e3)

p1 <- rus_chn_usa %>% 
  filter(sciname == "gadus chalcogrammus",
         year > 1996) %>%
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  xlim(1997, 2020) +
  scale_y_continuous(position = "right") +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Alaska pollock via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = margin(l = 2, b = -2, unit = "mm")
  )

p2 <- rus_chn_usa %>%
  filter(year > 1996,
         sciname == "gadus morhua") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  scale_y_continuous(position = "right") +
  xlim(1997, 2020) +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Atlantic cod via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = margin(r = 2, l = 2, b = -2, unit = "mm")
  )

p3 <- rus_chn_usa %>%
  filter(sciname == "oncorhynchus gorbuscha",
         year > 1996) %>%
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  scale_y_continuous(position = "right") +
  xlim(1997, 2020) +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian pink salmon via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = margin(r = 2, l = 2, b = -2, unit = "mm")
  )

p4 <- rus_chn_usa %>%
  filter(sciname == "melanogrammus aeglefinus",
         year > 1996) %>%
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  scale_y_continuous(position = "right") +
  xlim(1997, 2020) +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian haddock via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = margin(l = 2, b = -2, r = 1.5, unit = "mm")
  )

p5 <- rus_chn_usa %>%
  filter(sciname == "gadus macrocephalus",
         year > 1996) %>%
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  scale_y_continuous(position = "right") +
  xlim(1997, 2020) +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Pacific cod via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 7),
    plot.margin = margin(t = -1, r = 2, l = 2, b = -2, unit = "mm")
  )

p_joined <- ggarrange(p1, p2, p3, p4, p5, ncol = 1)

ggexport(p_joined, filename = "US_species_import_range.png")

# Top species US consumes sourced from Russia
species_rank_df <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct\nimport", 
    TRUE ~ "Import from\nintermediate partner"
  )) %>% 
  rename("importer_iso3c" = "consumer_iso3c",
         "live_weight_t" = "consumption_live_t") %>%
  mutate(common_name_hs_modified = case_when(
    common_name_hs_modified == "alaska pollock(=walleye poll.)" ~ "Alaska Pollock",
    common_name_hs_modified == "atlantic cod" ~ "Atlantic Cod",
    common_name_hs_modified == "pink(=humpback) salmon" ~ "Pink Salmon",
    common_name_hs_modified == "haddock" ~ "Haddock",
    common_name_hs_modified == "pacific cod" ~ "Pacific Cod",
    TRUE ~ common_name_hs_modified
  )) %>%
  mutate(common_name_hs_modified = gsub(" ", "\n", common_name_hs_modified)) %>%
  mutate(live_weight_t = live_weight_t / length(2015:2019)) %>%
  mutate(live_weight_t = live_weight_t / 1e3)

species_rank_1 <- species_rank_df %>%
  filter(common_name_hs_modified == "Alaska\nPollock") %>%
  mutate(dom_source == "") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) +
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_2 <- species_rank_df %>%
  filter(common_name_hs_modified == "Atlantic\nCod") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_3 <- species_rank_df %>%
  filter(common_name_hs_modified == "Pink\nSalmon") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_4 <- species_rank_df %>%
  filter(common_name_hs_modified == "Haddock") %>%
  mutate(common_name_hs_modified = paste("\n", common_name_hs_modified, sep = "")) %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_5 <- species_rank_df %>%
  filter(common_name_hs_modified == "Pacific\nCod") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    axis.text.x = element_text(size = 7),
    axis.title.x = element_text(size = 7, hjust = 1),
    legend.key.height = unit(3, "mm"),
    legend.key.width = unit(3, "mm"),
    plot.margin = margin(t = -2, b = -1, unit = "mm")
  ) +
  labs(y = "", x = "Avg. Consumption (1000 t) 2015-2019", fill = "")

species_legend <- get_legend(species_rank_5)

# Format Figure 2 together
fig2 <- ggarrange(
  species_rank_1, p1,
  species_rank_2, p2,
  species_rank_3, p3,
  species_rank_4, p4,
  species_rank_5, p5,
  ncol = 2, nrow = 5,
  widths = c(1, 2),
  heights = c(1, 1, 1, 1, 1),
  legend.grob = species_legend,
  # common.legend = TRUE,
  legend = "bottom"
  )

fig2

fig2 <- annotate_figure(
  fig2,
  right = text_grob("US Imports of Russian Species (1000 t, live weight)", rot = 270)
  )

fig2 <- ggarrange(
  rus_us_sankey,
  fig2,
  nrow = 2,
  heights = c(1, 2)
)

fig2

ggsave("fig2.png", device = "png", width = 6.5, height = 6)
```

```{r}
# Explore spike in China's apparent consumption of Russian products
tmp <- consumption %>% 
  filter(source_country_iso3c == "RUS", consumer_iso3c != "RUS") %>%
  group_by(year, consumer_iso3c) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

consumption %>% 
  filter(source_country_iso3c == "RUS", consumer_iso3c == "CHN") %>%
  group_by(year) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = consumption_live_t)) +
  geom_line() + 
  theme_bw()

tmp <- consumption %>% 
  filter(source_country_iso3c == "RUS", consumer_iso3c == "CHN") %>%
  group_by(year, sciname_hs_modified) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

prod %>% 
  filter(iso3c == "RUS", sciname == "gadus chalcogrammus") %>%
  group_by(year) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ggplot(aes(x = year, y = live_weight_t)) +
  geom_line() +
  theme_bw()

artis %>% 
  filter(exporter_iso3c == "RUS", importer_iso3c == "CHN") %>%
  plot_ts(artis_var = "hs6", plot.type = "filled", prop_flow_cutoff = 0.07)

artis %>% 
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN") %>%
  group_by(year) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
  ggplot(aes(year, live_weight_t)) +
  geom_line() +
  theme_bw()

artis %>% 
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN") %>%
  plot_ts(artis_var = "importer_iso3c", plot.type = "filled")

artis %>% 
  filter(hs6 %in% c(30379, 30380, 303429, 30499, 30510, 30520, 
                    30530, 30549, 30569, 51191, 1400410, 140420,
                    160419, 160430), exporter_iso3c == "CHN") %>%
  plot_ts(artis_var = "hs6", plot.type = "filled")

```

### 2024-04-18 prep_data.R
creates directories if they dont exist

@@ -13,6 +13,11 @@ library(ggpubr)
 
 # Setup-------------------------------------------------------------------------
 outdir <- "data"
+figdir <- "figures"
+
+# Create directories if they do not exist
+if (dir.exists(outdir)) { dir.create(outdir) }
+if (dir.exists(figdir)) { dir.create(figdir) }
 
 # Initial database pulls--------------------------------------------------------
 # Database connection

### 2024-04-19 ms-russia-figures.Rmd
Add stats for MS text

--- 2024-03-14 ms-russia-figures.Rmd
@@
 
+# Percent of US consumption moving through intermediate country
+consumption %>%
+  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
+  mutate(path = case_when(
+    exporter_iso3c == "RUS" ~ "direct", 
+    TRUE ~ "indirect"
+  )) %>%
+  group_by(path) %>% 
+  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(percent = 100*consumption_live_t/sum(consumption_live_t))
+
 # Percent by species

### 2024-04-19 ms-russia-figures.Rmd

--- 2024-04-17 ms-russia-figures.Rmd
@@
 
-ggsave(file.path(figdir, "fig1.png"), device = "png", width = 6.5, height = 5, unit = "in")
+ggsave(file.path(figdir, "fig1.png"), device = "png", width = 6.5, height = 5, unit = "in", dpi = 500)
 ```
@@
 rus_chn_usa <- read.csv(file.path(datadir, "rus_chn_usa.csv"))
+chn_to_usa <- read.csv(file.path(datadir, "chn_to_usa.csv"))
 
@@
 
-ggsave(file.path(figdir, "fig2.png"), device = "png", width = 6.6, height = 6)
+ggsave(file.path(figdir, "fig2.png"), device = "png", width = 6.6, height = 6, dpi = 500)
 ```

### 2024-04-19 ms-russia-results.Rmd

---
title: "ms_russia_results"
author: ""
date: "2024-04-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

library(tidyverse)
library(reactable)
library(reactablefmtr)

datadir <- "data"
```

```{r load_data}
consumption <- read.csv(file.path(datadir, "case_study_consumption.csv"))
consumption_by_rus <- read.csv(file.path(datadir, "fig1_consumption_by_russia.csv"))
rus_chn_usa <- read.csv(file.path(datadir, "rus_chn_usa.csv"))
```

```{r rus_imports_change}
# Calculating Russia's consumption from countries imposing sanctions across years
consumption_change <- consumption %>%
  filter(source_sanctions_towards_russia == "Russia unfriendly countries",
         consumer_iso3c == "RUS") %>%
  group_by(year) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup()

# Russia's consumption (2013-2014) from countries imposing sanctions
q_pre <- consumption_change %>%
  filter(year %in% 2013:2014) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup() %>%
  pull(consumption_live_t)

# Russia's consumption (2013-2014) from countries imposing sanctions
q_post <- consumption_change %>%
  filter(year %in% 2015:2016) %>%
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup %>%
  pull(consumption_live_t)

# Percent change in Russian consumption from countries imposing sanctions
percent_change <- 100 * ((q_post - q_pre) / q_pre)
```

Russia's consumption, in 2013-2014, from countries imposing sanctions was `r signif(q_pre / 1e6, digits = 3)` million tonnes. Russia's consumption, in 2015-2016, from countries imposing sanctions was `r signif(q_post / 1e5, digits = 3)` hundred thousand tonnes. This represented a percent change of `r signif(percent_change, digits = 3)`%.

```{r top_intermediate_partners, echo = TRUE}
intermediate_partners <- consumption %>%
  filter(consumer_iso3c == "USA",
         source_country_iso3c == "RUS",
         year %in% 2015:2019) %>% 
  group_by(exporter_iso3c) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(percent = 100 * consumption_live_t / sum(consumption_live_t)) %>%
  arrange(desc(percent))

top_intermediates <- intermediate_partners %>%
  slice_max(order_by = percent, n = 5)

colnames(top_intermediates) <- c("Intermediate Exporter", "Consumption (live weight tonnes)", "Percent (%)")
```
### Top Intermediate Exporters for Russian sourced products to the US (2015-2019)
`r reactable(top_intermediates)`

```{r}
top_intermediate_partner <- intermediate_partners %>%
  slice_max(order_by = percent, n = 1) %>%
  pull(exporter_iso3c)

top_intermediate_partner_percent <- intermediate_partners %>%
  slice_max(order_by = percent, n = 1) %>%
  pull(percent)

top_intermediate_partner_species <- consumption %>%
  filter(consumer_iso3c == "USA", exporter_iso3c == top_intermediate_partner, source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
  group_by(common_name_hs_modified) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
  arrange(desc(percent)) %>%
  slice_max(order_by = percent, n = 3)
```

### Top Species Exported from RUS -> `r top_intermediate_partner` -> USA
`r reactable(top_intermediate_partner_species)`

We show that in recent years (2015-2019), `r signif(top_intermediate_partner_percent, digits = 3)` of Russian products consumed in the US moved through `r top_intermediate_partner`, with the majority being `r top_intermediate_partner_species[1,]$common_name_hs_modified`, `r top_intermediate_partner_species[2,]$common_name_hs_modified`, and `r top_intermediate_partner_species[3,]$common_name_hs_modified`.

```{r unfriendly_countries_consumption}
unfriendly_rus_consumption <- consumption %>%
  filter(sanctions_towards_russia == "Russia unfriendly countries" &
           ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
  mutate(period = case_when(
    year %in% 2013:2014 ~ "before_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(sanctions_towards_russia, period) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup()

unfriendly_consumption_pre <- unfriendly_rus_consumption %>%
  filter(period == "before_sanctions") %>%
  pull(consumption_live_t)

unfriendly_consumption_post <- unfriendly_rus_consumption %>%
  filter(period == "after_sanctions") %>%
  pull(consumption_live_t)

unfriendly_consumption_percent_change = 100 * ((unfriendly_consumption_post - unfriendly_consumption_pre) / unfriendly_consumption_pre)
```

Analyzing consumption of Russian-caught seafood following the 2014 round of sanctions, we find that countries that imposed sanctions (“unfriendly countries”) initially moderately reduced total consumption of Russian seafood (`r signif(unfriendly_consumption_percent_change, digits = 3)`%) in 2015–2016 compared to 2013-2014.

```{r friendly_countries_consumption}
friendly_rus_consumption <- consumption %>%
  filter(sanctions_towards_russia == "Russia friendly countries" &
           ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
  mutate(period = case_when(
    year %in% 2013:2014 ~ "before_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(sanctions_towards_russia, period) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup()

friendly_consumption_pre <- friendly_rus_consumption %>%
  filter(period == "before_sanctions") %>%
  pull(consumption_live_t)

friendly_consumption_post <- friendly_rus_consumption %>%
  filter(period == "after_sanctions") %>%
  pull(consumption_live_t)

friendly_consumption_percent_change = 100 * ((friendly_consumption_post - friendly_consumption_pre) / friendly_consumption_pre)
```

Countries which did not impose sanctions (“friendly countries”) also increased consumption of Russian products (`r signif(friendly_consumption_percent_change, digits = 3)`% in 2015–2016 compared to 2013–2014).

```{r consumption_by_russia}

consumption_by_rus <- consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS",
         ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
  mutate(period = case_when(
    year %in% 2013:2014 ~ "before_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(source_sanctions_towards_russia, period) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ungroup()

rus_of_unfriendly <- consumption_by_rus %>%
  filter(source_sanctions_towards_russia == "Russia unfriendly countries")

rus_of_unfriendly_pre <- rus_of_unfriendly %>%
  filter(period == "before_sanctions") %>%
  pull(consumption_live_t)

rus_of_unfriendly_post <- rus_of_unfriendly %>%
  filter(period == "after_sanctions") %>%
  pull(consumption_live_t)

rus_of_unfriendly_percent_change <- 100 * ((rus_of_unfriendly_post - rus_of_unfriendly_pre) / rus_of_unfriendly_pre)
```

### Consumption By Russia
`r reactable(consumption_by_rus)`

Russia reduced consumption of seafood from unfriendly countries by `r signif(rus_of_unfriendly_percent_change, digits = 3)`% between 2015-2016 compared to 2013-2014.

```{r}
rus_to_us_path <- consumption %>%
  filter(consumer_iso3c == "USA" & source_country_iso3c == "RUS" &
           (year >= 2015 & year <= 2019)) %>%
  group_by(source_country_iso3c, exporter_iso3c, consumer_iso3c) %>%
  summarize(consumption_live_t = sum(consumption_live_t)) %>%
  ungroup() %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct",
    TRUE ~ "Indirect"
  )) %>%
  group_by(source_country_iso3c, consumer_iso3c, path) %>%
  summarize(consumption_live_t = sum(consumption_live_t)) %>%
  ungroup() %>%
  group_by(consumer_iso3c, source_country_iso3c) %>%
  mutate(percent = 100 * (consumption_live_t/sum(consumption_live_t))) %>%
  ungroup()

rus_to_us_indirect_percent <- rus_to_us_path %>%
  filter(path == "Indirect") %>%
  pull(percent)
```

### US Direct vs Indirect consumption of Russian Products (2015-2019)

`r reactable(rus_to_us_path)`

We find that for 2015–2019, `r signif(rus_to_us_indirect_percent, digits = 3)`% of Russian-harvested seafood consumed in the US was processed in and imported from a country other than Russia, with `r signif(top_intermediate_partner_percent, digits = 3)`% moving through `r top_intermediate_partner`

```{r}

rus_to_us_species <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
  group_by(sciname_hs_modified, common_name_hs_modified) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(percent = 100 * consumption_live_t / sum(consumption_live_t)) %>%
  arrange(desc(percent))

top_rus_to_us_species <- rus_to_us_species %>%
  slice_max(order_by = percent, n = 5)

top_rus_to_us_species_percent <- sum(top_rus_to_us_species$percent)
```

The top five species were `r top_rus_to_us_species[1,]$common_name_hs_modified` (`r top_rus_to_us_species[1,]$sciname_hs_modified`), `r top_rus_to_us_species[2,]$common_name_hs_modified` (`r top_rus_to_us_species[2,]$sciname_hs_modified`), `r top_rus_to_us_species[3,]$common_name_hs_modified` (`r top_rus_to_us_species[3,]$sciname_hs_modified`),  `r top_rus_to_us_species[4,]$common_name_hs_modified` (`r top_rus_to_us_species[4,]$sciname_hs_modified`), and `r top_rus_to_us_species[5,]$common_name_hs_modified` (`r top_rus_to_us_species[5,]$sciname_hs_modified`), which collectively made up `r signif(top_rus_to_us_species_percent, digits = 3)`% of US consumption of Russian products.

```{r consumption_minimums_2020}

alaska_pollock_min <- rus_chn_usa %>%
  filter(year == 2020 &
           sciname == "gadus chalcogrammus") %>%
  pull(min_russia)

pink_salmon_min <- rus_chn_usa %>%
  filter(year == 2020 &
           sciname == "oncorhynchus gorbuscha") %>%
  pull(min_russia)
```

While US imports of Atlantic cod from China could technically be explained without Russian-sourced products, we estimate that the US imported at least `r signif(alaska_pollock_min, digits = 3)` thousand and `r signif(pink_salmon_min, digits = 3)` thousand tonnes of Russian-sourced Alaska pollock and pink salmon, respectively, via China in 2020.

### 2024-04-19 ms-russia-results.Rmd
update stats text

@@
 ```
+
 ### Top Intermediate Exporters for Russian sourced products to the US (2015-2019)
@@
 unfriendly_rus_consumption <- consumption %>%
-  filter(sanctions_towards_russia == "Russia unfriendly countries" &
+  filter(consumer_iso3c != "RUS" &
+           sanctions_towards_russia == "Russia unfriendly countries" &
            ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
@@
 ```{r friendly_countries_consumption}
+# Look at 2014 drop in consumption of Russian products by friendly countries
 friendly_rus_consumption <- consumption %>%
-  filter(sanctions_towards_russia == "Russia friendly countries" &
-           ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
+  filter(consumer_iso3c != "RUS" & 
+           sanctions_towards_russia == "Russia friendly countries" &
+           ((year %in% 2012:2013) | (year %in% 2014))) %>%
   mutate(period = case_when(
-    year %in% 2013:2014 ~ "before_sanctions",
+    year %in% 2012:2013 ~ "before_sanctions",
     TRUE ~ "after_sanctions"
@@
   group_by(sanctions_towards_russia, period) %>%
-  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
+  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)/length(unique(year))) %>%
   ungroup()
@@
 friendly_consumption_percent_change = 100 * ((friendly_consumption_post - friendly_consumption_pre) / friendly_consumption_pre)
+
+# Friendly country consumption of Russian products following 2014
+friendly_consumption_2020 <- consumption %>%
+  filter(consumer_iso3c != "RUS" & 
+           sanctions_towards_russia == "Russia friendly countries" &
+           year == 2020) %>%
+  group_by(year) %>%
+  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
+  pull(consumption_live_t)
+
+friendly_consumption_percent_change_2020 = 100 * ((friendly_consumption_2020 - friendly_consumption_pre) / friendly_consumption_pre)
 ```
 
-Countries which did not impose sanctions (“friendly countries”) also increased consumption of Russian products (`r signif(friendly_consumption_percent_change, digits = 3)`% in 2015–2016 compared to 2013–2014).
+Countries which did not impose sanctions (“friendly countries”) decreased consumption of Russian products (`r signif(friendly_consumption_percent_change, digits = 3)`% in 2014 compared to 2012–2013), but their consumption quickly rebounded, exceeding `r floor(friendly_consumption_percent_change_2020)`% of the pre-2014 value in 2020.
 

### 2024-06-11 ms-russia-figures.Rmd
update figures ahead of coauthor approval

@@
 consumption_russian_ts_fill <- consumption_russian_ts %>%
-  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
-  geom_area() +
+  ggplot() +
+  geom_area(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
   geom_vline(aes(xintercept = 2014), linetype = 2) +
@@
   labs(x = "", y = "Consumption (mil t, live weight)", fill = "") +
-  facet_wrap(~sanctions_towards_russia) +
+  facet_wrap(~sanctions_towards_russia,
+             labeller = labeller(group = c(a = "A", b = "B"))) +
   theme_minimal() +
@@
   plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) +
+  scale_fill_manual(values = c("#D4B95f", # khaki
+                               "#4FA2A2" # teal
+  )) + 
   xlim(0, 90) +
@@
   plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
+  scale_fill_manual(values = c("#D4B95f", # khaki
+                               "#4FA2A2" # teal
+  )) + 
   xlim(0, 90) +
@@
   nrow = 2,
-  heights = c(1, 2)
+  heights = c(1, 2),
+  labels = c("a", "b")
 )

### 2024-06-11 ms-russia-results.Rmd
update figures ahead of coauthor approval

@@
 ```{r load_data}
-consumption <- read.csv(file.path(datadir, "case_study_consumption.csv"))
+consumption <- read.csv(file.path(datadir, "case_study_consumption.csv")) %>%
+  mutate(sciname_hs_modified = case_when(
+    is.na(sciname_hs_modified) ~ sciname,
+    TRUE ~ sciname_hs_modified
+  ))
+
 consumption_by_rus <- read.csv(file.path(datadir, "fig1_consumption_by_russia.csv"))
+
 rus_chn_usa <- read.csv(file.path(datadir, "rus_chn_usa.csv"))
+
+us_consumption <- read.csv(file.path(datadir, "case_study_usa_consumption.csv")) %>%
+  mutate(sciname_hs_modified = case_when(
+    is.na(sciname_hs_modified) ~ sciname,
+    TRUE ~ sciname_hs_modified
+  ))
 ```
@@
 ```{r consumption_minimums_2020}
-
+# Min value from Russia
 alaska_pollock_min <- rus_chn_usa %>%
@@
   pull(min_russia)
+
+# Max value from Russia
+alaska_pollock_max <- rus_chn_usa %>%
+  filter(year == 2020 &
+           sciname == "gadus chalcogrammus") %>%
+  pull(max_russia)
+
+pink_salmon_max <- rus_chn_usa %>%
+  filter(year == 2020 &
+           sciname == "oncorhynchus gorbuscha") %>%
+  pull(max_russia)
+
+us_total_pollock_consumption <- us_consumption %>%
+  filter(sciname == "gadus chalcogrammus") %>%
+  # Min/max flow values are in 1000 tonnes
+  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
+  pull(consumption_live_t)
+
+us_imported_pollock_consumption <- us_consumption %>%
+  filter(sciname == "gadus chalcogrammus",
+         !is.na(exporter_iso3c)) %>%
+  # Min/max flow values are in 1000 tonnes
+  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
+  pull(consumption_live_t)
+
+us_imported_salmon_consumption <- us_consumption %>%
+  filter(sciname == "oncorhynchus gorbuscha",
+         !is.na(exporter_iso3c)) %>%
+  # Min/max flow values are in 1000 tonnes
+  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
+  pull(consumption_live_t)
+
+us_russian_pollock_consumption <- us_consumption %>%
+  filter(sciname == "gadus chalcogrammus",
+         !is.na(exporter_iso3c),
+         source_country_iso3c == "RUS") %>%
+  # Min/max flow values are in 1000 tonnes
+  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
+  pull(consumption_live_t)
+
+us_russian_salmon_consumption <- us_consumption %>%
+  filter(sciname == "oncorhynchus gorbuscha",
+         !is.na(exporter_iso3c),
+         source_country_iso3c == "RUS") %>%
+  # Min/max flow values are in 1000 tonnes
+  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
+  pull(consumption_live_t)
+
+us_consumption %>%
+  filter(consumer_iso3c == "USA", 
+         sciname_hs_modified %in% c("oncorhynchus gorbuscha", "gadus chalcogrammus")) %>%
+  mutate(consumption_source = case_when(
+    (source_country_iso3c == consumer_iso3c & is.na(exporter_iso3c)) ~ "domestic",
+    (source_country_iso3c == consumer_iso3c & !is.na(exporter_iso3c)) ~ "domestic, foreign processed",
+    (source_country_iso3c != consumer_iso3c) ~ "foreign"
+  )) %>%
+  group_by(sciname_hs_modified, consumption_source) %>%
+  summarise(consumption_live_t = sum(consumption_live_t)) %>%
+  group_by(sciname_hs_modified) %>%
+  mutate(percent = 100*consumption_live_t/sum(consumption_live_t))
+
+# tmp <- us_consumption %>%
+#   filter(consumer_iso3c == "USA", 
+#          sciname_hs_modified %in% c("oncorhynchus gorbuscha", "gadus chalcogrammus")) %>%
+#   group_by(sciname_hs_modified, source_country_iso3c) %>%
+#   summarise(consumption_live_t = sum(consumption_live_t)) %>%
+#   group_by(sciname_hs_modified) %>%
+#   mutate(percent = 100*consumption_live_t/sum(consumption_live_t))
+
+us_consumption %>%
+  filter(consumer_iso3c == "USA", 
+         sciname_hs_modified == "oncorhynchus gorbuscha") %>%
+  mutate(exporter_iso3c = case_when(
+    is.na(exporter_iso3c) ~ source_country_iso3c,
+    TRUE ~ exporter_iso3c
+  )) %>%
+  plot_sankey(cols = c("source_country_iso3c", 
+                       "exporter_iso3c", 
+                       "consumer_iso3c"),
+              value = "consumption_live_t")
+
 ```
@@
 While US imports of Atlantic cod from China could technically be explained without Russian-sourced products, we estimate that the US imported at least `r signif(alaska_pollock_min, digits = 3)` thousand and `r signif(pink_salmon_min, digits = 3)` thousand tonnes of Russian-sourced Alaska pollock and pink salmon, respectively, via China in 2020.
+
+Based on these ranges, we estimate `r signif(100*alaska_pollock_min/us_imported_pollock_consumption, digits = 3)`-`r min(signif(100*alaska_pollock_max/us_imported_pollock_consumption, digits = 3), 100)`% of imported Alaska pollock and `r signif(100*pink_salmon_min/us_imported_salmon_consumption, digits = 3)`-`r min(signif(100*pink_salmon_max/us_imported_salmon_consumption, digits = 3), 100)`% of imported pink salmon is Russian-harvested.

### 2024-06-11 prep_data.R

@@ -89,7 +89,13 @@ artis <- artis %>%
               select(sciname, common_name), 
             by = "sciname") 
 
+# Filter to USA for consumption data
+consumption_usa <- consumption %>%
+  filter(consumer_iso3c == "USA")
 
+write.csv(consumption_usa, file.path(outdir, "case_study_usa_consumption.csv"), row.names = FALSE)
+
+# Filter consumption to flows involving Russia
 consumption <- consumption %>%
   # Filter consumption to when Russia is involved
   filter(source_country_iso3c == "RUS"|exporter_iso3c == "RUS"|consumer_iso3c == "RUS") %>%

### 2024-10-21 ms-russia-results.Rmd
Add numeric results for Russia consumption changes

@@
 rus_of_unfriendly_percent_change <- 100 * ((rus_of_unfriendly_post - rus_of_unfriendly_pre) / rus_of_unfriendly_pre)
+
+# All consumption
+consumption_by_rus_total <- consumption %>%
+  filter(consumer_iso3c == "RUS", 
+         source_country_iso3c != "RUS",
+         ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
+  mutate(period = case_when(
+    year %in% 2013:2014 ~ "before_sanctions",
+    TRUE ~ "after_sanctions"
+  )) %>%
+  group_by(period) %>%
+  summarise(consumption_live_t = sum(consumption_live_t)) %>%
+  ungroup()
+
+rus_of_total_pre <- consumption_by_rus_total %>%
+  filter(period == "before_sanctions") %>%
+  pull(consumption_live_t)
+
+rus_of_total_post <- consumption_by_rus_total %>%
+  filter(period == "after_sanctions") %>%
+  pull(consumption_live_t)
+
+rus_total_percent_change <- 100 * ((rus_of_total_post - rus_of_total_pre) / rus_of_total_pre)
+
+# Consumption from friendly countries
+consumption_by_rus_friendly <- consumption %>%
+  filter(consumer_iso3c == "RUS", 
+         source_country_iso3c != "RUS",
+         ((year %in% 2015) | (year %in% 2019))) %>%
+  mutate(period = case_when(
+    year %in% 2015 ~ "at_sanctions",
+    TRUE ~ "after_sanctions"
+  )) %>%
+  group_by(source_sanctions_towards_russia, period) %>%
+  summarise(consumption_live_t = sum(consumption_live_t)) %>%
+  ungroup()
+
+rus_of_friendly <- consumption_by_rus_friendly %>%
+  filter(source_sanctions_towards_russia == "Russia friendly countries")
+
+rus_of_friendly_pre <- rus_of_friendly %>%
+  filter(period == "at_sanctions") %>%
+  pull(consumption_live_t)
+
+rus_of_friendly_post <- rus_of_friendly %>%
+  filter(period == "after_sanctions") %>%
+  pull(consumption_live_t)
+
+rus_of_friendly_percent_change <- 100 * ((rus_of_friendly_post - rus_of_friendly_pre) / rus_of_friendly_pre)
 ```
